### 2019-05-24 gwnnDraft01.tex
Add files via upload

\documentclass[nofootinbib,twocolumn,preprintnumbers]{revtex4-2}
%\usepackage[dvips]{graphicx}
\pdfoutput=1
\usepackage{amsmath,amsthm,amssymb,multirow,psfrag}
\usepackage{epsfig}
\usepackage{color}
\usepackage{slashed}
\graphicspath{{./Figures/}}

\begin{document}

%%%%%%%%%%%new definitions: 
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
  \raise1pt\hbox{$<$}}}
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
  \raise1pt\hbox{$>$}}}
\newcommand{\vev}[1]{ \left\langle {#1} \right\rangle }
\newcommand{\bra}[1]{ \langle {#1} | }
\newcommand{\ket}[1]{ | {#1} \rangle }
\newcommand{\ev}{ {\rm eV} }
\newcommand{\kev}{{\rm keV}}
\newcommand{\mev}{{\rm MeV}}
\newcommand{\gev}{{\mathrm GeV}}
\newcommand{\tev}{{\rm TeV}}
\newcommand{\mpl}{$M_{Pl}$}
\newcommand{\mw}{$M_{W}$}
\newcommand{\Ft}{F_{T}}
\newcommand{\Zparity}{\mathbb{Z}_2}
\newcommand{\BLambda}{\boldsymbol{\lambda}}
\newcommand{\met}{\;\not\!\!\!{E}_T}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\nn}{\nonumber}
\newcommand{\hc}{\mathrm{h.c.}}
\newcommand{\eps}{\epsilon}
\newcommand{\bwt}{\begin{widetext}}
\newcommand{\ewt}{\end{widetext}}
\newcommand{\draftnote}[1]{{\bf\color{blue} #1}}

\newcommand{\cO}{{\cal O}}
\newcommand{\cL}{{\cal L}}
\newcommand{\cM}{{\cal M}}

%References  
\newcommand{\fref}[1]{Fig.~\ref{fig:#1}} 
\newcommand{\eref}[1]{Eq.~\eqref{eq:#1}} 
\newcommand{\aref}[1]{Appendix~\ref{app:#1}}
\newcommand{\sref}[1]{Section~\ref{sec:#1}}
\newcommand{\tref}[1]{Table~\ref{tab:#1}}

\title{\LARGE{{\bf{Piled up gravitational waves:} \\
\bf{Searching for new signals of $N$naturalness} }}}
\author{{\bf {Paul Smith$\,^{a}$}}}

\affiliation{
$^a$Ottawa-Carleton  Institute  for  Physics,  Carleton  University,\\
1125  Colonel  By  Drive,  Ottawa,  Ontario  K1S  5B6,  Canada
}

\email{
PaulSmith3@cmail.carleton.ca \\
}

\begin{abstract}
We explore the possibility of detecting gravitational waves generated by 1st order phase transitions in multiple dark sectors. Nnaturalness is taken as a sample model that features multiple additional sectors, many of which undergo phase transitions that produce gravitational waves. We examine the cosmological history of this framework and determine the gravitational wave profiles generated. These profiles are checked against projections of next generation gravitational wave experiments, demonstrating that Nnaturalness can indeed produce unique gravitational wave signatures that will be probed by these future experiments. 
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} 
\label{sec:intro}

\section{Gravitational Waves}
\label{sec:gw}

\section{Enter Nnaturalness}
\label{sec:nn}

\subsection{Mechanism}
$N$naturalness is a model framework that looks to solve the hierarchy problem through the introduction of $N$ mutually non-interacting sectors \cite{Arkani-Hamed:2016rle}. The framework itself is very general: the various sectors can possess a wide range of particle content that can be freely selected by the model builder. The one exception to this is that ``our" sector must consist of the Standard Model. For simplicity, the original paper takes all additional new sectors to be copies of the SM (with the same gauge groups and Yukawa structure); however the Higgs mass parameters of each sector are allowed to taken on values distributed between $-\Lambda_H^2$ and $\Lambda^2_H$, with $\Lambda_H$ being the scale that cuts off quadratic divergences.

This construction leads to sectors that are automatically accidentally tuned to the $1/N$ level, leading to a sector with a mass parameter $m_H^2 \sim \Lambda_H^2/N$. The sector with the smallest non-zero vacuum expectation value (vev) as ``our" sector --- the SM sector. It should be noted that the values of $m_H^2$ pass through zero, resulting in effectively 2 types of sectors: ``standard" sectors like our own with a negative Higgs mass parameter squared, possess a vev, and exhibit electroweak symmetry breaking and ``exotic" sectors with a positive Higgs mass parameter squared that thus feature no electroweak symmetry breaking and a zero vev.

Keeping with the original convention, we write our mass parameter as
\begin{equation}\label{eqn:massParam}
\left(m_H^2\right)_i = -\frac{\Lambda_H^2}{N}(2i+r),
\end{equation}
where $i$ denotes the sector ($-\frac{N}{2}\leq i \leq \frac{N}{2}$). $i = 0$ is the sector that possess the smallest vev and is thus ``our" SM sector. Finally, the parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one. Within this work, we looked at variants on this sort of tuning including non-uniform distributions and clustered sector effects; these ideas are discussed in Sec. \ref{sec:signals}.

As mentioned above, half of all sectors in this model feature a Higgs mass parameter such that $m_H^2 < 0$. These sectors feature electroweak symmetry breaking just like in the SM, however the vevs produced scale with the changing mass parameter: $v_i \sim v\sqrt{i}$. As the masses for particles in these sectors scale with the vev, this leads to the masses of particles within each sector strictly increasing with $i$. The consequences of this on the QCD of $i \geq 1$ sectors is further discussed in Sec. \ref{sec:dQCD}.

The remaining sectors within this model provide a radical departure from our own. $m_H^2 > 0$ leads to no vev and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$. As a result, fermion masses are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet. This leads to very light fermions: $m_f \sim y_f y_t \Lambda_{QCD}^3/(m^2_H)_i \leq 100$ eV, with $y_f$ representing the Yukawa coupling to fermion $f$. The extremely light quarks that appear in these sectors dramatically change the nature of the QCD phase transition --- unlike the SM, the transition is strongly first order. Again, this is further developed in Sec. \ref{sec:dQCD}. Crucially, this results in the production of gravitational waves. This is the physical signature we're interested in exploring within this paper; the calculation and results are presented in Sec. \ref{sec:signals}.

A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by number of effective neutrinos ($N_{eff}$) bounds. This is done through the introduction of a post-inflationary field called the ``reheaton". After inflation, the reheaton field possess the majority of the energy density of the Universe. Although this field can generically be either by bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$. Our focus is primarily the production of gravitational waves from multiple sectors: the shifting to a fermion reheaton doesn't change the scaling of the energy density of the exotic sectors and, as a result, is ignored in our analysis.

\subsection{Reheating}

In order to maintain the naturalness of our SM sector, the reheaton coupling is taken to be universal to every sector's Higgs. However, a large amount of the Universe's energy density must ultimately be deposited in our own sector for $N$naturalness to avoid instant exclusion. In order to accomplish this the decay width into each sector must drop as $\vert m_H\vert$ grows. If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$ then we construct a model that behaves as desired.

The appropriate Lagrangian for a scalar reheaton $\phi$ is: 
\begin{equation}\label{eqn:nnLagrangian}
\cL_\phi \supset -a\phi\sum_i\vert H_i\vert^2 - \frac{1}{2}m^2_\phi \phi^2.
\end{equation}
Note that the cross-quartic couplings are absent, suppressed by a very small coupling. Effective Lagrangians for the two different types of sectors present in this theory can be obtained through the integrating out of the Higgs bosons in every sector:
\begin{equation}\label{eqn:nnEffLag}
\begin{split}
\cL_\phi^{v \neq 0} &\supset C_1 a y_q\frac{v}{m_h^2}\phi q q^c,
\\
\cL_\phi^{v = 0} &\supset C_2 a \frac{g^2}{16\pi^2 m_H^2}\phi W_{\mu\nu}W^{\mu\nu},
\end{split}
\end{equation}
with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.

Immediately from Eq. (\ref{eqn:nnEffLag}), we can see that the matrix element for decays into standard sectors is inversely proportional to that sectors higgs mass, $\cM_{m_H^2 < 0} \sim 1/m_{h_i}$. The Feynman diagram for this process is presented in Fig. \ref{fig:something}. The loop decay of $\phi \rightarrow \gamma\gamma$ is always sub-leading and can be neglected. It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$. For sectors where this kinematic threshold is passed for charm quarks, contributions to cosmological observables can be safely ignored. All in all, we end up with a decay width that scales as $\Gamma_{m_H^2<0} \sim 1/m_h^2$. Since we can expect energy density to be proportional to the decay width, $\frac{\rho_i}{\rho_{SM}} \approx \frac{\Gamma_i}{\Gamma_{SM}}$, this indicates that energy density of standard sectors falls proportional to $1/i$.

For the exotic sectors, Eq. (\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$. As the Feynman diagram (Fig. \ref{fig:something}) shows, the reheaton decays to exotic sectors are loop suppressed, leading to a significantly lower energy density than the standard sectors. Both the decay width and energy density for these sectors scale as: $\Gamma_{m_H^2<0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2$.

As a final note, the reheating temperature, $T_{RH}$, has an upper bound on the order of the weak scale. If this bound is not observed, the SM Higgs mass would have major thermal corrections --- leading to the branching ratios into other sectors being problematically large. In accordance with this restriction, this project only examines reheating temperatures at or below $100$ GeV.

\section{Dark QCD}
\label{sec:dQCD}

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=1.0\textwidth]{columbia.png}
\end{minipage}
\hfill
\caption{Two possible scenarios for the Columbia Plot with the up and down quark mass taken to be identical. The ``physical point" is the Standard Model. Plot from \cite{Cuteri:2017zcb}
}
\label{fig:columbia}
\end{figure*}

Beginning with the work of Pedro Schwaller \cite{Schwaller:2015tja} and continuing through the work of many others \cite{everyoneelse}, strong first order phase transitions for SU(N) dark sectors with arbitrary numbers of flavours have been explored as a source of gravitational waves. As $N$naturalness features $N$ distinct QCD sectors, this becomes an incredibly important potential signature of this class of models. Crucially, the behaviour of the QCD phase transition for each sector must be understood --- sectors that feature a weak cross-over transition do not generate the sought after gravitational wave signatures.

Due to the confining nature of QCD, the exact nature of the phase transition is often difficult to ascertain analytically and requires the study of lattice simulations. The results of these studies on the nature of QCD phase transitions is summarized in the so-called ``Columbia" plot (Fig. \ref{fig:columbia}). As seen in the above figure (and explicitly demonstrated through lattice studies \cite{lattice}), our sector is solidly in the weak-cross over area. In order to observe the strong first order transition required for gravitational wave production, at least some of the additional sectors present in $N$naturalness must feature quarks in either the heavy quark (pure Yang-Mills) or massless limits.

In the Yang-Mills limit we see $m_{u,d,s} \rightarrow \infty$. This leads to the presence of a global $Z_3$ centre symmetry that is broken at high temperatures but restored low temperatures. Ultimately, this restoration results in a first order phase transition \cite{SVETITSKY1982423}. On the other end of the spectrum, ``massless" quark theories ($m_q \ll \Lambda_{QCD}$ for all quarks) also contain strong phase transitions due to the breakdown of SU$(N)\,\times$ SU$(N)$ chiral symmetry \cite{Pisarski:1983ms}. Both the Yang-Mills and massless limit arguments can be generalized to SU$(N \geq 3)$: coupling both with the additional restriction that we avoid the conformal window indicates that strong first order phase transitions can occur if we have $n = 0$ (pure Yang-Mills) or $3 \leq n < 4N$ (light quark limit) very light flavours.

For $N$naturalness, standard sectors with higher vevs possess more massive quarks; eventually, sectors with large enough vevs push us into the upper-right corner. Conversely, exotic sectors with zero vev feature incredibly light quarks and drop us into the bottom-left corner. In order to figure out the specifics of each sector, we follow  the same procedure as \cite{Cui:2011wk} but generalize it to an arbitrary number of additional sectors. First, due to the parameters of each sector being taken to be identical save for the higgs mass squared (thus $v \neq v_i$, where $v$ is the SM vev), we assume that the strong coupling of every sector is identical at some high scale. 
Explicitly, above the top quark mass scale $\Lambda_{QCD} = 89 \pm 5$ in $\overline{MS}$ \cite{PhysRevD.98.030001}. Since the running of the gauge coupling at scale $\mu$ is given by 
\begin{equation}\label{eqn:QCDrunning}
\alpha_s (\mu) = \frac{2\pi}{11-\frac{2n_f}{3}}\frac{1}{\ln{\mu/\Lambda}}
\end{equation} 
where $n_f$ is the number of quark flavours and $\Lambda$ is the confinement scale $\Lambda_{QCD}$ \cite{Peskin:1995ev}.

For any other sector $i$ we write out the expression as: 
\begin{equation}\label{eqn:QCDrunningi}
\alpha_{s}^i (\mu) = \frac{2\pi}{11-\frac{2n^i_f}{3}}\frac{1}{\ln{\mu/\Lambda^i}},
\end{equation}
featuring the equivalent definitions for the additional sectors. Because we've set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at scales above the top quark mass for the heaviest sector. However, since the masses of the quarks in each sector are different, we end up with a unique running of the coupling for each sector. At every quark mass threshold for a given sector, we match the coupling strengths above and below the threshold and determine the new $\Lambda^i$ for the lower scale:
\begin{equation}
\alpha_s^{i(5)} = \alpha_s^{i(6)}
\end{equation} 
and thus
\begin{equation}
\Lambda_{(5)}^i = (m_t^{i})^{2/23}(\Lambda_{(6)}^i)^{21/23}.
\end{equation}

Suppressing the $i$s for cleanliness, we can arrive at similar relations at the bottom and charm thresholds
\begin{equation}
\begin{split}
\Lambda_{(4)} = (m_b)^{2/25}(\Lambda_{(5)})^{23/25},
\\
\Lambda_{(3)} = (m_c)^{2/23}(\Lambda_{(4)})^{25/27}.
\end{split}
\end{equation}
These can be combined to show that
\begin{equation}
\Lambda_{(3)} = (m_t m_b m_c)^{2/27}(\Lambda_{(6)})^{21/27}.
\end{equation}
This type of matching procedure can be done as many times as necessary for a given sector. The process terminates when $\Lambda_i$ for a given scale is larger than the next quark mass threshold (i.e running the scale down arrives at the $\Lambda_{QCD}$ phase transition before reaching the next quark mass scale).

In cosmological terms, we can envision a sector's thermal history unfolding where as the plasma cools below each quark mass threshold, said quarks are frozen out. At a certain point, the sector arrives at the QCD phase transition and confinement occurs (provided there are light enough quarks to confine) --- if this occurs when $\geq 3$ quarks are at a much lower scale or all quarks have already frozen out, we get the desired phase transition.

\subsection{Standard Sectors}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{critIndex.png}

\hfill
\caption{Critical index $i$ as a function of slop factor. 
}
\label{fig:critIndex}
\end{figure}

As mentioned in the previous sections, for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$. This leads to increasingly heavy particle spectra for higher sectors --- eventually leading to sectors that are essentially pure Yang-Mills that featuring strong first order phase transitions. This, of course, begs the question: at what index $i$ do said phase transitions begin?

The actual boundary of region of interest on the Columbia plot is not precisely known and further lattice simulations are required to determine exactly where in parameter space cross-over transitions end and first order transitions begin. In lieu of such studies, we parameterize our ignorance in the form of a ``slop factor" $\kappa$. Assuming the up and down quarks of each sector to be of roughly the same scale, we determine what sector $i$ features $\kappa m_u^i \approx \Lambda_{QCD}$.

Using the methods outlined in the prior section we determine $\Lambda_{QCD}$ to have a relevant value of 
\begin{equation}\label{eqn:lambda2}
\Lambda^i_{(2)} = (m_s^i m_c^i m_b^i m_t^i)^{2/29}(\Lambda^i_{(6)})^{21/29}
\end{equation} 
at the energy scale we're interested in. $\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a standard model value. Rewriting Eq. (\ref{eqn:lambda2}) in terms of standard model variables, 
\begin{equation}\label{eqn:lambda2adj}
\Lambda^i_{(2)} = (m_s m_c m_b m_t i^2)^{2/29}(\Lambda_{(6)})^{21/29}.
\end{equation}
Setting this equal to some multiple of the quark mass of sector $i$,
\begin{equation}
\kappa m^i_u = \kappa m_u \sqrt{i} = (m_s m_c m_b m_t i^2)^{2/29}(\Lambda_{(6)})^{21/29}.
\end{equation}
This can be solved for $i$:
\begin{equation}\label{eqn:critIndex}
i = \frac{(m_s m_c m_b m_t i^2)^{4/25}(\Lambda_{(6)})^{42/25}}{(\kappa m_u)^{58/25}}.
\end{equation}
The results as a function of $\kappa$ are plotted in Fig. \ref{fig:critIndex}.

The critical index plot (Fig. \ref{fig:critIndex}) clearly demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$. Looking back to the energy density plot (Fig. \ref{fig:energyDensity}), we see the energy density of these sectors is at most $10^{-8}$ that of our sector. As a result, the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.

\subsection{Exotic Sectors}

\section{Constraints}
\label{sec:constraints}

\section{Signals}
\label{sec:signals}

\section{Conclusion}
\label{sec:conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{apsrev4-2}
\bibliography{refs}

\end{document}

### 2019-06-03 gwnnDraft01.tex
Added Constraints Section

@@
 \begin{equation}\label{eqn:critIndex}
-i = \frac{(m_s m_c m_b m_t i^2)^{4/25}(\Lambda_{(6)})^{42/25}}{(\kappa m_u)^{58/25}}.
+i = \frac{(m_s m_c m_b m_t)^{4/25}(\Lambda_{(6)})^{42/25}}{(\kappa m_u)^{58/25}}.
 \end{equation}
@@
 
+In every exotic sector the fermion masses are exceptionally light: even the most massive quark of each sector is orders of magnitude smaller than our confinement scale, $m_t \ll \Lambda_{QCD}$.
+Additionally, since $m_q \propto 1/(m^2_H)_i$ this separation only becomes more pronounced as we move to sectors further from our own.
+The scale of the exotic quarks makes it unnecessary to run down the scale of the strong coupling as done for the standard sectors --- the phase transition for all exotic sectors occurs at $\sim 90 \,\mathrm{MeV}$ and a strong first order phase transition occurs for all exotic sectors at this temperature.
+
+The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6) \,\times$ SU$(6) \rightarrow\,$ SU$(6)$.
+This leads to the production of 35 pseudo-Goldstone bosons during the phase transition.
+These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
+Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh},
+\begin{equation}\label{eqn:critPTstrength}
+\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
+\end{equation} 
+for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
+
+The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation \cite{Schwartz:2013pla},
+\begin{equation}\label{eqn:gmor}
+m^2_{\pi} = \frac{V^3}{F^2_{\pi}}(m_u + m_d),
+\end{equation}
+where $V \sim \Lambda_{QCD}$, $F_\pi$ is the pion decay constant. So, for mesons in exotic sector $i$:
+\begin{equation}
+m_{\pi}^i \sim \sqrt{\frac{m_1^i+m_2^i}{m_u + m_d}} m_{\pi}.
+\end{equation}
+Ultimately, calculating the critical phase transition strength for each sector using Eq.
+(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.
+
 \section{Constraints}
 \label{sec:constraints}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{NeffBounds.png}
+\label{fig:Neff}
+\hfill
+\caption{$\Delta N_{eff}$ as a function of relativistic degrees of freedom in a fully decoupled hidden sector ($g_h$) and the temperature ratio of said sector.
+Contours set $\Delta N_{eff}$ to 0.01 (forest green), 0.03 (lime green), 0.1 (gentle pink), and 0.5 (royal violet).
+Most stringent current $N_{eff}$ bounds shade in grey.
+}
+\end{figure}
+
+In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom.
+Dark photons, neutrinos, and the like abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons of these sectors are can easily be relativistic.
+In $N$naturalness this feature is realized quite dramatically: each of the thousands (or millions or billions) of sectors possess relativistic degrees of freedom.
+The presence of these particles can have two main effects: extra relativistic particles can alter the expansion history of the universe through changes to the energy density or hidden sectors can feature annihilations that reheat the photons or neutrinos of our sector near Big Bang Nucleosynthesis (BBN) and affect the light element abundances.
+The effective number of neutrino species, $N_{eff}$, describes these contributions and, as such, is the strictest constraint that must be dealt with when studying these type of multi-phase transition models.
+
+The SM predicts that $N^{SM}_{eff} = 3.046$ \cite{Mangano:2005cc}.
+This is in good agreement with bounds from studies of the Cosmic Microwave Background (CMB) by Planck combined with bayon acoustic oscillations (BAO) measurements \cite{Aghanim:2018eyx}:
+\begin{equation}
+N_{eff} = 2.99^{+0.34}_{-0.33}.
+\end{equation}
+Various different assumptions about the history of the universe can be made and different data sets can be chosen to obtain slightly different results \cite{Breitbach:2018ddu} --- for the purposes of this exploratory work, wading through this landscape is unnecessary.
+
+For fully decoupled sectors that never enters (or reenters) thermal equilibrium with our sector, we obtain additional contributions to $N^{SM}_{eff}$ \cite{Breitbach:2018ddu}
+\begin{equation}\label{eqn:DeltaNeff1hs}
+\Delta N_{eff} = \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_h \xi_h^4.
+\end{equation} 
+Here, $g_h$ represents the effective number of relativistic degrees of freedom for the hidden sector when the hidden sector has a temperature $T_h = \xi_h T_\gamma$.
+Contours for Eq.
+(\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.
+\ref{fig:Neff}.
+We take this approach and generalize it to include many additional sectors:
+\begin{equation}\label{eqn:DeltaNeff}
+\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \xi^4_{i}.
+\end{equation}
+
+As Fig.
+\ref{fig:Neff} demonstrates, sectors with a temperature ratio above $\xi_h\sim 0.5$ with even a couple of relativist particles are immediately excluded by CMB constraints.
+Accordingly, the additional sectors present in this project must be heated to a much smaller fraction of our own sector's temperature.
+
+\subsection{Exotic Sector Contributions}
+
+The original $N$naturalness paper focused on the (stronger) $N_{eff}$ constraints from the additional standard sectors and ignored the exotic sectors altogether \cite{Arkani-Hamed:2016rle}; in contrast, we take the opposite approach.
+Since we're more interested in a more general scenario with multiple dark phase transitions, we focus in on whether zero vev sectors can dodge these $N_{eff}$ bounds.
+
+Within the framework of SM-like sectors (save the higgs mass parameter), our exotic sectors feature at most 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom.
+Scaling the fermionic contributions by $7/8$ gives us 106.75 effective relativistic degrees of freedom.
+After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom.
+Since all additional sectors are colder than our own by the time photon decoupling occurs ($\sim 0.39 \ev$), the pions of all of these sectors have a much higher mass in accordance with Eq.
+(\ref{eqn:gmor}) and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector.
+
+Coupling the number of effective degrees of freedom per sector with the energy density scaling of $\sim 1/m_H^4$ found in the zero vev sectors leads to tiny temperature ratios.
+Assuming a reheating temperature of $100$ GeV and a completely uniform distribution of sectors, the temperature of the first exotic sector is slightly more than $6\%$ of our sector at reheating.
+Applying Eq.
+(\ref{eqn:DeltaNeff}) to this particular situation gives us:
+\begin{equation}
+\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{0.06}{i^2}\right)^4.
+\end{equation}     
+Summing over all sectors (sectors above $i \sim 10$ essentially don't contribute due to the small temperature ratio) gives us a contribution of $\mathcal{O} (10^{-4})$.
+Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.
+
+In additional runs completed with various adjustments to the exotic sectors (e.g.
+adjusting the exotic sectors to have a lower higgs mass squared or clustering multiple hidden sectors close to the first exotic one) the value of $\Delta N_{eff}$ coming from the exotic sectors is larger than the base $N$naturalness case.
+This increase is, for the most part, not excluded by current bounds, but will be mostly probeable by next generation CMB experiments.
 

### 2019-08-01 gwnnDraft02.tex
Adding in the second draft plus files
Includes the image files (Feynman diagrams) introduced in draft 2. I've restructured the paper to make it flow towards a more general multi-hidden sector analysis.

--- 2019-06-03 gwnnDraft01.tex
@@
 
-\section{Enter Nnaturalness}
+\section{Particle Setup}
 \label{sec:nn}
 
-\subsection{Mechanism}
+Beginning with the work of Pedro Schwaller \cite{Schwaller:2015tja} and continuing through the work of many others \cite{everyoneelse}, strong first order phase transitions for SU(N) dark sectors with arbitrary numbers of flavours have been explored as a source of gravitational waves.
+Here, we look to generalize this study to include classes of models that feature multiple dark sectors that undergo gravitational wave producing phase transitions.
+The multiple sets of gravitational waves produced in these types of models superimpose: potentially creating signals that deviate from the typical phase transition gravitational wave spectrum.
+For any multi dark sector model, the behaviour of the QCD phase transition for each sector must be understood --- sectors that feature a weak cross-over transition do not generate the sought after gravitational wave signatures.
+We use $N$naturalness as an example framework since it features $N$ distinct QCD sectors at a wide range of possible scales; this allows us to probe a wide range potential signature of this class of models.
+As an additional bonus, different sectors (``standard" and ``exotic", as will be outlined later in this section) can lead to different types of symmetry breaking outlined in Sec.
+\ref{sec:dQCD}.
+
+\subsection{NNaturalness}
+
+\begin{figure*}[tb]
+\centering
+\begin{minipage}[c]{\textwidth}
+\includegraphics[width=0.4\textwidth]{standardDecay.eps}
+\includegraphics[width=0.4\textwidth]{exoticDecay.eps}
+\end{minipage}
+\hfill
+\caption{Feynman diagrams for primary reheaton decays assuming $m_{\phi} \ll m_H$.
+The left decay is the primary decay for standard sectors ($\langle H\rangle\neq 0$), with $f$ representing all possible fermions.
+The right decay occurs in exotic sectors ($\langle H\rangle = 0$)
+}
+\label{fig:reheatonDecays}
+\end{figure*}
+
 $N$naturalness is a model framework that looks to solve the hierarchy problem through the introduction of $N$ mutually non-interacting sectors \cite{Arkani-Hamed:2016rle}.
@@
 
+\subsection{Reheating N Sectors}
+
 A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by number of effective neutrinos ($N_{eff}$) bounds.
@@
 
-\subsection{Reheating}
-
 In order to maintain the naturalness of our SM sector, the reheaton coupling is taken to be universal to every sector's Higgs.
@@
 If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$ then we construct a model that behaves as desired.
+
+Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we generalize our results to include the (rather unnatural) case where sectors are reheated ``randomly" as opposed to in relation to the higg's mass parameter.
+This allows us to explore more general models with multiple dark sectors at a huge range of scales.
+For these models, the reheating mechanism remains undefined and the results of this section are completely irrelevant.
 
@@
 The Feynman diagram for this process is presented in Fig.
-\ref{fig:something}.
+\ref{fig:reheatonDecays}.
 The loop decay of $\phi \rightarrow \gamma\gamma$ is always sub-leading and can be neglected.
@@
 As the Feynman diagram (Fig.
-\ref{fig:something}) shows, the reheaton decays to exotic sectors are loop suppressed, leading to a significantly lower energy density than the standard sectors.
-Both the decay width and energy density for these sectors scale as: $\Gamma_{m_H^2<0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2$.
+\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, leading to a significantly lower energy density than the standard sectors.
+Both the decay width and energy density for these sectors scale as: $\Gamma_{m_H^2>0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2$.
 
@@
 
-Beginning with the work of Pedro Schwaller \cite{Schwaller:2015tja} and continuing through the work of many others \cite{everyoneelse}, strong first order phase transitions for SU(N) dark sectors with arbitrary numbers of flavours have been explored as a source of gravitational waves.
-As $N$naturalness features $N$ distinct QCD sectors, this becomes an incredibly important potential signature of this class of models.
-Crucially, the behaviour of the QCD phase transition for each sector must be understood --- sectors that feature a weak cross-over transition do not generate the sought after gravitational wave signatures.
-
 Due to the confining nature of QCD, the exact nature of the phase transition is often difficult to ascertain analytically and requires the study of lattice simulations.
@@
 As seen in the above figure (and explicitly demonstrated through lattice studies \cite{lattice}), our sector is solidly in the weak-cross over area.
-In order to observe the strong first order transition required for gravitational wave production, at least some of the additional sectors present in $N$naturalness must feature quarks in either the heavy quark (pure Yang-Mills) or massless limits.
+In order to observe the strong first order transition required for gravitational wave production, at least some of the additional sectors present must feature quarks in either the heavy quark (pure Yang-Mills) or massless limits.
 
@@
 
-For $N$naturalness, standard sectors with higher vevs possess more massive quarks; eventually, sectors with large enough vevs push us into the upper-right corner.
+For $N$naturalness (or other mirror sector models), standard sectors with higher vevs possess more massive quarks; eventually, sectors with large enough vevs push us into the upper-right corner.
 Conversely, exotic sectors with zero vev feature incredibly light quarks and drop us into the bottom-left corner.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{critIndex.png}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.45\textwidth]{critIndex.png}
 
-\hfill
-\caption{Critical index $i$ as a function of slop factor. 
-}
-\label{fig:critIndex}
-\end{figure}
+%\hfill
+%\caption{Critical index $i$ as a function of slop factor. 
+%}
+%\label{fig:critIndex}
+%\end{figure}
 
@@
 \end{equation}
-The results as a function of $\kappa$ are plotted in Fig. \ref{fig:critIndex}.
 
-The critical index plot (Fig.
-\ref{fig:critIndex}) clearly demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
-Looking back to the energy density plot (Fig.
-\ref{fig:energyDensity}), we see the energy density of these sectors is at most $10^{-8}$ that of our sector.
+The critical index demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
+Looking back to the description of reheating within $N$naturalness, we see the energy density of these sectors is at most $10^{-4}$ that of our sector.
 As a result, the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.
+
+However, if we move away from the standard $N$naturalness reheating mechanism and begin exploring mirror sectors with large vevs with $\cO( >10\%)$ of our energy density $\rho_{SM}$, we can have sectors with relatively high dark QCD scales that produce detectable gravitational waves.
+These sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+From Eq.
+(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector --- the maximum possible given a $10^{16}$ limit \cite{Arkani-Hamed:2016rle} of sectors is $\sim 38 \,\gev$.
+After imposing $N_{eff}$ constraints (as in Sec.
+\ref{sec:constraints}), the energy density of said sector is limited to $\sim 0.25\rho_{SM}$.
+The signals of this sector and other test cases like it are explored in Sec.
+\ref{sec:signals}.
+It is important to note that these type of sectors mimic the general behaviour of any Yang-Mills like multi dark sector model.
 
@@
 This is in good agreement with bounds from studies of the Cosmic Microwave Background (CMB) by Planck combined with bayon acoustic oscillations (BAO) measurements \cite{Aghanim:2018eyx}:
-\begin{equation}
+\begin{equation}\label{eqn:NeffBounds}
 N_{eff} = 2.99^{+0.34}_{-0.33}.
@@
 After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom.
-Since all additional sectors are colder than our own by the time photon decoupling occurs ($\sim 0.39 \ev$), the pions of all of these sectors have a much higher mass in accordance with Eq.
+Since all additional sectors are colder than our own by the time photon decoupling occurs ($\sim 0.39 \,\ev$), the pions of all of these sectors have a much higher mass in accordance with Eq.
 (\ref{eqn:gmor}) and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector.
@@
 
-In additional runs completed with various adjustments to the exotic sectors (e.g.
-adjusting the exotic sectors to have a lower higgs mass squared or clustering multiple hidden sectors close to the first exotic one) the value of $\Delta N_{eff}$ coming from the exotic sectors is larger than the base $N$naturalness case.
-This increase is, for the most part, not excluded by current bounds, but will be mostly probeable by next generation CMB experiments.
+It should be noted that modifying the exotic sectors' structure (e.g.
+adjusting the exotic sectors to have a lower higgs mass squared or clustering multiple hidden sectors close to the first exotic one) leads to a $\Delta N_{eff}$ contribution that is larger than the base $N$naturalness case.
+This increase is not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.
+
+\subsection{High Scale Transitions}
+
+The generalization of possible reheating mechanisms mentioned in section \ref{sec:nn} --- where the reheating mechanism no longer depends on the higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study.
+Specifically, this allow mirror sectors with large vevs to reheat to significant energy densities and thus produce gravitational waves with enough power to be detected.
+Crucially, despite this analysis being limited to mirror sectors with large higgs' masses this analysis pertains to any strong, confining phase transition at high scales.
+
+Since $N_{eff}$ constraints remain our strongest cosmological bounds for massive standard sectors, our starting point for exploring the limits of high transition temperatures is Eq.
+(\ref{eqn:DeltaNeff}).
+Assuming heavy, standard sectors we can saturate the bounds of Eq.
+(\ref{eqn:NeffBounds}) and solve for the maximum energy density allowed for any number of sectors:
+\begin{equation}\label{eqn:energyDensityAllowed}
+\begin{split}
+\rho_i &\sim 0.25 \rho_{SM} \,\,\,\,\, \mathrm{1}\,\, \mathrm{hidden}\,\, \mathrm{sector},
+\\
+\rho_i &\sim 0.17 \rho_{SM} \,\,\,\,\, \mathrm{5} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
+\\
+\rho_i &\sim 0.14 \rho_{SM} \,\,\,\,\, \mathrm{10} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
+\\
+\rho_i &\sim 0.08 \rho_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors}.
+\end{split}
+\end{equation}
+
+Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own.
+In terms of the $N$naturalness framework, this consisted of looking at various different sectors above the critical index, as mentioned in Sec.
+\ref{sec:dQCD}.
+The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are show in Sec.
+\ref{sec:signals}.
 

### 2019-08-01 gwnnDraft02.tex
fixing typos

@@
 \ref{sec:dQCD}.
-The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are show in Sec.
+The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are shown in Sec.
 \ref{sec:signals}.

### 2019-08-02 gwnnDraft02.tex
Change author list

--- 2019-08-01 gwnnDraft02.tex
@@
 \bf{Searching for new signals of $N$naturalness} }}}
-\author{{\bf {Paul Smith$\,^{a}$}}}
+\author{{\bf {Paul Archer-Smith, Dylan Linthorne, and Daniel Stolarski}}}
 
 \affiliation{
-$^a$Ottawa-Carleton  Institute  for  Physics,  Carleton  University,\\
+Ottawa-Carleton  Institute  for  Physics,  Carleton  University,\\
 1125  Colonel  By  Drive,  Ottawa,  Ontario  K1S  5B6,  Canada

### 2019-08-02 gwnnDraft02.tex
Updated phrasing and grammar

@@
 
-Within the framework of SM-like sectors (save the higgs mass parameter), our exotic sectors feature at most 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom.
+Within the framework of SM-like particle content (save the higgs mass parameter), our exotic sectors feature at most 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom.
 Scaling the fermionic contributions by $7/8$ gives us 106.75 effective relativistic degrees of freedom.
 After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom.
-Since all additional sectors are colder than our own by the time photon decoupling occurs ($\sim 0.39 \,\ev$), the pions of all of these sectors have a much higher mass in accordance with Eq.
-(\ref{eqn:gmor}) and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector.
+Since all additional sectors are colder than our own by the time photon decoupling occurs ($\sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.
+(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector.
 
@@
 \end{equation}     
-Summing over all sectors (sectors above $i \sim 10$ essentially don't contribute due to the small temperature ratio) gives us a contribution of $\mathcal{O} (10^{-4})$.
+Summing over all sectors (sectors above $i \sim 10$ essentially don't contribute due to the small temperature ratios) gives us a contribution of $\mathcal{O} (10^{-4})$.
 Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.

### 2019-08-16 gwnnDraft02.tex
signals update

@@
-\documentclass[nofootinbib,twocolumn,preprintnumbers]{revtex4-2}
+\documentclass[nofootinbib,twocolumn,preprintnumbers]{revtex4-1}
 %\usepackage[dvips]{graphicx}
@@
 \label{sec:gw}
+Sectors other than the SM can be reheated through multifield inflationary theories, Reheaton models, etc.
+In these models, the SM will receive the majority of the energy density while the remaining energy density will be distributed, in a model dependent way, to the various hidden sectors.
+If there does not exist a portal between the sectors, they will remain decoupled and evolve independently.
+When looking at multiple thermally decoupled hidden sectors it is convienent to define the temperature ratio [cite cold,dark,noisy]
+\begin{equation}
+\xi_i \equiv  \frac{T_{i}}{T_{\gamma}}
+\end{equation}
+Where $T_{i}$ is the temperature of the $i^{th}$ hidden sector, and $T_{\gamma}$ the temperature of the standard model (assuming radiation domination).
 
+\vspace{1em }
+- first order phase transitions ( strength, scale, origin)
+Right after reheating, the temperatures of the respective sectors are high leading to restoration of a given sector's symmetry.
+An example being the SM's $SU(3) \times SU(2) \times U(1)$ symmetry being restored as the scalar potential's vev becomes global minimum.
+As the sectors cool down their scalar potentials may change, producing a new global vev at which the symmetry will break by an induced phase transition.
+Depending on the characteristics of the symmetry breaking, the phase transition may be strongly first ordered (SFOPT).
+
+Once the temperature reaches the critical temperature the SFOPT will occur, at which bubbles of the new phase will start to nucleate.
+These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.
+These bubbles are discribed by the following Euclidean action
+
+\begin{equation}
+S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg]
+\end{equation}
+
+Where the time component has been integrated out due to finite temperature effects.
+The system has solutions with a $O(3)$ symmetry.
+We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood.
+Some authors have used the chiral effective lagrangian to calculate a low energy thermalized potential for confining $SU(N)$ .
+
+The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
+A quantity that characterizes the strength of the PT is the ratio of the latent heat and energy density of radiation, at the time of nucleation,
+\begin{equation}
+\alpha = \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30}
+\end{equation}
+Assuming that there is a negligible amount of energy being dumped back into the SM radiation bath, which would cause significant reheating of $\rho_{\gamma}$, the latent heat of the PT $\epsilon$ should  approximately be the energy density of the hidden sector going through the PT.
+$g_{*}$ has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
+\begin{equation}
+g_{*} = g_{*,\gamma} + \sum_{i = 1}^{N} g_{*,i} (\xi_{i})^4
+\end{equation}
+It will be seen that for models with a significant number of hidden sectors, that the lack of substantial reheating in adjecent sectors will cause their respective $g_{*}$ corrections to become negligible, $g_{*} \approx g_{*,\gamma}$.
 \section{Particle Setup}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{NeffBounds.png}
+\includegraphics[width=0.45\textwidth]{neff.png}
 \label{fig:Neff}
@@
 \caption{$\Delta N_{eff}$ as a function of relativistic degrees of freedom in a fully decoupled hidden sector ($g_h$) and the temperature ratio of said sector.
-Contours set $\Delta N_{eff}$ to 0.01 (forest green), 0.03 (lime green), 0.1 (gentle pink), and 0.5 (royal violet).
-Most stringent current $N_{eff}$ bounds shade in grey.
+Contours set $\Delta N_{eff}$ to (0.01, 0.03,  0.1,  0.5) as the dashed lines, from left to right.
+Most stringent current $N_{eff}$ bounds shade in purple.
 }
@@
 \label{sec:signals}
+\begin{figure*}[tb]
+\centering
+\begin{minipage}[c]{\textwidth}
+\includegraphics[width=.45\textwidth]{TwoFar.png} 
+\hfill
+\includegraphics[width=.45\textwidth]{TwoMed.png} 
+\hfill
+\includegraphics[width=.45\textwidth ]{highest.png}
+\hfill
+\includegraphics[width=.45\textwidth]{energydensity.png} 
+\end{minipage}
+\hfill
+\caption{ Gravitational wave power spectrum for various models.
+The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures.
+The bottom right (left) are examples of exotic sectors, discussed in section V, with sectors reheated at $\rho \sim 0.25\rho_{SM}$ ($\rho \sim 0.17\rho_{SM}$ ).
+All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
+The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+\label{fig:Haa}
+\end{figure*}
+Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  The three leading order contributions to the GW power spectrum are as follows:
+\begin{itemize}
+\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration.
+With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$.
+\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves.
+With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
+\item \textbf{Magnetohydrodynamics contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves.
+With efficiency factor $\kappa_{
+turb} \approx 0.1 \kappa_{v} $.
+\end{itemize}
+The total gravitational wave power spectrum is a linear combination of the three contributions,
+\begin{equation}
+h^2\Omega_{GW} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
+\end{equation}
+In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$.
+As shown in section IV, the mass spectrum from the dark QCD chiral breaking sectors is such that the runaway bubble condition is satisfied ($\alpha >\alpha_{\infty}$).
+In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{GW} \approx h^2\Omega_{\phi}$.
+The form of the GW power spectrum at the time of nucleation is given as,
+
+\begin{equation}
+h^2\Omega_{GW} = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
+\end{equation}
+Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
+$S(f)$ is the  frequency spectrum, and a parametric from has been found through numerical simulations of bubble wall collisions.
+\begin{equation}
+S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
+\end{equation}
+The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.
+Depending on the model, the various hidden sectors can phase transition at different scales and therefore temperatures, cause a shift in the GW spectrum's peak frequency given by,
+
+\begin{equation}
+f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}}
+\end{equation}
+
+Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
+In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$.
+As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{GW}^{*}(f)$, will redshift to today's value $\Omega_{GW}^{0}(f) = \mathcal{A}\, \Omega_{GW}^{*}((a_{0}/a) f) $.
+Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,
+
+\begin{equation}
+\Omega_{GW}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{GW}^{i,*}((a_{0}/a)_{i} f) 
+\end{equation}
+
+It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within Nnatrualness or other decoupled hidden sector models.
+In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar.
+This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.
+We can also see that the frequency dependence in the spectrum takes the form of $f/f_{p}$, this causes a cancellation of the redshifting factors in the ratios.
+As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
+This is seen in figures [], where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
+The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
+Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{apsrev4-2}
+\bibliographystyle{apsrev4-1}
 \bibliography{refs}

### 2019-08-16 gwnnDraft02.tex
Lots of draftnotes.

@@
 
-\title{\LARGE{{\bf{Piled up gravitational waves:} \\
-\bf{Searching for new signals of $N$naturalness} }}}
+%\title{\LARGE{{\bf{Piled up gravitational waves:} \\
+%\bf{Searching for new signals of $N$naturalness} }}}
+\title{\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\
+}}}
 \author{{\bf {Paul Archer-Smith, Dylan Linthorne, and Daniel Stolarski}}}
@@
 
-\section{Gravitational Waves}
-\label{sec:gw}
-Sectors other than the SM can be reheated through multifield inflationary theories, Reheaton models, etc.
-In these models, the SM will receive the majority of the energy density while the remaining energy density will be distributed, in a model dependent way, to the various hidden sectors.
-If there does not exist a portal between the sectors, they will remain decoupled and evolve independently.
-When looking at multiple thermally decoupled hidden sectors it is convienent to define the temperature ratio [cite cold,dark,noisy]
-\begin{equation}
-\xi_i \equiv  \frac{T_{i}}{T_{\gamma}}
-\end{equation}
-Where $T_{i}$ is the temperature of the $i^{th}$ hidden sector, and $T_{\gamma}$ the temperature of the standard model (assuming radiation domination).
+The recent experimental detection of gravitational waves~\cite{} gives humanity a new way to observe the universe.
+Future experiments~\cite{} will greatly expand the frequency range observable.
+Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{}.
+Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.
 
-\vspace{1em }
-- first order phase transitions ( strength, scale, origin)
-Right after reheating, the temperatures of the respective sectors are high leading to restoration of a given sector's symmetry.
-An example being the SM's $SU(3) \times SU(2) \times U(1)$ symmetry being restored as the scalar potential's vev becomes global minimum.
-As the sectors cool down their scalar potentials may change, producing a new global vev at which the symmetry will break by an induced phase transition.
-Depending on the characteristics of the symmetry breaking, the phase transition may be strongly first ordered (SFOPT).
+Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
+This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{}.
 
-Once the temperature reaches the critical temperature the SFOPT will occur, at which bubbles of the new phase will start to nucleate.
-These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.
-These bubbles are discribed by the following Euclidean action
+In this work, we explore the possibility of having multiple decoupled hidden sectors.
+Large numbers of hidden sectors can solve the hierarchy problem as in the Dvali Redi model~\cite{Dvali:2009ne} or in the more recently explored Nnaturalness~\cite{Arkani-Hamed:2016rle} framework, or in the orbifold Higgs models (maybe?\cite{}).
+They can also be motivated by dark matter considerations (dynamical dark matter?
+others?).
 
-\begin{equation}
-S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg]
-\end{equation}
+Motivated by solutions to the hierachy problem, we consider hidden sectors with the same particle content as the Standard Model that have all dimensionless couplings (defined at some high scale) equal to those of the Standard Model.
+The only parameter that varies across sectors is the dimension two Higgs mass squared parameter.
+This simple ansatz can lead to very rich phenomenology and interesting gravitational wave spectra, but we stress that it is only a starting point for exploring the space of theories with multiple hidden sectors.
 
-Where the time component has been integrated out due to finite temperature effects.
-The system has solutions with a $O(3)$ symmetry.
-We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood.
-Some authors have used the chiral effective lagrangian to calculate a low energy thermalized potential for confining $SU(N)$ .
-
-The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
-A quantity that characterizes the strength of the PT is the ratio of the latent heat and energy density of radiation, at the time of nucleation,
-\begin{equation}
-\alpha = \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30}
-\end{equation}
-Assuming that there is a negligible amount of energy being dumped back into the SM radiation bath, which would cause significant reheating of $\rho_{\gamma}$, the latent heat of the PT $\epsilon$ should  approximately be the energy density of the hidden sector going through the PT.
-$g_{*}$ has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
-\begin{equation}
-g_{*} = g_{*,\gamma} + \sum_{i = 1}^{N} g_{*,i} (\xi_{i})^4
-\end{equation}
-It will be seen that for models with a significant number of hidden sectors, that the lack of substantial reheating in adjecent sectors will cause their respective $g_{*}$ corrections to become negligible, $g_{*} \approx g_{*,\gamma}$.
 \section{Particle Setup}
@@
 The left decay is the primary decay for standard sectors ($\langle H\rangle\neq 0$), with $f$ representing all possible fermions.
-The right decay occurs in exotic sectors ($\langle H\rangle = 0$)
+The right decay occurs in exotic sectors ($\langle H\rangle = 0$).
 }
@@
 $i = 0$ is the sector that possess the smallest vev and is thus ``our" SM sector.
-Finally, the parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one.
+\draftnote{Write an equation that shows how the vev scales with $i$.}Finally, the parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one.
 Within this work, we looked at variants on this sort of tuning including non-uniform distributions and clustered sector effects; these ideas are discussed in Sec.
@@
 Although this field can generically be either by bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$.
-Our focus is primarily the production of gravitational waves from multiple sectors: the shifting to a fermion reheaton doesn't change the scaling of the energy density of the exotic sectors and, as a result, is ignored in our analysis.
+Our focus is primarily the production of gravitational waves from multiple sectors: \draftnote{What does the following mean?} the shifting to a fermion reheaton doesn't change the scaling of the energy density of the exotic sectors  and, as a result, is ignored in our analysis.
 
@@
 
-Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we generalize our results to include the (rather unnatural) case where sectors are reheated ``randomly" as opposed to in relation to the higg's mass parameter.
+Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we generalize our results to include the (rather unnatural) case where sectors are reheated ``randomly" as opposed to in relation to the higgs mass parameter.
 This allows us to explore more general models with multiple dark sectors at a huge range of scales.
@@
 \end{equation}
-with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
+\draftnote{Should the first equation go like $1/m_h$ (not squared)?}with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
 
@@
 It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$.
-For sectors where this kinematic threshold is passed for charm quarks, contributions to cosmological observables can be safely ignored.
+\draftnote{Put an equation sketching how $m_f$ scales with $m_h$} For sectors where this kinematic threshold is passed for charm quarks, contributions to cosmological observables can be safely ignored.
 All in all, we end up with a decay width that scales as $\Gamma_{m_H^2<0} \sim 1/m_h^2$.
@@
 (\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$.
-As the Feynman diagram (Fig.
-\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, leading to a significantly lower energy density than the standard sectors.
+As the Feynman diagram (Fig.~\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, leading to a significantly lower energy density than the standard sectors.
 Both the decay width and energy density for these sectors scale as: $\Gamma_{m_H^2>0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2$.
 
-As a final note, the reheating temperature, $T_{RH}$, has an upper bound on the order of the weak scale.
+As a final note, the reheating temperature, $T_{RH}$, \draftnote{What is this parameter exactly?
+The reheat temperature of the SM?
+Also, is this effect discussed in the original NNaturalness paper?} has an upper bound on the order of the weak scale.
 If this bound is not observed, the SM Higgs mass would have major thermal corrections --- leading to the branching ratios into other sectors being problematically large.
@@
 
-As mentioned in the previous sections, for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$.
+As mentioned in the previous sections,\draftnote{refer to a particular equation} for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$.
 This leads to increasingly heavy particle spectra for higher sectors --- eventually leading to sectors that are essentially pure Yang-Mills that featuring strong first order phase transitions.
@@
 at the energy scale we're interested in.
-$\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a standard model value.
+$\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a standard model value \draftnote{what is that value?}.
 Rewriting Eq.
@@
 The critical index demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
-Looking back to the description of reheating within $N$naturalness, we see the energy density of these sectors is at most $10^{-4}$ that of our sector.
-As a result, the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.
+Looking back to the description of reheating \draftnote{refer to a particular equation} within $N$naturalness, we see the energy density of these sectors is at most $10^{-4}$ \draftnote{why not $10^{-3}$?} that of our sector.
+As a result, \draftnote{As we will show below?} the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.
 
@@
 From Eq.
-(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector --- the maximum possible given a $10^{16}$ limit \cite{Arkani-Hamed:2016rle} of sectors is $\sim 38 \,\gev$.
+(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector --- the maximum possible given a $10^{16}$ limit \cite{Arkani-Hamed:2016rle} \draftnote{Is this actually an upper value of $m_H^2$ at the gut scale?} of sectors is $\sim 38 \,\gev$.
 After imposing $N_{eff}$ constraints (as in Sec.
@@
 It is important to note that these type of sectors mimic the general behaviour of any Yang-Mills like multi dark sector model.
+\draftnote{What does this sentence mean?
+Are there references that should appear here?}
 
@@
 
-In every exotic sector the fermion masses are exceptionally light: even the most massive quark of each sector is orders of magnitude smaller than our confinement scale, $m_t \ll \Lambda_{QCD}$.
-Additionally, since $m_q \propto 1/(m^2_H)_i$ this separation only becomes more pronounced as we move to sectors further from our own.
-The scale of the exotic quarks makes it unnecessary to run down the scale of the strong coupling as done for the standard sectors --- the phase transition for all exotic sectors occurs at $\sim 90 \,\mathrm{MeV}$ and a strong first order phase transition occurs for all exotic sectors at this temperature.
+In every exotic sector the fermion masses are exceptionally light: their masses are generated by dimension six operators with the Higgs integrated out as show in \draftnote{cite an equation from before}, and are therefore all below the confinement scale.
+The exotic sectors all have identical one-loop running of the QCD gauge coupling, and thus all have approximately the same confinement scale given by $\Lambda_{\rm ex} \sim 90 \,\mathrm{MeV}$.
+These sectors all have six light fermions, so a strong first order phase transition occurs for all exotic sectors at this temperature.
 
-The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6) \,\times$ SU$(6) \rightarrow\,$ SU$(6)$.
-This leads to the production of 35 pseudo-Goldstone bosons during the phase transition.
+The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6) \,\times$ SU$(6) \rightarrow\,$ SU$(6)$ and thus 35 pseudo-Goldstone bosons.
 These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
@@
 
-The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation \cite{Schwartz:2013pla},
+The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation \draftnote{Also cite Gell-Mann et al} \cite{Schwartz:2013pla},
 \begin{equation}\label{eqn:gmor}
@@
 \end{equation}
-Ultimately, calculating the critical phase transition strength for each sector using Eq.
+\draftnote{What are $m_a^i$?
+Is this the right formula,isn't $V$ and $f_\pi$ different from the SM to the $i$th exotic sector?
+Also, how do you compute $\Delta m$ when you have a different set of particles inside (pions) as outside (quarks) the bubble?
+} Ultimately, calculating the critical phase transition strength for each sector using Eq.
 (\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
@@
 
-The SM predicts that $N^{SM}_{eff} = 3.046$ \cite{Mangano:2005cc}.
+\draftnote{This is not the physics described in the previous paragraph} The SM predicts that $N^{SM}_{eff} = 3.046$ \cite{Mangano:2005cc}.
 This is in good agreement with bounds from studies of the Cosmic Microwave Background (CMB) by Planck combined with bayon acoustic oscillations (BAO) measurements \cite{Aghanim:2018eyx}:
@@
 \end{equation}
+\draftnote{Are these $1\sigma$? Maybe show the 95\% interval instead?}
 Various different assumptions about the history of the universe can be made and different data sets can be chosen to obtain slightly different results \cite{Breitbach:2018ddu} --- for the purposes of this exploratory work, wading through this landscape is unnecessary.
 
-For fully decoupled sectors that never enters (or reenters) thermal equilibrium with our sector, we obtain additional contributions to $N^{SM}_{eff}$ \cite{Breitbach:2018ddu}
+For fully decoupled sectors that never enter (or reenter) thermal equilibrium with our sector, we obtain additional contributions to $N^{SM}_{eff}$ \cite{Breitbach:2018ddu}
 \begin{equation}\label{eqn:DeltaNeff1hs}
@@
 Contours for Eq.
-(\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.
-\ref{fig:Neff}.
+(\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:Neff}.
 We take this approach and generalize it to include many additional sectors:
@@
 
-As Fig.
-\ref{fig:Neff} demonstrates, sectors with a temperature ratio above $\xi_h\sim 0.5$ with even a couple of relativist particles are immediately excluded by CMB constraints.
+As Fig.~\ref{fig:Neff} \draftnote{Why is it figure V?} demonstrates, sectors with a temperature ratio above $\xi_h\sim 0.5$ with even a couple of relativistic particles are immediately excluded by CMB constraints.
 Accordingly, the additional sectors present in this project must be heated to a much smaller fraction of our own sector's temperature.
+\draftnote{$\xi=0.5$ and $g=2$ is not excluded.}
 
@@
 After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom.
-Since all additional sectors are colder than our own by the time photon decoupling occurs ($\sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.
-(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector.
+Since all additional sectors are colder than our own \draftnote{Aren't they always colder than our own?} by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.
+(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector \draftnote{From photons and neutrinos?
+What about $\Delta N_{eff}$ constraints from BBN?
+This would be a much higher (SM) temperature.} .
 
@@
 Assuming a reheating temperature of $100$ GeV and a completely uniform distribution of sectors, the temperature of the first exotic sector is slightly more than $6\%$ of our sector at reheating.
-Applying Eq.
-(\ref{eqn:DeltaNeff}) to this particular situation gives us:
+Applying Eq.~(\ref{eqn:DeltaNeff}) to this particular situation gives us:
 \begin{equation}
-\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{0.06}{i^2}\right)^4.
+\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{0.06}{i^2}\right)^4 \sim 10^{-4}.
 \end{equation}     
-Summing over all sectors (sectors above $i \sim 10$ essentially don't contribute due to the small temperature ratios) gives us a contribution of $\mathcal{O} (10^{-4})$.
+\draftnote{Where does the $0.06$ come from?} This is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$.
 Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.
@@
 \ref{sec:signals}.
+\draftnote{This assumes that only photons and neutrinos are relativistic?}
 
-\section{Signals}
-\label{sec:signals}
+\section{Gravitational Wave Signals}
+
+\label{sec:gw}
+Sectors other than the SM can be reheated through multifield inflationary theories, Reheaton models, etc.
+In these models, the SM will receive the majority of the energy density while the remaining energy density will be distributed, in a model dependent way, to the various hidden sectors.
+If there does not exist a portal between the sectors, they will remain decoupled and evolve independently.
+When looking at multiple thermally decoupled hidden sectors it is convienent to define the temperature ratio [cite cold,dark,noisy]
+\begin{equation}
+\xi_i \equiv  \frac{T_{i}}{T_{\gamma}}
+\end{equation}
+Where $T_{i}$ is the temperature of the $i^{th}$ hidden sector, and $T_{\gamma}$ the temperature of the standard model (assuming radiation domination).
+
+\vspace{1em }
+- first order phase transitions ( strength, scale, origin)
+Right after reheating, the temperatures of the respective sectors are high leading to restoration of a given sector's symmetry.
+An example being the SM's $SU(3) \times SU(2) \times U(1)$ symmetry being restored as the scalar potential's vev becomes global minimum.
+As the sectors cool down their scalar potentials may change, producing a new global vev at which the symmetry will break by an induced phase transition.
+Depending on the characteristics of the symmetry breaking, the phase transition may be strongly first ordered (SFOPT).
+
+Once the temperature reaches the critical temperature the SFOPT will occur, at which bubbles of the new phase will start to nucleate.
+These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.
+These bubbles are discribed by the following Euclidean action
+
+\begin{equation}
+S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg]
+\end{equation}
+
+Where the time component has been integrated out due to finite temperature effects.
+The system has solutions with a $O(3)$ symmetry.
+We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood.
+Some authors have used the chiral effective lagrangian to calculate a low energy thermalized potential for confining $SU(N)$ .
+
+The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
+A quantity that characterizes the strength of the PT is the ratio of the latent heat and energy density of radiation, at the time of nucleation,
+\begin{equation}
+\alpha = \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30}
+\end{equation}
+\draftnote{What is $\epsilon$?} Assuming that there is a negligible amount of energy being dumped back into the SM radiation bath, which would cause significant reheating of $\rho_{\gamma}$, the latent heat of the PT $\epsilon$ should  approximately be the energy density of the hidden sector going through the PT.
+$g_{*}$ has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
+\begin{equation}
+g_{*} = g_{*,\gamma} + \sum_{i = 1}^{N} g_{*,i} (\xi_{i})^4
+\end{equation}
+It will be seen that for models with a significant number of hidden sectors, that the lack of substantial reheating in adjecent sectors will cause their respective $g_{*}$ corrections to become negligible, $g_{*} \approx g_{*,\gamma}$.
+
+%\section{Signals}
+%\label{sec:signals}
 \begin{figure*}[tb]
@@
 With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$.
-\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves.
+\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ \draftnote{Define $\beta$ somewhere} enhanced gravitational waves.
 With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
@@
 \end{itemize}
-The total gravitational wave power spectrum is a linear combination of the three contributions,
+The total gravitational wave power spectrum \draftnote{Is $\Omega$ really a power spectrum? Isn't just an energy density?} is a linear combination of the three contributions,
 \begin{equation}
@@
 
-Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
+\draftnote{Define $g_*$} Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
 In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$.
 As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{GW}^{*}(f)$, will redshift to today's value $\Omega_{GW}^{0}(f) = \mathcal{A}\, \Omega_{GW}^{*}((a_{0}/a) f) $.
-Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,
+\draftnote{Define $\mathcal{A}$} Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,
 
@@
 As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
-This is seen in figures [], where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
+This is seen in figures \ref{}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
 The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).

### 2019-08-17 gwnnDraft02.tex
Dealt with suggested edits

@@
 $i = 0$ is the sector that possess the smallest vev and is thus ``our" SM sector.
-\draftnote{Write an equation that shows how the vev scales with $i$.}Finally, the parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one.
+\textcolor{green}{Write an equation that shows how the vev scales with $i$.} The vev for each standard sector is given explicitly by
+\begin{equation}\label{eqn:vevs}
+v^i = m^i_H/\sqrt{\lambda_i} = \sqrt{\frac{2i + r}{N}}\left(\frac{\Lambda_H}{\lambda}\right),
+\end{equation}
+$\lambda_i$ is the quartic coefficient of the scalar potential and is the same across all sectors.
+The parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one.
 Within this work, we looked at variants on this sort of tuning including non-uniform distributions and clustered sector effects; these ideas are discussed in Sec.
-\ref{sec:signals}.
+\ref{sec:gw}.
 
 As mentioned above, half of all sectors in this model feature a Higgs mass parameter such that $m_H^2 < 0$.
-These sectors feature electroweak symmetry breaking just like in the SM, however the vevs produced scale with the changing mass parameter: $v_i \sim v\sqrt{i}$.
-As the masses for particles in these sectors scale with the vev, this leads to the masses of particles within each sector strictly increasing with $i$.
+These sectors feature electroweak symmetry breaking just like in the SM, however the vevs produced scale with the changing mass parameter: $v_i \sim v\sqrt{i}$ (explicitly demonstrated in Eq.~(\ref{eqn.vevs}) As the masses for particles in these sectors scale with the vev, this leads to the masses of particles within each sector strictly increasing with $i$.
 The consequences of this on the QCD of $i \geq 1$ sectors is further discussed in Sec.
@@
 As a result, fermion masses are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet.
-This leads to very light fermions: $m_f \sim y_f y_t \Lambda_{QCD}^3/(m^2_H)_i \leq 100$ eV, with $y_f$ representing the Yukawa coupling to fermion $f$.
+This leads to very light fermions:
+\begin{equation}\label{eqn:exoticFM}
+m_f \sim y_f y_t \Lambda_{QCD}^3/(m^2_H)_i \leq 100 \,\ev,
+\end{equation}
+with $y_f$ representing the Yukawa coupling to fermion $f$.
 The extremely light quarks that appear in these sectors dramatically change the nature of the QCD phase transition --- unlike the SM, the transition is strongly first order.
@@
 This is the physical signature we're interested in exploring within this paper; the calculation and results are presented in Sec.
-\ref{sec:signals}.
+\ref{sec:gw}.
 
@@
 Although this field can generically be either by bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$.
-Our focus is primarily the production of gravitational waves from multiple sectors: \draftnote{What does the following mean?} the shifting to a fermion reheaton doesn't change the scaling of the energy density of the exotic sectors  and, as a result, is ignored in our analysis.
+Our focus is primarily the production of gravitational waves from multiple sectors: \textcolor{yellow}{What does the following mean?} a fermion reheaton doesn't change the scaling of the energy density of the exotic sectors and thus doesn't affect expected gravitational wave profiles.
 
@@
 \end{equation}
-\draftnote{Should the first equation go like $1/m_h$ (not squared)?}with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
+\textcolor{green}{Should the first equation go like $1/m_h$ (not squared)?
+It does --- v scales identically to $m_h$}with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
 
@@
 The loop decay of $\phi \rightarrow \gamma\gamma$ is always sub-leading and can be neglected.
-It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$.
-\draftnote{Put an equation sketching how $m_f$ scales with $m_h$} For sectors where this kinematic threshold is passed for charm quarks, contributions to cosmological observables can be safely ignored.
+It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions ($m_f \sim v_i \sim v_{us}\sqrt{i}$) eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$.
+\textcolor{green}{Put an equation sketching how $m_f$ scales with $m_h$} For sectors where this kinematic threshold is passed for charm quarks, contributions to cosmological observables can be safely ignored.
 All in all, we end up with a decay width that scales as $\Gamma_{m_H^2<0} \sim 1/m_h^2$.
-Since we can expect energy density to be proportional to the decay width, $\frac{\rho_i}{\rho_{SM}} \approx \frac{\Gamma_i}{\Gamma_{SM}}$, this indicates that energy density of standard sectors falls proportional to $1/i$.
+Since we can expect energy density to be proportional to the decay width, $\frac{\rho_i}{\rho_{SM}} \approx \frac{\Gamma_i}{\Gamma_{SM}}$, this indicates that energy density of standard sectors falls:
+\begin{equation}\label{eqn:edSS}
+\rho_i \sim \frac{\rho_{SM}}{i}.
+\end{equation}
 
@@
 
-As a final note, the reheating temperature, $T_{RH}$, \draftnote{What is this parameter exactly?
+As a final note, the reheating temperature of our sector, $T_{RH}$, \textcolor{yellow}{What is this parameter exactly?
 The reheat temperature of the SM?
-Also, is this effect discussed in the original NNaturalness paper?} has an upper bound on the order of the weak scale.
-If this bound is not observed, the SM Higgs mass would have major thermal corrections --- leading to the branching ratios into other sectors being problematically large.
+Also, is this effect discussed in the original NNaturalness paper?
+Yes to both.} has an upper bound on the order of the weak scale.
+If this bound is not observed, the SM Higgs mass would have major thermal corrections --- leading to the branching ratios into other sectors being problematically large \citep{Arkani-Hamed:2016rle}.
 In accordance with this restriction, this project only examines reheating temperatures at or below $100$ GeV.
@@
 
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.45\textwidth]{critIndex.png}
-
-%\hfill
-%\caption{Critical index $i$ as a function of slop factor. 
-%}
-%\label{fig:critIndex}
-%\end{figure}
-
-As mentioned in the previous sections,\draftnote{refer to a particular equation} for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$.
+As mentioned in the previous sections (see Eq.~(\ref{eqn:vevs})),\textcolor{green}{refer to a particular equation} for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$.
 This leads to increasingly heavy particle spectra for higher sectors --- eventually leading to sectors that are essentially pure Yang-Mills that featuring strong first order phase transitions.
@@
 at the energy scale we're interested in.
-$\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a standard model value \draftnote{what is that value?}.
-Rewriting Eq.
-(\ref{eqn:lambda2}) in terms of standard model variables,
+$\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a standard model value of $\Lambda^{(6)}_{MS} =(89 \pm 6)\, \mev$\cite{PhysRevD.98.030001}\textcolor{green}{what is that value?}.
+Rewriting Eq.~(\ref{eqn:lambda2}) in terms of standard model variables,
 \begin{equation}\label{eqn:lambda2adj}
@@
 The critical index demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
-Looking back to the description of reheating \draftnote{refer to a particular equation} within $N$naturalness, we see the energy density of these sectors is at most $10^{-4}$ \draftnote{why not $10^{-3}$?} that of our sector.
-As a result, \draftnote{As we will show below?} the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.
+Looking back to the energy density scaling in Eq.~(\ref{eqn:edSS})\textcolor{green}{refer to a particular equation} we see that, within the context of $N$naturalness, the energy density of these sectors is at most $10^{-4}$ \textcolor{red}{why not $10^{-3}$?} that of our sector.
+As a result, \textcolor{red}{As we will show below?} the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.
 
@@
 These sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
-From Eq.
-(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector --- the maximum possible given a $10^{16}$ limit \cite{Arkani-Hamed:2016rle} \draftnote{Is this actually an upper value of $m_H^2$ at the gut scale?} of sectors is $\sim 38 \,\gev$.
+From Eq.~(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector --- the maximum possible given a $10^{16}$ limit \cite{Arkani-Hamed:2016rle} \textcolor{yellow}{Is this actually an upper value of $m_H^2$ at the gut scale?
+The more sectors added in, the lower the scale of strong gravitational coupling.
+With more sectors than $10^16$, the top sectors start having vevs higher than the gravitational scale} of sectors is $\sim 38 \,\gev$.
 After imposing $N_{eff}$ constraints (as in Sec.
@@
 The signals of this sector and other test cases like it are explored in Sec.
-\ref{sec:signals}.
-It is important to note that these type of sectors mimic the general behaviour of any Yang-Mills like multi dark sector model.
-\draftnote{What does this sentence mean?
-Are there references that should appear here?}
+\ref{sec:gw}.
 
@@
 
-In every exotic sector the fermion masses are exceptionally light: their masses are generated by dimension six operators with the Higgs integrated out as show in \draftnote{cite an equation from before}, and are therefore all below the confinement scale.
+In every exotic sector the fermion masses are exceptionally light: their masses are generated by dimension six operators with the Higgs integrated out as shown in Eq.~(\ref{eqn:exoticFM}) \textcolor{green}{cite an equation from before}, and are therefore all below the confinement scale.
 The exotic sectors all have identical one-loop running of the QCD gauge coupling, and thus all have approximately the same confinement scale given by $\Lambda_{\rm ex} \sim 90 \,\mathrm{MeV}$.
@@
 
-The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation \draftnote{Also cite Gell-Mann et al} \cite{Schwartz:2013pla},
+The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation \textcolor{green}{Also cite Gell-Mann et al} \cite{Gell-Mann,Schwartz:2013pla},
 \begin{equation}\label{eqn:gmor}
@@
 \end{equation}
-\draftnote{What are $m_a^i$?
+\textcolor{red}{What are $m_a^i$?
 Is this the right formula,isn't $V$ and $f_\pi$ different from the SM to the $i$th exotic sector?
 Also, how do you compute $\Delta m$ when you have a different set of particles inside (pions) as outside (quarks) the bubble?
-} Ultimately, calculating the critical phase transition strength for each sector using Eq.
-(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+} Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
 Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.
@@
 \includegraphics[width=0.45\textwidth]{neff.png}
-\label{fig:Neff}
 \hfill
@@
 }
+\label{fig:neff}
 \end{figure}
@@
 The presence of these particles can have two main effects: extra relativistic particles can alter the expansion history of the universe through changes to the energy density or hidden sectors can feature annihilations that reheat the photons or neutrinos of our sector near Big Bang Nucleosynthesis (BBN) and affect the light element abundances.
-The effective number of neutrino species, $N_{eff}$, describes these contributions and, as such, is the strictest constraint that must be dealt with when studying these type of multi-phase transition models.
+The effective number of neutrino species, $N_{eff}$, is impacted by these contributions and, as such, is the strictest constraint that must be dealt with when studying these type of multi-phase transition models.
 
-\draftnote{This is not the physics described in the previous paragraph} The SM predicts that $N^{SM}_{eff} = 3.046$ \cite{Mangano:2005cc}.
+\textcolor{yellow}{This is not the physics described in the previous paragraph} The SM predicts that $N^{SM}_{eff} = 3.046$ \cite{Mangano:2005cc}.
 This is in good agreement with bounds from studies of the Cosmic Microwave Background (CMB) by Planck combined with bayon acoustic oscillations (BAO) measurements \cite{Aghanim:2018eyx}:
@@
 \end{equation}
-\draftnote{Are these $1\sigma$? Maybe show the 95\% interval instead?}
+\textcolor{green}{Are these $1\sigma$? Maybe show the 95\% interval instead?These are $2\sigma$}
 Various different assumptions about the history of the universe can be made and different data sets can be chosen to obtain slightly different results \cite{Breitbach:2018ddu} --- for the purposes of this exploratory work, wading through this landscape is unnecessary.
@@
 Contours for Eq.
-(\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:Neff}.
+(\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:neff}.
 We take this approach and generalize it to include many additional sectors:
@@
 
-As Fig.~\ref{fig:Neff} \draftnote{Why is it figure V?} demonstrates, sectors with a temperature ratio above $\xi_h\sim 0.5$ with even a couple of relativistic particles are immediately excluded by CMB constraints.
+As Fig.~\ref{fig:neff} \textcolor{green}{Why is it figure V?} demonstrates, sectors with a temperature ratio above $\xi_h\sim 0.6$ with even a couple of relativistic particles are immediately excluded by CMB constraints.
 Accordingly, the additional sectors present in this project must be heated to a much smaller fraction of our own sector's temperature.
-\draftnote{$\xi=0.5$ and $g=2$ is not excluded.}
+\textcolor{green}{$\xi=0.5$ and $g=2$ is not excluded.}
 
@@
 After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom.
-Since all additional sectors are colder than our own \draftnote{Aren't they always colder than our own?} by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.
-(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector \draftnote{From photons and neutrinos?
+Since all additional sectors are colder than our own \textcolor{yellow}{Aren't they always colder than our own?
+Yes, they are.} by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.~(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector \textcolor{red}{From photons and neutrinos?
 What about $\Delta N_{eff}$ constraints from BBN?
@@
 \begin{equation}
-\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{0.06}{i^2}\right)^4 \sim 10^{-4}.
+\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{(T_{RH_{E1}}/T_{RH})}{i^2}\right)^4 \sim 10^{-4},
 \end{equation}     
-\draftnote{Where does the $0.06$ come from?} This is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$.
+with $T_{RH_{E1}}/T_{RH}$ being the ratio of the reheat temperatures of the 1st exotic sector and our own sector ($0.06$ in standard $N$naturalness with $r = 1$).
+\textcolor{green}{Where does the $0.06$ come from?} This is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$.
 Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.
@@
 
-Since $N_{eff}$ constraints remain our strongest cosmological bounds for massive standard sectors, our starting point for exploring the limits of high transition temperatures is Eq.
-(\ref{eqn:DeltaNeff}).
-Assuming heavy, standard sectors we can saturate the bounds of Eq.
-(\ref{eqn:NeffBounds}) and solve for the maximum energy density allowed for any number of sectors:
+Since $N_{eff}$ constraints remain our strongest cosmological bounds for massive standard sectors, our starting point for exploring the limits of high transition temperatures is Eq.~(\ref{eqn:DeltaNeff}).
+Assuming heavy, standard sectors (with the only relativistic particles being photons and neutrinos) we can saturate the bounds of Eq.~(\ref{eqn:NeffBounds}) and solve for the maximum energy density allowed for any number of sectors:
 \begin{equation}\label{eqn:energyDensityAllowed}
@@
 Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own.
-In terms of the $N$naturalness framework, this consisted of looking at various different sectors above the critical index, as mentioned in Sec.
-\ref{sec:dQCD}.
-The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are shown in Sec.
-\ref{sec:signals}.
-\draftnote{This assumes that only photons and neutrinos are relativistic?}
+In terms of the $N$naturalness framework, this consisted of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}.
+The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are shown in Sec.~\ref{sec:gw}.
+\textcolor{yellow}{This assumes that only photons and neutrinos are relativistic?
+Yes.}
 

### 2019-08-19 gwnnDraft02.tex
Fixed red comments

@@
 The loop decay of $\phi \rightarrow \gamma\gamma$ is always sub-leading and can be neglected.
-It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions ($m_f \sim v_i \sim v_{us}\sqrt{i}$) eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$.
+It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions ($m_f \sim v_i \sim v_{SM}\sqrt{i}$) eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$.
 \textcolor{green}{Put an equation sketching how $m_f$ scales with $m_h$} For sectors where this kinematic threshold is passed for charm quarks, contributions to cosmological observables can be safely ignored.
@@
 \begin{equation}\label{eqn:edSS}
-\rho_i \sim \frac{\rho_{SM}}{i}.
+\rho_i \sim r_{s}\frac{\rho_{SM}}{i}
 \end{equation} 
+with $r_s$ being the ratio of the energy density of the first additional standard sector over the energy density of our sector.
 
@@
 The critical index demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
-Looking back to the energy density scaling in Eq.~(\ref{eqn:edSS})\textcolor{green}{refer to a particular equation} we see that, within the context of $N$naturalness, the energy density of these sectors is at most $10^{-4}$ \textcolor{red}{why not $10^{-3}$?} that of our sector.
-As a result, \textcolor{red}{As we will show below?} the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.
+Looking back to the energy density scaling in Eq.~(\ref{eqn:edSS})\textcolor{green}{refer to a particular equation} we see that, within the context of $N$naturalness, the energy density of these sectors is at most $10^{-4}$ \textcolor{green}{why not $10^{-3}$?} that of our sector.
+As a result, \textcolor{green}{As we will show below?} the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.
 
@@
 \end{equation}
-where $V \sim \Lambda_{QCD}$, $F_\pi$ is the pion decay constant. So, for mesons in exotic sector $i$:
+where $V \sim \Lambda_{QCD}$, $F_\pi$ is the pion decay constant.
+One expects that within a given sector $F_\pi \sim V \sim \Lambda_{QCD}$ \cite{Schwartz:2013pla} and as exotic sectors have $\Lambda_{ex} \sim 90 \,\mev$ while the SM features $\Lambda_{QCD} = (332\pm17)\,\mev$ \cite{PhysRevD.98.030001} we expect at most $\mathcal{O}(1)$ difference in the $\sqrt{\frac{V^3}{F_\pi^2}}$ coefficient between sectors.
+So, for mesons in exotic sector $i$:
 \begin{equation}
-m_{\pi}^i \sim \sqrt{\frac{m_1^i+m_2^i}{m_u + m_d}} m_{\pi}.
+m_{\pi}^i \sim \sqrt{\frac{m_a^i+m_b^i}{m_a + m_b}} m_{\pi}.
 \end{equation}
-\textcolor{red}{What are $m_a^i$?
+Here, $a$ and $b$ denote the component quark flavours.
+It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.
+\textcolor{green}{What are $m_a^i$?
 Is this the right formula,isn't $V$ and $f_\pi$ different from the SM to the $i$th exotic sector?
 Also, how do you compute $\Delta m$ when you have a different set of particles inside (pions) as outside (quarks) the bubble?
-} Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+}
+
+Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
 Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.
@@
 Since we're more interested in a more general scenario with multiple dark phase transitions, we focus in on whether zero vev sectors can dodge these $N_{eff}$ bounds.
+Additionally,
+\begin{equation}
+\frac{(\Delta N^i_{eff})_{CMB}}{(\Delta N^i_{eff})_{BBN}} \geq 1
+\end{equation}
+for any sector $i$ \cite{Arkani-Hamed:2016rle}.
+Because the constraints on $N_{eff}$ are stronger at photon decoupling than at BBN, we can focus purely on the constraints provided by the former \cite{Aghanim:2018eyx}.
 
@@
 Since all additional sectors are colder than our own \textcolor{yellow}{Aren't they always colder than our own?
-Yes, they are.} by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.~(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector \textcolor{red}{From photons and neutrinos?
+Yes, they are.} by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.~(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector \textcolor{green}{From photons and neutrinos?
 What about $\Delta N_{eff}$ constraints from BBN?

### 2019-08-19 gwnnDraft02.tex
more intro

@@
 Motivated by solutions to the hierachy problem, we consider hidden sectors with the same particle content as the Standard Model that have all dimensionless couplings (defined at some high scale) equal to those of the Standard Model.
-The only parameter that varies across sectors is the dimension two Higgs mass squared parameter.
+The only parameter that varies across sectors is the dimension two Higgs mass squared parameter, $m_H^2$.
 This simple ansatz can lead to very rich phenomenology and interesting gravitational wave spectra, but we stress that it is only a starting point for exploring the space of theories with multiple hidden sectors.
+
+In this setup, there are two qualitatively different kinds of sectors:
+\begin{itemize}
+\item \textbf{Standard Sectors}: Those with $m_H^2 < 0$ where electroweak symmetry is broken by the vacuum expectation value (VEV) of a fundamental scalar.
+As in~\cite{Arkani-Hamed:2016rle}, we assume that the standard sector with the smallest absolute value of $m_H^2$ is the Standard Model.
+\item \textbf{Exotic Sectors}: Those with  $m_H^2 > 0$. In this case, electroweak symmetry breaking is preserved below the mass of the Higgs, and broken by the confinement of QCD~\cite{}.
+\end{itemize}
+Cosmological observations, particularly limits on extra relativistic degrees of freedom at the time of Big Bang Nucleosynthesis~\cite{} and the time fo the formation of the cosmic microwave background (CMB)~\cite{}, require that most of the energy in the universe is in the Standard Model sector as we will quantify.
+Therefore, the hidden sectors cannot be in thermal equilibrium at any time, and the physics of reheating must dump energy preferentially in the Standard Model sector.
+This can be accomplished in multifield inflation models~\cite{} and with the reheaton method~\cite{Arkani-Hamed:2016rle}.
+We will also explore alternative parameterizations of reheating that satisfy this condition.
+
+In all the above models, there is some energy in the hidden sectors, and these sectors undergo thermal evolution independent of the SM sector.
+If their initial reheating temperature is above their weak scale, the standard sectors will undergo phase transitions associated with the breaking of electroweak symmetry and with confinement of QCD.
+The exotic sectors will also undergo a phase transition when QCD confines and electroweak symmetry is broken simultaneously.
+The condition for these transitions to leave imprints on the stochastic gravitational wave spectrum is that they strongly first order phase transitions (SFOPT)~\cite{}.
+This does not occur at either the electroweak or QCD phase transition in the SM, but as we will show, it does happen in some standard sectors, and in \textit{all} exotic sectors that reheat above the QCD phase transition.
+
+This work is organized as follows...
 
@@
 
-Beginning with the work of Pedro Schwaller \cite{Schwaller:2015tja} and continuing through the work of many others \cite{everyoneelse}, strong first order phase transitions for SU(N) dark sectors with arbitrary numbers of flavours have been explored as a source of gravitational waves.
+%Beginning with the work of Pedro Schwaller \cite{Schwaller:2015tja} and continuing through the work of many others \cite{everyoneelse}, strong first order phase transitions for SU(N) dark sectors with arbitrary numbers of flavours have been explored as a source of gravitational waves.
 Here, we look to generalize this study to include classes of models that feature multiple dark sectors that undergo gravitational wave producing phase transitions.
@@
 
-\subsection{NNaturalness}
+%\subsection{NNaturalness}
+
+We consider the following Lagrangian as in~\cite{Arkani-Hamed:2016rle}:
+\begin{equation}
+{\cal L} = \sum_{i=-N/2}^{N/2} {\cal L}_i,
+\end{equation}
+with ${\cal L}_0 = {\cal L}_{\rm SM}$ being the Standard Model Lagrangian, and ${\cal L}_i$ being a copy of the SM Lagrangian with different fields, but with all dimensionless parameters the same.
+Each of the Lagrangians does contain a dimension operator:
+\begin{equation}
+{\cal L}_i \subset  - \left(m_H^2\right)_i H_i^\dagger H_i  
+\end{equation}
+where $H_i$ is a Higgs field in each sector, and the mass term is parametrically given by
+\begin{equation}\label{eqn:massParam}
+\left(m_H^2\right)_i \sim -\frac{\Lambda_H^2}{N}(2i+r),
+\end{equation}
+where $\Lambda$ is some high scale cutoff, $N$ is the number of sectors, and $r$ mass parameter in the SM in units of $\Lambda_H^2/N$.
+This setup solves the hierarchy problem if $r \sim \mathcal{O}(1)$\footnote{Constraints require $r$ to be somewhat smaller than 1.} and we the Higgs masses in the different sectors as randomly distributed~\cite{Arkani-Hamed:2016rle}.
+We have taken for simplicity that there equal numbers sectors with positive and negative $m_H^2$, but this is not nessesary.
+This Nnaturalness framework can be generalized: the various sectors can possess a wide range of particle content that can be freely selected by the model builder.
+The one exception to this is that ``our" sector must consist of the Standard Model.
+
+From the above Lagrangians, the Higgs in sectors with $i \geq 0$ will get a vev given by:
+\begin{equation}\label{eqn:vevs}
+v^i = m^i_H/\sqrt{\lambda_i} ~ \sqrt{\frac{2i + r}{N}}\left(\frac{\Lambda_H}{\lambda}\right),
+\end{equation}
+$\lambda_i$ is the quartic coefficient of the scalar potential and is the same across all sectors. 
+%The parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one.
+Within this work, we looked at variants on this sort of tuning including non-uniform distributions and clustered sector effects; these ideas are discussed in Sec.
+\ref{sec:gw}.
+%
+%
+%
+%
+%$N$naturalness is a model framework that looks to solve the hierarchy problem through the introduction of $N$ mutually non-interacting sectors \cite{Arkani-Hamed:2016rle}.
+The framework itself is very general: the various sectors can possess a wide range of particle content that can be freely selected by the model builder.
+The one exception to this is that ``our" sector must consist of the Standard Model.
+For simplicity, the original paper takes all additional new sectors to be copies of the SM (with the same gauge groups and Yukawa structure); however the Higgs mass parameters of each sector are allowed to taken on values distributed between $-\Lambda_H^2$ and $\Lambda^2_H$, with $\Lambda_H$ being the scale that cuts off quadratic divergences.
+%
+%This construction leads to sectors that are automatically accidentally tuned to the $1/N$ level, leading to a sector with a mass parameter $m_H^2 \sim \Lambda_H^2/N$.
+The sector with the smallest non-zero vacuum expectation value (vev) as ``our" sector --- the SM sector.
+It should be noted that the values of $m_H^2$ pass through zero, resulting in effectively 2 types of sectors: ``standard" sectors like our own with a negative Higgs mass parameter squared, possess a vev, and exhibit electroweak symmetry breaking and ``exotic" sectors with a positive Higgs mass parameter squared that thus feature no electroweak symmetry breaking and a zero vev.
+%
+%Keeping with the original convention, we write our mass parameter as
+%\begin{equation}\label{eqn:massParam}
+%\left(m_H^2\right)_i = -\frac{\Lambda_H^2}{N}(2i+r),
+%\end{equation}
+%where $i$ denotes the sector ($-\frac{N}{2}\leq i \leq \frac{N}{2}$).
+$i = 0$ is the sector that possess the smallest vev and is thus ``our" SM sector.
+\textcolor{green}{Write an equation that shows how the vev scales with $i$.} The vev for each standard sector is given explicitly by
+%\begin{equation}\label{eqn:vevs}
+%v^i = m^i_H/\sqrt{\lambda_i} = \sqrt{\frac{2i + r}{N}}\left(\frac{\Lambda_H}{\lambda}\right),
+%\end{equation}
+%$\lambda_i$ is the quartic coefficient of the scalar potential and is the same across all sectors.
+The parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one.
+Within this work, we looked at variants on this sort of tuning including non-uniform distributions and clustered sector effects; these ideas are discussed in Sec.
+\ref{sec:gw}.
+%
+%As mentioned above, half of all sectors in this model feature a Higgs mass parameter such that $m_H^2 < 0$. 
+These ``standard sectors'' feature electroweak symmetry breaking just like in the SM, however the vevs produced scale with the changing mass parameter: $v_i \sim v_{\rm SM}\sqrt{i}$.
+As the masses for particles in these sectors scale with the vev, this leads to the masses of the $W$, $Z$ and fermions within each sector increasing with $i$.
+The consequences of this on the confinement scale of QCD in the $i \geq 1$ sectors is further discussed in Sec.
+\ref{sec:dQCD}.
+
+The remaining ``exotic sectors'' within this model provide a radical departure from our own.
+$m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
+The mass of fundamental fermions are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet.
+This leads to very light fermions:
+\begin{equation}\label{eqn:exoticFM}
+m_f \sim y_f y_t \Lambda_{QCD}^3/(m^2_H)_i \leq 100 \,\ev,
+\end{equation}
+with $y_f$ representing the Yukawa coupling to fermion $f$.
+As we will see, the extremely light quarks that appear in these sectors dramatically change the nature of the QCD phase transition --- unlike the SM, the transition is strongly first order.
+Again, this is further developed in Sec.
+\ref{sec:dQCD}.
+Crucially, this results in the production of gravitational waves.
+This is the physical signature we're interested in exploring within this paper; the calculation and results are presented in Sec.
+\ref{sec:gw}.
+
+\subsection{Reheating N Sectors}
 
@@
 \end{figure*}
-
-$N$naturalness is a model framework that looks to solve the hierarchy problem through the introduction of $N$ mutually non-interacting sectors \cite{Arkani-Hamed:2016rle}.
-The framework itself is very general: the various sectors can possess a wide range of particle content that can be freely selected by the model builder.
-The one exception to this is that ``our" sector must consist of the Standard Model.
-For simplicity, the original paper takes all additional new sectors to be copies of the SM (with the same gauge groups and Yukawa structure); however the Higgs mass parameters of each sector are allowed to taken on values distributed between $-\Lambda_H^2$ and $\Lambda^2_H$, with $\Lambda_H$ being the scale that cuts off quadratic divergences.
-
-This construction leads to sectors that are automatically accidentally tuned to the $1/N$ level, leading to a sector with a mass parameter $m_H^2 \sim \Lambda_H^2/N$.
-The sector with the smallest non-zero vacuum expectation value (vev) as ``our" sector --- the SM sector.
-It should be noted that the values of $m_H^2$ pass through zero, resulting in effectively 2 types of sectors: ``standard" sectors like our own with a negative Higgs mass parameter squared, possess a vev, and exhibit electroweak symmetry breaking and ``exotic" sectors with a positive Higgs mass parameter squared that thus feature no electroweak symmetry breaking and a zero vev.
-
-Keeping with the original convention, we write our mass parameter as
-\begin{equation}\label{eqn:massParam}
-\left(m_H^2\right)_i = -\frac{\Lambda_H^2}{N}(2i+r),
-\end{equation}
-where $i$ denotes the sector ($-\frac{N}{2}\leq i \leq \frac{N}{2}$).
-$i = 0$ is the sector that possess the smallest vev and is thus ``our" SM sector.
-\textcolor{green}{Write an equation that shows how the vev scales with $i$.} The vev for each standard sector is given explicitly by
-\begin{equation}\label{eqn:vevs}
-v^i = m^i_H/\sqrt{\lambda_i} = \sqrt{\frac{2i + r}{N}}\left(\frac{\Lambda_H}{\lambda}\right),
-\end{equation}
-$\lambda_i$ is the quartic coefficient of the scalar potential and is the same across all sectors.
-The parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one.
-Within this work, we looked at variants on this sort of tuning including non-uniform distributions and clustered sector effects; these ideas are discussed in Sec.
-\ref{sec:gw}.
-
-As mentioned above, half of all sectors in this model feature a Higgs mass parameter such that $m_H^2 < 0$.
-These sectors feature electroweak symmetry breaking just like in the SM, however the vevs produced scale with the changing mass parameter: $v_i \sim v\sqrt{i}$ (explicitly demonstrated in Eq.~(\ref{eqn.vevs}) As the masses for particles in these sectors scale with the vev, this leads to the masses of particles within each sector strictly increasing with $i$.
-The consequences of this on the QCD of $i \geq 1$ sectors is further discussed in Sec.
-\ref{sec:dQCD}.
-
-The remaining sectors within this model provide a radical departure from our own.
-$m_H^2 > 0$ leads to no vev and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$.
-As a result, fermion masses are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet.
-This leads to very light fermions:
-\begin{equation}\label{eqn:exoticFM}
-m_f \sim y_f y_t \Lambda_{QCD}^3/(m^2_H)_i \leq 100 \,\ev,
-\end{equation}
-with $y_f$ representing the Yukawa coupling to fermion $f$.
-The extremely light quarks that appear in these sectors dramatically change the nature of the QCD phase transition --- unlike the SM, the transition is strongly first order.
-Again, this is further developed in Sec.
-\ref{sec:dQCD}.
-Crucially, this results in the production of gravitational waves.
-This is the physical signature we're interested in exploring within this paper; the calculation and results are presented in Sec.
-\ref{sec:gw}.
-
-\subsection{Reheating N Sectors}
 

### 2019-08-20 gwnnDraft02.tex
more signal

--- 2019-08-17 gwnnDraft02.tex
@@
 \usepackage{slashed}
+\usepackage{soul}
 \graphicspath{{./Figures/}}
@@
 \vspace{1em }
-- first order phase transitions ( strength, scale, origin)
 Right after reheating, the temperatures of the respective sectors are high leading to restoration of a given sector's symmetry.
@@
 These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.
-These bubbles are discribed by the following Euclidean action
+These bubbles are described by the following Euclidean action
 
@@
 \end{equation}
-\draftnote{What is $\epsilon$?} Assuming that there is a negligible amount of energy being dumped back into the SM radiation bath, which would cause significant reheating of $\rho_{\gamma}$, the latent heat of the PT $\epsilon$ should  approximately be the energy density of the hidden sector going through the PT.
+
+\begin{figure}[tb]
+\centering
+\includegraphics[scale=.3]{Nnatral.png} 
+\caption{ All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
+The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+\end{figure}
+
+\draftnote{\st{What is $\epsilon$?}} $\epsilon$ is the latent heat released during the phase transition, and is function of the scalar potential.
+Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  $\epsilon$ should approximately be equal to the energy density of the hidden sector going through the PT.
 $g_{*}$ has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
@@
 \end{equation}
-It will be seen that for models with a significant number of hidden sectors, that the lack of substantial reheating in adjecent sectors will cause their respective $g_{*}$ corrections to become negligible, $g_{*} \approx g_{*,\gamma}$.
+It will be seen that for models with a significant number of hidden sectors, that the lack of substantial reheating in adjacent sectors will cause their respective $g_{*}$ corrections to become negligible, $g_{*} \approx g_{*,\gamma}$.
+In the case of dark QCD-like $SU(6)$ chiral  phase transitions, such as in the generic Nnatrualness models, The temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{d})$.
+Some authors [bai, etc] have looked at calculating $\alpha$ through the low energy effective chiral lagrangian for $SU(6)_{L} \times SU(6)_{R}$ breaking.
+We take the optimistic scenario,
+
+\begin{equation}
+\alpha \approx \xi^{4} \approx \bigg( \frac{\Lambda_{d}}{T_{\gamma}^{nuc}}\bigg)^4
+\end{equation}
+
+The inverse timescale of the phase transition can be calculated
+\begin{equation}
+\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
+\end{equation}
 
@@
 With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$.
-\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ \draftnote{Define $\beta$ somewhere} enhanced gravitational waves.
+\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ \draftnote{\st{Define $\beta$ somewhere}} enhanced gravitational waves.
 With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
@@
 \begin{equation}
-h^2\Omega_{GW} = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
+h^2\Omega_{GW}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
 \end{equation}
@@
 
-\draftnote{Define $g_*$} Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
+\draftnote{\st{Define $g_*$}} Where $g_*$  is calculated using Eq.(12), although, due to the lack of substantial reheating into the hidden sectors, the first term is dominant.
+Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
 In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$.
 As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{GW}^{*}(f)$, will redshift to today's value $\Omega_{GW}^{0}(f) = \mathcal{A}\, \Omega_{GW}^{*}((a_{0}/a) f) $.
-\draftnote{Define $\mathcal{A}$} Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,
+\draftnote{\st{Define $\mathcal{A}$}}.The Redshift factor,$\mathcal{A}$, is related to the ratio of scale factors at the time of production and observation, and only scales with the relativistic degrees of freedom.
+Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,
 

### 2019-08-21 gwnnDraft02.tex
light drafting in sections 2-4

--- 2019-08-19 gwnnDraft02.tex
@@
 with ${\cal L}_0 = {\cal L}_{\rm SM}$ being the Standard Model Lagrangian, and ${\cal L}_i$ being a copy of the SM Lagrangian with different fields, but with all dimensionless parameters the same.
-Each of the Lagrangians does contain a dimension operator:
+Each of the Lagrangians does contain a dimensionful operator:
 \begin{equation}
@@
 where $\Lambda$ is some high scale cutoff, $N$ is the number of sectors, and $r$ mass parameter in the SM in units of $\Lambda_H^2/N$.
-This setup solves the hierarchy problem if $r \sim \mathcal{O}(1)$\footnote{Constraints require $r$ to be somewhat smaller than 1.} and we the Higgs masses in the different sectors as randomly distributed~\cite{Arkani-Hamed:2016rle}.
-We have taken for simplicity that there equal numbers sectors with positive and negative $m_H^2$, but this is not nessesary.
+We view the parameterization of Eq.~(\ref{eqn:massParam}) as a random distribution in theory space up to the cutoff $\Lambda$, therefore this setup solves the hierarchy problem if $r \sim \mathcal{O}(1)$~\cite{Arkani-Hamed:2016rle}\footnote{Constraints require $r$ to be somewhat smaller than 1.} and our sector is the one that that has the smallest absolute value of the Higgs mass parameter.
+We have taken for simplicity that there equal numbers sectors with positive and negative $m_H^2$, but this assumption does not affect our analysis.
 This Nnaturalness framework can be generalized: the various sectors can possess a wide range of particle content that can be freely selected by the model builder.
@@
 \begin{equation}\label{eqn:vevs}
-v^i = m^i_H/\sqrt{\lambda_i} ~ \sqrt{\frac{2i + r}{N}}\left(\frac{\Lambda_H}{\lambda}\right),
+v^i = \sqrt{-(m_H^2)_i/\lambda_i} \sim \Lambda_H\sqrt{\frac{2i + r}{\lambda N}},
 \end{equation}
-$\lambda_i$ is the quartic coefficient of the scalar potential and is the same across all sectors. 
+$\lambda_i$ is the quartic coefficient of the scalar potential and is the same across all sectors, $\lambda_i=\lambda$.
+This is another way to see how this framework can solve the hierarchy problem: the Higgs vev is parametrically smaller than the cutoff for $N \gg 1$.
 %The parameter $r$ is a way to adjust the tuning of the model: adjusting $r$ away from 1 (which leads to purely uniform spacing) allows us to make a larger gap between our sector and the next one.
@@
 %As mentioned above, half of all sectors in this model feature a Higgs mass parameter such that $m_H^2 < 0$. 
-These ``standard sectors'' feature electroweak symmetry breaking just like in the SM, however the vevs produced scale with the changing mass parameter: $v_i \sim v_{\rm SM}\sqrt{i}$.
-As the masses for particles in these sectors scale with the vev, this leads to the masses of the $W$, $Z$ and fermions within each sector increasing with $i$.
+The ``standard sectors'' with $i>0$ feature electroweak symmetry breaking just like in the SM, however the vevs produced scale with the changing mass parameter: $v_i \sim v_{\rm SM}\sqrt{i}$.
+As the masses scale with the vev, this leads to the masses of the $W$, $Z$ and fermions within each sector increasing with $i$.
 The consequences of this on the confinement scale of QCD in the $i \geq 1$ sectors is further discussed in Sec.
@@
 
-The remaining ``exotic sectors'' within this model provide a radical departure from our own.
+The ``exotic sectors'' with $i<0$ provide a radical departure from our own.
 $m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
@@
 
-\subsection{Reheating N Sectors}
+\section{QCD Phase Transition}
+\label{sec:dQCD}
+%
+%\begin{figure*}[tb]
+%\centering
+%\begin{minipage}[c]{\textwidth}
+%\includegraphics[width=1.0\textwidth]{columbia.png}
+%\end{minipage}
+%\hfill
+%\caption{Two possible scenarios for the Columbia Plot with the up and down quark mass taken to be identical. The ``physical point" is the Standard Model. Plot from \cite{Cuteri:2017zcb}
+%}
+%\label{fig:columbia}
+%\end{figure*}
 
-\begin{figure*}[tb]
-\centering
-\begin{minipage}[c]{\textwidth}
-\includegraphics[width=0.4\textwidth]{standardDecay.eps}
-\includegraphics[width=0.4\textwidth]{exoticDecay.eps}
-\end{minipage}
-\hfill
-\caption{Feynman diagrams for primary reheaton decays assuming $m_{\phi} \ll m_H$.
-The left decay is the primary decay for standard sectors ($\langle H\rangle\neq 0$), with $f$ representing all possible fermions.
-The right decay occurs in exotic sectors ($\langle H\rangle = 0$).
-}
-\label{fig:reheatonDecays}
-\end{figure*}
+We now study the nature of the QCD phase transition across the different sectors.
+Due to the confining nature of QCD, the exact nature of the phase transition is often difficult to ascertain analytically and requires the study of lattice simulations.
+In the SM, it is known that the phase transition is a crossover and does lead to gravitational wave signals~\cite{}.
+In the general case \draftnote{Is this specific to three colours?}, the phase transition can be strongly first order in two regimes~\cite{lattice,SVETITSKY1982423,Pisarski:1983ms}:
+\begin{itemize}
+\item Three or more light flavours.
+\item No light flavours. 
+\end{itemize}
+Light means mass small compared to the confinement scale $\Lambda_{QCD}$, but what that means quantitatively is not precisely determined.
+In the SM, the up and down quarks are light, but the strange is not sufficiently light for an SFOPT.
 
-A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by number of effective neutrinos ($N_{eff}$) bounds.
-This is done through the introduction of a post-inflationary field called the ``reheaton".
-After inflation, the reheaton field possess the majority of the energy density of the Universe.
-Although this field can generically be either by bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$.
-Our focus is primarily the production of gravitational waves from multiple sectors: \textcolor{yellow}{What does the following mean?} a fermion reheaton doesn't change the scaling of the energy density of the exotic sectors and thus doesn't affect expected gravitational wave profiles.
-
-In order to maintain the naturalness of our SM sector, the reheaton coupling is taken to be universal to every sector's Higgs.
-However, a large amount of the Universe's energy density must ultimately be deposited in our own sector for $N$naturalness to avoid instant exclusion.
-In order to accomplish this the decay width into each sector must drop as $\vert m_H\vert$ grows.
-If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$ then we construct a model that behaves as desired.
-
-Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we generalize our results to include the (rather unnatural) case where sectors are reheated ``randomly" as opposed to in relation to the higgs mass parameter.
-This allows us to explore more general models with multiple dark sectors at a huge range of scales.
-For these models, the reheating mechanism remains undefined and the results of this section are completely irrelevant.
-
-The appropriate Lagrangian for a scalar reheaton $\phi$ is: 
-\begin{equation}\label{eqn:nnLagrangian}
-\cL_\phi \supset -a\phi\sum_i\vert H_i\vert^2 - \frac{1}{2}m^2_\phi \phi^2.
-\end{equation}
-Note that the cross-quartic couplings are absent, suppressed by a very small coupling.
-Effective Lagrangians for the two different types of sectors present in this theory can be obtained through the integrating out of the Higgs bosons in every sector:
-\begin{equation}\label{eqn:nnEffLag}
-\begin{split}
-\cL_\phi^{v \neq 0} &\supset C_1 a y_q\frac{v}{m_h^2}\phi q q^c,
-\\
-\cL_\phi^{v = 0} &\supset C_2 a \frac{g^2}{16\pi^2 m_H^2}\phi W_{\mu\nu}W^{\mu\nu},
-\end{split}
-\end{equation}
-\textcolor{green}{Should the first equation go like $1/m_h$ (not squared)?
-It does --- v scales identically to $m_h$}with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
-
-Immediately from Eq.
-(\ref{eqn:nnEffLag}), we can see that the matrix element for decays into standard sectors is inversely proportional to that sectors higgs mass, $\cM_{m_H^2 < 0} \sim 1/m_{h_i}$.
-The Feynman diagram for this process is presented in Fig.
-\ref{fig:reheatonDecays}.
-The loop decay of $\phi \rightarrow \gamma\gamma$ is always sub-leading and can be neglected.
-It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions ($m_f \sim v_i \sim v_{SM}\sqrt{i}$) eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$.
-\textcolor{green}{Put an equation sketching how $m_f$ scales with $m_h$} For sectors where this kinematic threshold is passed for charm quarks, contributions to cosmological observables can be safely ignored.
-All in all, we end up with a decay width that scales as $\Gamma_{m_H^2<0} \sim 1/m_h^2$.
-Since we can expect energy density to be proportional to the decay width, $\frac{\rho_i}{\rho_{SM}} \approx \frac{\Gamma_i}{\Gamma_{SM}}$, this indicates that energy density of standard sectors falls:
-\begin{equation}\label{eqn:edSS}
-\rho_i \sim r_{s}\frac{\rho_{SM}}{i}
-\end{equation} 
-with $r_s$ being the ratio of the energy density of the first additional standard sector over the energy density of our sector.
-
-For the exotic sectors, Eq.
-(\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$.
-As the Feynman diagram (Fig.~\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, leading to a significantly lower energy density than the standard sectors.
-Both the decay width and energy density for these sectors scale as: $\Gamma_{m_H^2>0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2$.
-
-As a final note, the reheating temperature of our sector, $T_{RH}$, \textcolor{yellow}{What is this parameter exactly?
-The reheat temperature of the SM?
-Also, is this effect discussed in the original NNaturalness paper?
-Yes to both.} has an upper bound on the order of the weak scale.
-If this bound is not observed, the SM Higgs mass would have major thermal corrections --- leading to the branching ratios into other sectors being problematically large \citep{Arkani-Hamed:2016rle}.
-In accordance with this restriction, this project only examines reheating temperatures at or below $100$ GeV.
-
-\section{Dark QCD}
-\label{sec:dQCD}
-
-\begin{figure*}[tb]
-\centering
-\begin{minipage}[c]{\textwidth}
-\includegraphics[width=1.0\textwidth]{columbia.png}
-\end{minipage}
-\hfill
-\caption{Two possible scenarios for the Columbia Plot with the up and down quark mass taken to be identical. The ``physical point" is the Standard Model. Plot from \cite{Cuteri:2017zcb}
-}
-\label{fig:columbia}
-\end{figure*}
-
-Due to the confining nature of QCD, the exact nature of the phase transition is often difficult to ascertain analytically and requires the study of lattice simulations.
-The results of these studies on the nature of QCD phase transitions is summarized in the so-called ``Columbia" plot (Fig.
+% The results of these studies on the nature of QCD phase transitions is summarized in the so-called ``Columbia" plot (Fig.
 \ref{fig:columbia}).
@@
 In order to observe the strong first order transition required for gravitational wave production, at least some of the additional sectors present must feature quarks in either the heavy quark (pure Yang-Mills) or massless limits.
-
-In the Yang-Mills limit we see $m_{u,d,s} \rightarrow \infty$.
+%
+%In the Yang-Mills limit we see $m_{u,d,s} \rightarrow \infty$.
 This leads to the presence of a global $Z_3$ centre symmetry that is broken at high temperatures but restored low temperatures.
@@
 
-For $N$naturalness (or other mirror sector models), standard sectors with higher vevs possess more massive quarks; eventually, sectors with large enough vevs push us into the upper-right corner.
-Conversely, exotic sectors with zero vev feature incredibly light quarks and drop us into the bottom-left corner.
-In order to figure out the specifics of each sector, we follow  the same procedure as \cite{Cui:2011wk} but generalize it to an arbitrary number of additional sectors.
+For the standard sectors in our setup, the quark masses increase with increasing vev, so for sufficiently large $i$, all the quarks will be heavier than $\Lambda_{QCD}$,\footnote{$\Lambda_{QCD}$ does vary with $i$, but the sensitivity is very weak as we will see below.} and those large $i$ sectors will undergo an SFOPT if they are reheated above the the confinement scale.
+%For $N$naturalness (or other mirror sector models), standard sectors with higher vevs possess more massive quarks; eventually, sectors with large enough vevs push us into the upper-right corner. 
+Conversely, exotic sectors with zero vev feature six very light quarks, so \textit{all} the exotic sectors undergo SFOPT at the temperature of QCD confinement.
+
+We now calculate the QCD confinement scale for each sector following the same procedure as \cite{Cui:2011wk}.
 First, due to the parameters of each sector being taken to be identical save for the higgs mass squared (thus $v \neq v_i$, where $v$ is the SM vev), we assume that the strong coupling of every sector is identical at some high scale.
-Explicitly, above the top quark mass scale $\Lambda_{QCD} = 89 \pm 5$ in $\overline{MS}$ \cite{PhysRevD.98.030001}. Since the running of the gauge coupling at scale $\mu$ is given by 
-\begin{equation}\label{eqn:QCDrunning}
-\alpha_s (\mu) = \frac{2\pi}{11-\frac{2n_f}{3}}\frac{1}{\ln{\mu/\Lambda}}
-\end{equation} 
-where $n_f$ is the number of quark flavours and $\Lambda$ is the confinement scale $\Lambda_{QCD}$ \cite{Peskin:1995ev}.
-
-For any other sector $i$ we write out the expression as: 
+Using the one-loop running, the $\beta$ function can be solved:
 \begin{equation}\label{eqn:QCDrunningi}
@@
 \end{equation}
-featuring the equivalent definitions for the additional sectors.
-Because we've set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at scales above the top quark mass for the heaviest sector.
+where $n_f^i$ is the number of quark flavours with mass less than $\mu/2$ and $\Lambda^i$ is the scale where it would confine if all quarks remain massless.
+In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 5$ in $\overline{MS}$~\cite{PhysRevD.98.030001}.
+
+Because we've set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at high scales for all sectors.
 However, since the masses of the quarks in each sector are different, we end up with a unique running of the coupling for each sector.
-At every quark mass threshold for a given sector, we match the coupling strengths above and below the threshold and determine the new $\Lambda^i$ for the lower scale:
+At every quark mass threshold for a given sector, we match the coupling strengths above and below the threshold and determine the new $\Lambda^i$ for the lower scale.
+For example, at the mass of the top quark, we match a five flavour coupling with the six flavour one:
 \begin{equation}
-\alpha_s^{i(5)} = \alpha_s^{i(6)}
+\alpha_s^{i(5)}(2 m^i_t) = \alpha_s^{i(6)}(2 m^i_t) 
 \end{equation} 
@@
 
-Suppressing the $i$s for cleanliness, we can arrive at similar relations at the bottom and charm thresholds
+Suppressing the $i$'s for notational cleanliness, we can arrive at similar relations at the bottom and charm thresholds
 \begin{equation}
@@
 
-As mentioned in the previous sections (see Eq.~(\ref{eqn:vevs})),\textcolor{green}{refer to a particular equation} for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$.
+As shown in Eq.~(\ref{eqn:vevs}), for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$.
 This leads to increasingly heavy particle spectra for higher sectors --- eventually leading to sectors that are essentially pure Yang-Mills that featuring strong first order phase transitions.
@@
 
-The actual boundary of region of interest on the Columbia plot is not precisely known and further lattice simulations are required to determine exactly where in parameter space cross-over transitions end and first order transitions begin.
+%The actual boundary of region of interest on the Columbia plot is not precisely known and further lattice simulations are required to determine exactly where in parameter space cross-over transitions end and first order transitions begin.
 In lieu of such studies, we parameterize our ignorance in the form of a ``slop factor" $\kappa$.
@@
 at the energy scale we're interested in.
-$\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a standard model value of $\Lambda^{(6)}_{MS} =(89 \pm 6)\, \mev$\cite{PhysRevD.98.030001}\textcolor{green}{what is that value?}.
+$\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a standard model value of $\Lambda^{(6)}_{MS} =(89 \pm 6)\, \mev$~\cite{PhysRevD.98.030001}.
 Rewriting Eq.~(\ref{eqn:lambda2}) in terms of standard model variables,
@@
 \end{equation}
-Setting this equal to some multiple of the quark mass of sector $i$,
+We take the sector with SFOPT to be the ones when the mass of the up quark, down quark, and QCD phase transition scale are all comparable:
 \begin{equation}
-\kappa m^i_u = \kappa m_u \sqrt{i} = (m_s m_c m_b m_t i^2)^{2/29}(\Lambda_{(6)})^{21/29}.
+m^i_u \sim m_u \sqrt{i} \sim (m_s m_c m_b m_t i^2)^{2/29}(\Lambda_{(6)})^{21/29}.
 \end{equation}
@@
 \begin{equation}\label{eqn:critIndex}
-i = \frac{(m_s m_c m_b m_t)^{4/25}(\Lambda_{(6)})^{42/25}}{(\kappa m_u)^{58/25}}.
+i^c \sim \frac{(m_s m_c m_b m_t)^{4/25}(\Lambda_{(6)})^{42/25}}{( m_u)^{58/25}} \sim 10^5
 \end{equation}
+%
+As we will see in Sec.~\ref{sec:reheat}, In the original Nnaturalness setup~\cite{Arkani-Hamed:2016rle}, the energy dumped into the $i$th sector scales as $i^{-8}$ \draftnote{check}, so there will will not be enough energy in the sectors with $i>I^c$ to see a signature of these phase transitions.
 
-The critical index demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
+%This critical index demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
 Looking back to the energy density scaling in Eq.~(\ref{eqn:edSS})\textcolor{green}{refer to a particular equation} we see that, within the context of $N$naturalness, the energy density of these sectors is at most $10^{-4}$ \textcolor{green}{why not $10^{-3}$?} that of our sector.
@@
 
-However, if we move away from the standard $N$naturalness reheating mechanism and begin exploring mirror sectors with large vevs with $\cO( >10\%)$ of our energy density $\rho_{SM}$, we can have sectors with relatively high dark QCD scales that produce detectable gravitational waves.
-These sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
-From Eq.~(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector --- the maximum possible given a $10^{16}$ limit \cite{Arkani-Hamed:2016rle} \textcolor{yellow}{Is this actually an upper value of $m_H^2$ at the gut scale?
-The more sectors added in, the lower the scale of strong gravitational coupling.
-With more sectors than $10^16$, the top sectors start having vevs higher than the gravitational scale} of sectors is $\sim 38 \,\gev$.
-After imposing $N_{eff}$ constraints (as in Sec.
-\ref{sec:constraints}), the energy density of said sector is limited to $\sim 0.25\rho_{SM}$.
+However, if we move away from the original $N$naturalness reheating mechanism and begin exploring mirror sectors with large vevs and with relative energy densities $\rho_i / \rho_{SM} \sim 10\%$, a possibility allowed by current constraints, we can have sectors with relatively high dark QCD scales that produce detectable gravitational waves.
+From Eq.~(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector.
+If we take Higgs vevs as high as the GUT scale $\sim 10^{16}$ GeV, then we can gave confinement scales as high as $\sim 38 \,\gev$.
 The signals of this sector and other test cases like it are explored in Sec.
@@
 
+\draftnote{Move the below two statements to the contraints and GW sections respectively}
+
+After imposing $N_{eff}$ constraints (as in Sec. \ref{sec:constraints}), the energy density of said sector is limited to $\sim 0.25\rho_{SM}$.
+
+These sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+
 \subsection{Exotic Sectors}
 
-In every exotic sector the fermion masses are exceptionally light: their masses are generated by dimension six operators with the Higgs integrated out as shown in Eq.~(\ref{eqn:exoticFM}) \textcolor{green}{cite an equation from before}, and are therefore all below the confinement scale.
+In every exotic sector the fermion masses are exceptionally light: their masses are generated by dimension six operators with the Higgs integrated out as shown in Eq.~(\ref{eqn:exoticFM}), and are therefore all below the confinement scale.
 The exotic sectors all have identical one-loop running of the QCD gauge coupling, and thus all have approximately the same confinement scale given by $\Lambda_{\rm ex} \sim 90 \,\mathrm{MeV}$.
@@
 
-The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6) \,\times$ SU$(6) \rightarrow\,$ SU$(6)$ and thus 35 pseudo-Goldstone bosons.
+The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6) \,\times$ SU$(6) \rightarrow\,$ SU$(6)$ and thus 35 pseudo-Goldstone bosons (pions).
+The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation~\cite{Gell-Mann,Schwartz:2013pla},
+\begin{equation}\label{eqn:gmor}
+m^2_{\pi} = \frac{V^3}{F^2_{\pi}}(m_u + m_d),
+\end{equation}
+where $V \sim \Lambda_{QCD}$, $F_\pi$ is the pion decay constant.
+One expects that within a given sector $F_\pi \sim V \sim \Lambda_{QCD}$ \cite{Schwartz:2013pla} and as exotic sectors have $\Lambda_{ex} \sim 90 \,\mev$ while the SM features $\Lambda_{QCD} = (332\pm17)\,\mev$ \cite{PhysRevD.98.030001} we expect at most $\mathcal{O}(1)$ difference in the $\sqrt{\frac{V^3}{F_\pi^2}}$ coefficient relative to the SM value.
+So, for pions in exotic sector $i$:
+\begin{equation}
+m_{\pi}^i \sim \sqrt{\frac{m_a^i+m_b^i}{m_a + m_b}} m_{\pi}.
+\end{equation}
+Here, $a$ and $b$ denote the component quark flavours. \draftnote{Shouldn't the denominator be up and down quarks in the SM?}
+
+\draftnote{move to GW section}
 These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
@@
 
-The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation \textcolor{green}{Also cite Gell-Mann et al} \cite{Gell-Mann,Schwartz:2013pla},
-\begin{equation}\label{eqn:gmor}
-m^2_{\pi} = \frac{V^3}{F^2_{\pi}}(m_u + m_d),
-\end{equation}
-where $V \sim \Lambda_{QCD}$, $F_\pi$ is the pion decay constant.
-One expects that within a given sector $F_\pi \sim V \sim \Lambda_{QCD}$ \cite{Schwartz:2013pla} and as exotic sectors have $\Lambda_{ex} \sim 90 \,\mev$ while the SM features $\Lambda_{QCD} = (332\pm17)\,\mev$ \cite{PhysRevD.98.030001} we expect at most $\mathcal{O}(1)$ difference in the $\sqrt{\frac{V^3}{F_\pi^2}}$ coefficient between sectors.
-So, for mesons in exotic sector $i$:
-\begin{equation}
-m_{\pi}^i \sim \sqrt{\frac{m_a^i+m_b^i}{m_a + m_b}} m_{\pi}.
-\end{equation}
-Here, $a$ and $b$ denote the component quark flavours.
 It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.
-\textcolor{green}{What are $m_a^i$?
-Is this the right formula,isn't $V$ and $f_\pi$ different from the SM to the $i$th exotic sector?
-Also, how do you compute $\Delta m$ when you have a different set of particles inside (pions) as outside (quarks) the bubble?
-}
 
@@
 
+\section{Reheating N Sectors}
+\label{sec:reheat}
+
+%\begin{figure*}[tb]
+%\centering
+%\begin{minipage}[c]{\textwidth}
+%\includegraphics[width=0.4\textwidth]{standardDecay.eps}
+%\includegraphics[width=0.4\textwidth]{exoticDecay.eps}
+%\end{minipage}
+%\hfill
+%\caption{Feynman diagrams for primary reheaton decays assuming $m_{\phi} \ll m_H$.
+The left decay is the primary decay for standard sectors ($\langle H\rangle\neq 0$), with $f$ representing all possible fermions.
+The right decay occurs in exotic sectors ($\langle H\rangle = 0$).
+%}
+%\label{fig:reheatonDecays}
+%\end{figure*}
+
+A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by cosmological constraints, particularly those from number of effective neutrinos ($N_{eff}$).
+In~\cite{Arkani-Hamed:2016rle} this is done through the introduction of a post-inflationary field called the ``reheaton".
+After inflation, the reheaton field possess the majority of the energy density of the Universe.
+Although this field can generically be either bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$.
+Our focus is primarily the production of gravitational waves from multiple sectors and a fermion reheaton does not change the scaling of the energy density of the exotic sectors and thus does not affect expected gravitational wave profiles.
+
+In order to maintain the naturalness of our SM sector, the reheaton coupling is taken to be universal to every sector's Higgs.
+However, a large amount of the Universe's energy density must ultimately be deposited in our own sector for $N$naturalness to avoid instant exclusion.
+In order to accomplish this the decay width into each sector must drop as $\vert m_H\vert$ grows.
+If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$ then we construct a model that behaves as desired.
+
+The appropriate Lagrangian for a scalar reheaton $\phi$ is: 
+\begin{equation}\label{eqn:nnLagrangian}
+\cL_\phi \supset -a\phi\sum_i\vert H_i\vert^2 - \frac{1}{2}m^2_\phi \phi^2.
+\end{equation}
+\draftnote{what does this sentence mean?} Note that the cross-quartic couplings are absent, suppressed by a very small coupling.
+Effective Lagrangians for the two different types of sectors present in this theory can be obtained by integrating out of the Higgs bosons in every sector:
+\begin{equation}\label{eqn:nnEffLag}
+\begin{split}
+\cL_\phi^{v \neq 0} &\supset C_1 a y_q\frac{v}{m_h^2}\phi q q^c,
+\\
+\cL_\phi^{v = 0} &\supset C_2 a \frac{g^2}{16\pi^2 m_H^2}\phi W_{\mu\nu}W^{\mu\nu},
+\end{split}
+\end{equation}
+with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
+
+Immediately from Eq.
+(\ref{eqn:nnEffLag}), we can see that the matrix element for decays into standard sectors is inversely proportional to that sectors higgs mass, $\cM_{m_H^2 < 0} \sim 1/m_{h_i}$ (since $v\sim m_H$).
+%The Feynman diagram for this process is presented in Fig. \ref{fig:reheatonDecays}. 
+The loop decay of $\phi \rightarrow \gamma\gamma$ is always sub-leading and can be neglected.
+It should be noted that as one goes to sectors with larger and larger vevs, the increasing mass of the fermions ($m_f \sim v_i \sim v_{SM}\sqrt{i}$) eventually leads to situations where the decay to two on-shell bottom or charm quarks is kinematically forbidden, $m_\phi < 2 m_q$.
+For sectors where this kinematic threshold is passed for charm quarks, the amount of energy in these sectors becomes so small that contributions to cosmological observables can be safely ignored.
+All in all, we end up with a decay width that scales as $\Gamma_{m_H^2<0} \sim 1/m_h^2$.
+Since we can expect energy density to be proportional to the decay width, $\frac{\rho_i}{\rho_{SM}} \approx \frac{\Gamma_i}{\Gamma_{SM}}$, this indicates that energy density of standard sectors falls:
+\begin{equation}\label{eqn:edSS}
+\rho_i \sim r_{s}\frac{\rho_{SM}}{i}
+\end{equation} 
+with $r_s$ being the ratio of the energy density of the first additional standard sector over the energy density of our sector.
+
+For the exotic sectors, Eq.~(\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$ and is also loop supressed. 
+%As the Feynman diagram (Fig.~\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, 
+This leads to a significantly lower energy density than the standard sectors.
+Both the decay width and energy density for these sectors scale as: $\Gamma_{m_H^2>0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2$.
+
+As a final note, in this setup the reheating temperature of the SM, $T_{RH}$, has an upper bound on the order of the weak scale.
+If this bound is not observed, the SM Higgs mass would have major thermal corrections --- leading to the branching ratios into other sectors being problematically large~\citep{Arkani-Hamed:2016rle}.
+Thus we only consider relatively low reheating temperatures $\lesssim 100$ GeV.
+
+Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we also consider a more general parameterization where sectors are reheated ``randomly" as opposed to in relation to the Higgs mass parameter.
+This allows us to explore more a broader model space with multiple dark sectors at a huge range of scales.
+For these models, the reheating mechanism remains undefined and the results of this section are completely irrelevant.
+
 \section{Constraints}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{neff.png}
-\hfill
-\caption{$\Delta N_{eff}$ as a function of relativistic degrees of freedom in a fully decoupled hidden sector ($g_h$) and the temperature ratio of said sector.
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.45\textwidth]{neff.png}
+%\hfill
+%\caption{$\Delta N_{eff}$ as a function of relativistic degrees of freedom in a fully decoupled hidden sector ($g_h$) and the temperature ratio of said sector.
 Contours set $\Delta N_{eff}$ to (0.01, 0.03,  0.1,  0.5) as the dashed lines, from left to right.
 Most stringent current $N_{eff}$ bounds shade in purple.
-}
-\label{fig:neff}
-\end{figure}
+%}
+%\label{fig:neff}
+%\end{figure}
 
 In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom.
-Dark photons, neutrinos, and the like abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons of these sectors are can easily be relativistic.
+Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons of these sectors can also  be relativistic.
 In $N$naturalness this feature is realized quite dramatically: each of the thousands (or millions or billions) of sectors possess relativistic degrees of freedom.
@@
 
-\textcolor{yellow}{This is not the physics described in the previous paragraph} The SM predicts that $N^{SM}_{eff} = 3.046$ \cite{Mangano:2005cc}.
-This is in good agreement with bounds from studies of the Cosmic Microwave Background (CMB) by Planck combined with bayon acoustic oscillations (BAO) measurements \cite{Aghanim:2018eyx}:
+The SM predicts that $N^{SM}_{eff} = 3.046$ \cite{Mangano:2005cc}.
+This is in good agreement with the $2\sigma$ bounds from studies of the Cosmic Microwave Background (CMB) by Planck combined with baryon acoustic oscillations (BAO) measurements \cite{Aghanim:2018eyx}:
 \begin{equation}\label{eqn:NeffBounds}
@@
 \end{equation}
-\textcolor{green}{Are these $1\sigma$? Maybe show the 95\% interval instead?These are $2\sigma$}
 Various different assumptions about the history of the universe can be made and different data sets can be chosen to obtain slightly different results \cite{Breitbach:2018ddu} --- for the purposes of this exploratory work, wading through this landscape is unnecessary.
@@
 Here, $g_h$ represents the effective number of relativistic degrees of freedom for the hidden sector when the hidden sector has a temperature $T_h = \xi_h T_\gamma$.
-Contours for Eq.
-(\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:neff}.
+\draftnote{These should be defined at the time of CMB decoupling?}
+%Contours for Eq. (\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:neff}. 
 We take this approach and generalize it to include many additional sectors:
@@
 
-As Fig.~\ref{fig:neff} \textcolor{green}{Why is it figure V?} demonstrates, sectors with a temperature ratio above $\xi_h\sim 0.6$ with even a couple of relativistic particles are immediately excluded by CMB constraints.
+\draftnote{Maybe give what the temperature ratio should be for one standard (or exotic) sector to not be excluded.} 
+%As Fig.~\ref{fig:neff} \textcolor{green}{Why is it figure V?} demonstrates, sectors with a temperature ratio above $\xi_h\sim 0.6$ with even a couple of relativistic particles are immediately excluded by CMB constraints.
 Accordingly, the additional sectors present in this project must be heated to a much smaller fraction of our own sector's temperature.

### 2019-08-22 gwnnDraft02.tex
test
first bit of refs added

@@
 
-The recent experimental detection of gravitational waves~\cite{} gives humanity a new way to observe the universe.
-Future experiments~\cite{} will greatly expand the frequency range observable.
-Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{}.
+The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe.
+Future experiments~\cite{Crowder:2005nr,Harry:2006fi,Sathyaprakash:2012jk,2017arXiv170200786A,Seto:2001qf,Sato:2017dkf,Janssen:2014dka} will greatly expand the frequency range observable.
+Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Caprini:2015zlo,Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Mazumdar:2018dfl}.
 Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.
@@
 Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
-This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{}.
+This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu}.
 

### 2019-08-22 gwnnDraft02.tex
more citations

@@
 As in~\cite{Arkani-Hamed:2016rle}, we assume that the standard sector with the smallest absolute value of $m_H^2$ is the Standard Model.
-\item \textbf{Exotic Sectors}: Those with  $m_H^2 > 0$. In this case, electroweak symmetry breaking is preserved below the mass of the Higgs, and broken by the confinement of QCD~\cite{}.
+\item \textbf{Exotic Sectors}: Those with  $m_H^2 > 0$.
+In this case, electroweak symmetry breaking is preserved below the mass of the Higgs, and broken by the confinement of QCD~\cite{Arkani-Hamed:2016rle,Pisarski:1983ms}.
 \end{itemize}
-Cosmological observations, particularly limits on extra relativistic degrees of freedom at the time of Big Bang Nucleosynthesis~\cite{} and the time fo the formation of the cosmic microwave background (CMB)~\cite{}, require that most of the energy in the universe is in the Standard Model sector as we will quantify.
+Cosmological observations, particularly limits on extra relativistic degrees of freedom at the time of Big Bang Nucleosynthesis and the time of the formation of the cosmic microwave background (CMB)~\cite{Aghanim:2018eyx}, require that most of the energy in the universe is in the Standard Model sector as we will quantify.
 Therefore, the hidden sectors cannot be in thermal equilibrium at any time, and the physics of reheating must dump energy preferentially in the Standard Model sector.
@@
 The exotic sectors will also undergo a phase transition when QCD confines and electroweak symmetry is broken simultaneously.
-The condition for these transitions to leave imprints on the stochastic gravitational wave spectrum is that they strongly first order phase transitions (SFOPT)~\cite{}.
+The condition for these transitions to leave imprints on the stochastic gravitational wave spectrum is that they strongly first order phase transitions (SFOPT)~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080}.
 This does not occur at either the electroweak or QCD phase transition in the SM, but as we will show, it does happen in some standard sectors, and in \textit{all} exotic sectors that reheat above the QCD phase transition.

### 2019-08-22 gwnnDraft02.tex
more drafting

--- 2019-08-22 gwnnDraft02.tex
@@
 %
-As we will see in Sec.~\ref{sec:reheat}, In the original Nnaturalness setup~\cite{Arkani-Hamed:2016rle}, the energy dumped into the $i$th sector scales as $i^{-8}$ \draftnote{check}, so there will will not be enough energy in the sectors with $i>I^c$ to see a signature of these phase transitions.
+\draftnote{please check, I get this:}
+\begin{equation}\label{eqn:critIndex}
+i^c \sim \frac{(m_s m_c m_b m_t)^{4/21}(\Lambda_{(6)})^{2}}{( m_u)^{58/21}} \sim 10^6
+\end{equation}
+As we will see in Sec.~\ref{sec:reheat}, in the original Nnaturalness setup~\cite{Arkani-Hamed:2016rle}, the energy dumped into the $i$th sector scales as $i^{-1}$, so there will will not be enough energy in the sectors with $i>i^c$ to see a signature of these phase transitions.
 
@@
 \ref{sec:gw}.
-
-\draftnote{Move the below two statements to the contraints and GW sections respectively}
-
-After imposing $N_{eff}$ constraints (as in Sec. \ref{sec:constraints}), the energy density of said sector is limited to $\sim 0.25\rho_{SM}$.
-
-These sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
 
@@
 m_{\pi}^i \sim \sqrt{\frac{m_a^i+m_b^i}{m_a + m_b}} m_{\pi}.
+\label{eq:ith_pion_mass}
 \end{equation}
 Here, $a$ and $b$ denote the component quark flavours. \draftnote{Shouldn't the denominator be up and down quarks in the SM?}
-
-\draftnote{move to GW section}
-These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
-Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh},
-\begin{equation}\label{eqn:critPTstrength}
-\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
-\end{equation} 
-for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
-
-It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.
-
-Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
-Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.
 
@@
 %As the Feynman diagram (Fig.~\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, 
-This leads to a significantly lower energy density than the standard sectors.
-Both the decay width and energy density for these sectors scale as: $\Gamma_{m_H^2>0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2$.
+This leads to a significantly lower energy density than the standard sectors. Both the decay width and energy density for these sectors scale as: 
+\begin{equation}
+\Gamma_{m_H^2>0} \sim \rho_i \sim 1/m_H^4 \sim 1/i^2.
+\label{eq:reheat_exotic}
+\end{equation}
 
@@
 Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons of these sectors can also be relativistic.
-In $N$naturalness this feature is realized quite dramatically: each of the thousands (or millions or billions) of sectors possess relativistic degrees of freedom.
+In $N$naturalness this feature is realized quite dramatically: each of the $N$ of sectors possess relativistic degrees of freedom.
 The presence of these particles can have two main effects: extra relativistic particles can alter the expansion history of the universe through changes to the energy density or hidden sectors can feature annihilations that reheat the photons or neutrinos of our sector near Big Bang Nucleosynthesis (BBN) and affect the light element abundances.
@@
 Various different assumptions about the history of the universe can be made and different data sets can be chosen to obtain slightly different results \cite{Breitbach:2018ddu} --- for the purposes of this exploratory work, wading through this landscape is unnecessary.
+Additionally,
+\begin{equation}
+\frac{(\Delta N^i_{eff})_{CMB}}{(\Delta N^i_{eff})_{BBN}} \geq 1
+\end{equation}
+for any \draft{check} decoupled hidden sector~\cite{Arkani-Hamed:2016rle}.
+Because the constraints on $N_{eff}$ are stronger at photon decoupling than at BBN, we can focus purely on the constraints provided by the former.
 
@@
 \end{equation} 
-Here, $g_h$ represents the effective number of relativistic degrees of freedom for the hidden sector when the hidden sector has a temperature $T_h = \xi_h T_\gamma$.
+Here, $g_h$ represents the effective number of relativistic degrees of freedom for the hidden sector\footnote{$g_h = N_{\rm boson} + 7 N_{\rm fermion}/8$.} when the hidden sector has a temperature $T_h = \xi_h T_\gamma$.
 \draftnote{These should be defined at the time of CMB decoupling?}
@@
 \end{equation} 
+For a dark sector with one relativistic degree of freedom, its temperature must be $\sim T_{\rm SM}/2$ to not be excluded.
+This sector would have an energy density $\rho \sim 0.1 \rho_{\rm SM}$.
+\draftnote{check!}
 
-\draftnote{Maybe give what the temperature ratio should be for one standard (or exotic) sector to not be excluded.} 
+%\draftnote{Maybe give what the temperature ratio should be for one standard (or exotic) sector to not be excluded.} 
 %As Fig.~\ref{fig:neff} \textcolor{green}{Why is it figure V?} demonstrates, sectors with a temperature ratio above $\xi_h\sim 0.6$ with even a couple of relativistic particles are immediately excluded by CMB constraints.
@@
 
-The original $N$naturalness paper focused on the (stronger) $N_{eff}$ constraints from the additional standard sectors and ignored the exotic sectors altogether \cite{Arkani-Hamed:2016rle}; in contrast, we take the opposite approach.
+\draftnote{...}
+
+This means, that for a single standard sector, the energy density is limited to $\sim 0.25\rho_{SM}$, while for an exotic sector, we can have ??
+
+%The original $N$naturalness paper focused on the (stronger) $N_{eff}$ constraints from the additional standard sectors and ignored the exotic sectors altogether \cite{Arkani-Hamed:2016rle}; in contrast, we take the opposite approach.
 Since we're more interested in a more general scenario with multiple dark phase transitions, we focus in on whether zero vev sectors can dodge these $N_{eff}$ bounds.
-Additionally,
-\begin{equation}
-\frac{(\Delta N^i_{eff})_{CMB}}{(\Delta N^i_{eff})_{BBN}} \geq 1
-\end{equation}
-for any sector $i$ \cite{Arkani-Hamed:2016rle}.
-Because the constraints on $N_{eff}$ are stronger at photon decoupling than at BBN, we can focus purely on the constraints provided by the former \cite{Aghanim:2018eyx}.
 
-Within the framework of SM-like particle content (save the higgs mass parameter), our exotic sectors feature at most 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom.
+We begin by computing the constraints on exotic sectors; these are significantly weaker than those for standard sectors~\cite{Arkani-Hamed:2016rle}. 
+%At high scales, these sectors feature 106.75 effective degrees of freedom at high energies: 72 from quarks,  12 from charged leptons, 6 from neutrinos, 16 from gluons, 2 from photons, 6 from W bosons (no longitudinal modes due to a no symmetry breaking), 4 from the higgs sector (again, no symmetry breaking leads to 3 additional modes), for a total of 118 degress of freedom.
 Scaling the fermionic contributions by $7/8$ gives us 106.75 effective relativistic degrees of freedom.
 After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom.
-Since all additional sectors are colder than our own \textcolor{yellow}{Aren't they always colder than our own?
-Yes, they are.} by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.~(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector \textcolor{green}{From photons and neutrinos?
-What about $\Delta N_{eff}$ constraints from BBN?
-This would be a much higher (SM) temperature.} .
+At the time of photon decoupling ($T_\gamma \sim 0.39 \,\ev$) while the temperature of the exotic sectors is lower still.
+This means that for sectors with small and moderate $i$, we can use Eqs.~(\ref{eqn:exoticFM}) and~(\ref{eq:ith_pion_mass}) to see that the pions will be non-relativistic  leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.
+\draftnote{Pions are not decoupled at BBN time, does this in any way affect the analysis?} For very large $i$, the pions can be much lighter, but those sectors also have very little energy in them in the standard reheating scenario.
 
-Coupling the number of effective degrees of freedom per sector with the energy density scaling of $\sim 1/m_H^4$ found in the zero vev sectors leads to tiny temperature ratios.
+%Since all additional sectors are colder than our own, by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.~(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.
+\draftnote{Pions are not decoupled at BBN time, does this in any way affect the analysis?}
+
+Coupling the number of effective degrees of freedom per sector with the energy density scaling of $\sim 1/m_H^4$ as in Eq.~(\ref{eq:reheat_exotic}) means that the zero vev sectors have small temperature ratios.
 Assuming a reheating temperature of $100$ GeV and a completely uniform distribution of sectors, the temperature of the first exotic sector is slightly more than $6\%$ of our sector at reheating.
@@
 \end{equation}     
+\draftnote{doesn't $\rho$ go like $i^{-2}$ rather than $\xi$ going like $i^{-2}$??}
 with $T_{RH_{E1}}/T_{RH}$ being the ratio of the reheat temperatures of the 1st exotic sector and our own sector ($0.06$ in standard $N$naturalness with $r = 1$).
-\textcolor{green}{Where does the $0.06$ come from?} This is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$.
+This sum is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$.
 Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.
@@
 adjusting the exotic sectors to have a lower higgs mass squared or clustering multiple hidden sectors close to the first exotic one) leads to a $\Delta N_{eff}$ contribution that is larger than the base $N$naturalness case.
-This increase is not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.
+This increase is typically not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.
 
-\subsection{High Scale Transitions}
+\subsection{Generalized Reheating Scenarios}
 
-The generalization of possible reheating mechanisms mentioned in section \ref{sec:nn} --- where the reheating mechanism no longer depends on the higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study.
-Specifically, this allow mirror sectors with large vevs to reheat to significant energy densities and thus produce gravitational waves with enough power to be detected.
-Crucially, despite this analysis being limited to mirror sectors with large higgs' masses this analysis pertains to any strong, confining phase transition at high scales.
+The generalization of possible reheating mechanisms mentioned in section~\ref{sec:reheat} --- where the reheating mechanism no longer depends on the higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study.
+Specifically, this allows mirror sectors with large Higgs vevs to be reheated to significant energy densities and thus produce gravitational waves with enough power to be detected.
+Crucially, despite this analysis being limited to mirror sectors with large Higgs masses, this analysis pertains to any strong, confining phase transition at high scales.
 
@@
 \\
-\rho_i &\sim 0.08 \rho_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors}.
+\rho_i &\sim 0.08 \rho_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
 \end{split}
 \end{equation}
+where all the hidden sectors have the same temperature as one another. \draftnote{right?}
 
 Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own.
-In terms of the $N$naturalness framework, this consisted of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}.
+In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the cirtical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale.
+ %of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}.
 The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are shown in Sec.~\ref{sec:gw}.
@@
 \section{Gravitational Wave Signals}
+
+\draftnote{exotic sector computation}
+These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
+Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh},
+\begin{equation}\label{eqn:critPTstrength}
+\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
+\end{equation} 
+for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
+
+It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.
+
+Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+
+Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.
 

### 2019-08-23 gwnnDraft02.tex
drafting in sections 4-6

@@
 \end{equation} 
-Here, $g_h$ represents the effective number of relativistic degrees of freedom for the hidden sector\footnote{$g_h = N_{\rm boson} + 7 N_{\rm fermion}/8$.} when the hidden sector has a temperature $T_h = \xi_h T_\gamma$.
-\draftnote{These should be defined at the time of CMB decoupling?}
+Here, $g_h$ represents the effective number of relativistic degrees of freedom for the hidden sector\footnote{$g_h = N_{\rm boson} + 7 N_{\rm fermion}/8$.}, and we parameterize the hidden sector temperature by~\cite{Breitbach:2018ddu}
+\begin{equation}
+\xi_h \equiv  \frac{T_{h}}{T_{\gamma}},
+\label{eq:xi}
+\end{equation}
+and these should be evaluated at the time of photon decoupling. 
+%
+%
+%when the hidden sector has a temperature $T_h = \xi_h T_\gamma$. \draftnote{These should be defined at the time of CMB decoupling?} 
 %Contours for Eq. (\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:neff}. 
@@
 \subsection{Exotic Sector Contributions}
-
-\draftnote{...}
-
-This means, that for a single standard sector, the energy density is limited to $\sim 0.25\rho_{SM}$, while for an exotic sector, we can have ??
 
@@
 This increase is typically not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.
+
+\draftnote{What is temperature ratio for random reheating scenario?}
 
@@
 
+\draftnote{---------}
+
 \label{sec:gw}
-Sectors other than the SM can be reheated through multifield inflationary theories, Reheaton models, etc.
+%Sectors other than the SM can be reheated through multifield inflationary theories, Reheaton models, etc.
 In these models, the SM will receive the majority of the energy density while the remaining energy density will be distributed, in a model dependent way, to the various hidden sectors.
 If there does not exist a portal between the sectors, they will remain decoupled and evolve independently.
-When looking at multiple thermally decoupled hidden sectors it is convienent to define the temperature ratio [cite cold,dark,noisy]
-\begin{equation}
-\xi_i \equiv  \frac{T_{i}}{T_{\gamma}}
-\end{equation}
-Where $T_{i}$ is the temperature of the $i^{th}$ hidden sector, and $T_{\gamma}$ the temperature of the standard model (assuming radiation domination).
+When looking at multiple thermally decoupled hidden sectors it is convenient to define the temperature ratio [cite cold,dark,noisy]
+%\begin{equation}
+%\xi_i \equiv  \frac{T_{i}}{T_{\gamma}}
+%\end{equation}
+%Where $T_{i}$ is the temperature of the $i^{th}$ hidden sector, and $T_{\gamma}$ the temperature of the standard model (assuming radiation domination).
 
-\vspace{1em }
-Right after reheating, the temperatures of the respective sectors are high leading to restoration of a given sector's symmetry.
+We now turn to the gravitational wave signatures of our setup.
+At high temperature, each of the hidden sectors has QCD in the quark/gluon phase, but at temperatures around $\Lambda_{\rm QCD,i}$, the sector undergoes a phase transition into the hadron phase, where we compute $\Lambda_{\rm QCD,i}$ for the different sectors in Sec.~\ref{sec:dQCD}.
+As discussed in that section, this phase transition will be strongly first order (SFOPT) if certain regions of parameter space, which will generate gravitational waves.
+
+%Right after reheating, the temperatures of the respective sectors are high leading to restoration of a given sector's symmetry.
 An example being the SM's $SU(3) \times SU(2) \times U(1)$ symmetry being restored as the scalar potential's vev becomes global minimum.
@@
 
-Once the temperature reaches the critical temperature the SFOPT will occur, at which bubbles of the new phase will start to nucleate.
+A SFOPT proceeds through bubble nucleation, where bubbles of the hadron form in the vacuum of quark phase.
 These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.
-These bubbles are described by the following Euclidean action
+These bubbles are described by the following Euclidean action~\cite{}
+%
+\begin{equation}
+S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg],
+\end{equation}
+\draftnote{What is $\phi$?} where the time component has been integrated out due to finite temperature effects.
+The system has solutions with a $O(3)$ symmetry.
+We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood.
+Some authors~\cite{} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining $SU(N)$ .
 
+The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
+A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation,
 \begin{equation}
-S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg]
+\alpha = \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
+\label{eq:alpha}
+\end{equation}
+with $\epsilon$ being calculable from the scalar potential.
+Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  $\epsilon$ should approximately be equal to the energy density of the hidden sector going through the PT.
+\draftnote{What about the energy in photons, neutrinos, etc?}
+The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) \draftnote{define $g_*$}.
+It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
+\begin{equation}
+g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
+\end{equation}
+with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}).
+The bounds from effective number of neutrinos mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$.
+In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$.
+Some authors \cite{bai, etc} have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian for $SU(6)_{L} \times SU(6)_{R}$ breaking.
+We take the optimistic scenario,
+%
+\begin{equation}
+\alpha \approx \xi^{4} \approx \bigg( \frac{\Lambda_{d}}{T_{\gamma}^{nuc}}\bigg)^4
+\end{equation}
+%
+where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition.
+Another important parameter to characterize the phase transition is its inverse timescale \draftnote{define $\beta$}
+\begin{equation}
+\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
 \end{equation}
 
-Where the time component has been integrated out due to finite temperature effects.
-The system has solutions with a $O(3)$ symmetry.
-We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood.
-Some authors have used the chiral effective lagrangian to calculate a low energy thermalized potential for confining $SU(N)$ .
-
-The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
-A quantity that characterizes the strength of the PT is the ratio of the latent heat and energy density of radiation, at the time of nucleation,
-\begin{equation}
-\alpha = \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30}
-\end{equation}
+\subsection{Production of Gravitational Waves}
+\label{sec:signals}
 
@@
 
-\draftnote{\st{What is $\epsilon$?}} $\epsilon$ is the latent heat released during the phase transition, and is function of the scalar potential.
-Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  $\epsilon$ should approximately be equal to the energy density of the hidden sector going through the PT.
-$g_{*}$ has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
-\begin{equation}
-g_{*} = g_{*,\gamma} + \sum_{i = 1}^{N} g_{*,i} (\xi_{i})^4
-\end{equation}
-It will be seen that for models with a significant number of hidden sectors, that the lack of substantial reheating in adjacent sectors will cause their respective $g_{*}$ corrections to become negligible, $g_{*} \approx g_{*,\gamma}$.
-In the case of dark QCD-like $SU(6)$ chiral  phase transitions, such as in the generic Nnatrualness models, The temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{d})$.
-Some authors [bai, etc] have looked at calculating $\alpha$ through the low energy effective chiral lagrangian for $SU(6)_{L} \times SU(6)_{R}$ breaking.
-We take the optimistic scenario,
-
-\begin{equation}
-\alpha \approx \xi^{4} \approx \bigg( \frac{\Lambda_{d}}{T_{\gamma}^{nuc}}\bigg)^4
-\end{equation}
-
-The inverse timescale of the phase transition can be calculated
-\begin{equation}
-\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
-\end{equation}
-
-%\section{Signals}
-%\label{sec:signals}
 \begin{figure*}[tb]

### 2019-08-23 gwnnDraft02.tex
basic edits

--- 2019-08-22 gwnnDraft02.tex
@@
 Due to the confining nature of QCD, the exact nature of the phase transition is often difficult to ascertain analytically and requires the study of lattice simulations.
-In the SM, it is known that the phase transition is a crossover and does lead to gravitational wave signals~\cite{}.
-In the general case \draftnote{Is this specific to three colours?}, the phase transition can be strongly first order in two regimes~\cite{lattice,SVETITSKY1982423,Pisarski:1983ms}:
+In the SM, it is known that the phase transition is a crossover and does lead to gravitational wave signals~\cite{Aoki:2006we,Bhattacharya:2014ara}.
+In the general case with 3 or more colours, the phase transition can be strongly first order in two regimes~\cite{Panero:2009tv,SVETITSKY1982423,Pisarski:1983ms}:
 \begin{itemize}
@@
 \begin{equation}\label{eqn:critIndex}
-i^c \sim \frac{(m_s m_c m_b m_t)^{4/25}(\Lambda_{(6)})^{42/25}}{( m_u)^{58/25}} \sim 10^5
-\end{equation}
-%
-\draftnote{please check, I get this:}
-\begin{equation}\label{eqn:critIndex}
-i^c \sim \frac{(m_s m_c m_b m_t)^{4/21}(\Lambda_{(6)})^{2}}{( m_u)^{58/21}} \sim 10^6
+i^c \sim \frac{(m_s m_c m_b m_t)^{4/21}(\Lambda_{(6)})^{2}}{( m_u)^{58/21}} \sim 10^6.
 \end{equation}
@@
 \begin{equation}
-m_{\pi}^i \sim \sqrt{\frac{m_a^i+m_b^i}{m_a + m_b}} m_{\pi}.
+m_{\pi}^i \sim \sqrt{\frac{m_a^i+m_b^i}{m_u + m_d}} m_{\pi}.
 \label{eq:ith_pion_mass}
 \end{equation}
-Here, $a$ and $b$ denote the component quark flavours. \draftnote{Shouldn't the denominator be up and down quarks in the SM?}
+Here, $a$ and $b$ denote the component quark flavours.
 
@@
 \end{equation}
-\draftnote{what does this sentence mean?} Note that the cross-quartic couplings are absent, suppressed by a very small coupling.
+Note that cross-quartic couplings of the form $\kappa\vert H_i\vert^2\vert H_j\vert^2$ that could potentially ruin the spectrum of $N$naturalness are absent, taken to be suppressed by a very small coupling.
 Effective Lagrangians for the two different types of sectors present in this theory can be obtained by integrating out of the Higgs bosons in every sector:
@@
 Here, $g_h$ represents the effective number of relativistic degrees of freedom for the hidden sector\footnote{$g_h = N_{\rm boson} + 7 N_{\rm fermion}/8$.} when the hidden sector has a temperature $T_h = \xi_h T_\gamma$.
-\draftnote{These should be defined at the time of CMB decoupling?}
+In this analysis, these temperatures are taken at CMB decoupling.
 %Contours for Eq. (\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:neff}. 
@@
 \end{equation} 
-For a dark sector with one relativistic degree of freedom, its temperature must be $\sim T_{\rm SM}/2$ to not be excluded.
-This sector would have an energy density $\rho \sim 0.1 \rho_{\rm SM}$.
-\draftnote{check!}
+For a dark sector with one relativistic degree of freedom, its temperature must be $\sim 0.6\, T_{\rm SM}$ to not be excluded.
+This sector would have an energy density $\rho \sim 0.36\, \rho_{\rm SM}$.
 
@@
 \begin{equation}
-\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{(T_{RH_{E1}}/T_{RH})}{i^2}\right)^4 \sim 10^{-4},
+\Delta N_{eff} = \sum_i \frac{4}{7}\left(\frac{11}{4}\right)^{4/3}g_{i} \left(\frac{(T_{RH_{E1}}/T_{RH})}{i^{1/2}}\right)^4 \sim 10^{-4},
 \end{equation}     
-\draftnote{doesn't $\rho$ go like $i^{-2}$ rather than $\xi$ going like $i^{-2}$??}
 with $T_{RH_{E1}}/T_{RH}$ being the ratio of the reheat temperatures of the 1st exotic sector and our own sector ($0.06$ in standard $N$naturalness with $r = 1$).
@@
 Since $N_{eff}$ constraints remain our strongest cosmological bounds for massive standard sectors, our starting point for exploring the limits of high transition temperatures is Eq.~(\ref{eqn:DeltaNeff}).
-Assuming heavy, standard sectors (with the only relativistic particles being photons and neutrinos) we can saturate the bounds of Eq.~(\ref{eqn:NeffBounds}) and solve for the maximum energy density allowed for any number of sectors:
+Assuming heavy, standard sectors (with the only relativistic particles being photons and neutrinos) we can saturate the bounds of Eq.~(\ref{eqn:NeffBounds}) and solve for the maximum temperature allowed for any number of sectors:
 \begin{equation}\label{eqn:energyDensityAllowed}
 \begin{split}
-\rho_i &\sim 0.25 \rho_{SM} \,\,\,\,\, \mathrm{1}\,\, \mathrm{hidden}\,\, \mathrm{sector},
+T_i &\sim 0.25 \,T_{SM} \,\,\,\,\, \mathrm{1}\,\, \mathrm{hidden}\,\, \mathrm{sector},
 \\
-\rho_i &\sim 0.17 \rho_{SM} \,\,\,\,\, \mathrm{5} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
+T_i &\sim 0.17 \,T_{SM} \,\,\,\,\, \mathrm{5} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
 \\
-\rho_i &\sim 0.14 \rho_{SM} \,\,\,\,\, \mathrm{10} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
+T_i &\sim 0.14 \,T_{SM} \,\,\,\,\, \mathrm{10} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
 \\
-\rho_i &\sim 0.08 \rho_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
+T_i &\sim 0.08 \,T_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
 \end{split}
 \end{equation}
-where all the hidden sectors have the same temperature as one another. \draftnote{right?}
+where all the hidden sectors have the same temperature as one another.
 
@@
 The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures.
-The bottom right (left) are examples of exotic sectors, discussed in section V, with sectors reheated at $\rho \sim 0.25\rho_{SM}$ ($\rho \sim 0.17\rho_{SM}$ ).
+The bottom right (left) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ).
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.

### 2019-08-23 gwnnDraft02.tex

--- 2019-08-23 gwnnDraft02.tex
@@
 %when the hidden sector has a temperature $T_h = \xi_h T_\gamma$. \draftnote{These should be defined at the time of CMB decoupling?} 
+>>>>>>> 464ecaed5b4d39fcd253405584da9729b07eec68
 %Contours for Eq. (\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:neff}. 

### 2019-08-23 gwnnDraft02.tex
more edits and fixed temp ratios to current bounds
minor temp change
drafting in GW section

@@
 Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
-This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu}.
+This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu,}.
 
@@
 
+Future CMB experiments~\cite{} will improve the bound from Eq.~(\label{eqn:NeffBounds}) by about an order of magnitude.
+This could significantly reduce the allowed temperature ratio of any hidden sector, or alternatively could provide evidence for such sectors in a way that is complementary to the gravitational wave signatures described below.
+
 For fully decoupled sectors that never enter (or reenter) thermal equilibrium with our sector, we obtain additional contributions to $N^{SM}_{eff}$ \cite{Breitbach:2018ddu}
@@
 %when the hidden sector has a temperature $T_h = \xi_h T_\gamma$. \draftnote{These should be defined at the time of CMB decoupling?} 
->>>>>>> 464ecaed5b4d39fcd253405584da9729b07eec68
 %Contours for Eq. (\ref{eqn:DeltaNeff1hs}) at various temperature ratios as well as CMB bounds are plotted in Fig.~\ref{fig:neff}. 
@@
 For a dark sector with one relativistic degree of freedom, its temperature must be $\sim 0.6\, T_{\rm SM}$ to not be excluded.
-This sector would have an energy density $\rho \sim 0.36\, \rho_{\rm SM}$.
+This sector would have an energy density $\rho \sim 0.036\, \rho_{\rm SM}$.
 
@@
 \begin{split}
-T_i &\sim 0.25 \,T_{SM} \,\,\,\,\, \mathrm{1}\,\, \mathrm{hidden}\,\, \mathrm{sector},
+T_i &\sim 0.38 \,T_{SM} \,\,\,\,\, \mathrm{1}\,\, \mathrm{hidden}\,\, \mathrm{sector},
 \\
-T_i &\sim 0.17 \,T_{SM} \,\,\,\,\, \mathrm{5} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
+T_i &\sim 0.25 \,T_{SM} \,\,\,\,\, \mathrm{5} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
 \\
-T_i &\sim 0.14 \,T_{SM} \,\,\,\,\, \mathrm{10} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
+T_i &\sim 0.21 \,T_{SM} \,\,\,\,\, \mathrm{10} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
 \\
-T_i &\sim 0.08 \,T_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
+T_i &\sim 0.12 \,T_{SM} \,\,\,\,\, \mathrm{100} \,\,\mathrm{hidden}\,\, \mathrm{sectors},
 \end{split}
@@
 \section{Gravitational Wave Signals}
-
-\draftnote{exotic sector computation}
-These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
-Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh},
-\begin{equation}\label{eqn:critPTstrength}
-\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
-\end{equation} 
-for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
-
-It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.
-
-Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
-
-Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
-Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.
-
-\draftnote{---------}
 
@@
 
+Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  The energy in gravitational waves can be parameterized by \draftnote{Define $\Omega$ here}
+The three leading order contributions to the GW power spectrum are as follows:
+\begin{itemize}
+\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration.
+With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$.
+\draftnote{Define $\alpha_{\infty}$}
+\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ \draftnote{\st{Define $\beta$ somewhere}} enhanced gravitational waves.
+With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
+\item \textbf{Magnetohydrodynamics contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves.
+With efficiency factor $\kappa_{
+turb} \approx 0.1 \kappa_{v} $.
+\end{itemize}
+The total gravitational wave power spectrum \draftnote{Is $\Omega$ really a power spectrum? Isn't just an energy density?} is a linear combination of the three contributions,
+\begin{equation}
+h^2\Omega_{GW} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
+\end{equation}
+In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$.
+
+\draftnote{Properly stich these paragraphs in here.}
+These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
+Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh},
+\begin{equation}\label{eqn:critPTstrength}
+\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
+\end{equation} 
+for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
+
+It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.
+
+Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+
+Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.
+
+As shown in section IV, the mass spectrum from the dark QCD chiral breaking sectors is such that the runaway bubble condition is satisfied ($\alpha >\alpha_{\infty}$).
+In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{GW} \approx h^2\Omega_{\phi}$.
+The form of the GW power spectrum at the time of nucleation is given as,
+
+\begin{equation}
+h^2\Omega_{GW}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
+\end{equation}
+Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
+$S(f)$ is the frequency spectrum, \draftnote{What is the difference between $S(f)$ and $\Omega(f)$?} and a parametric from has been found through numerical simulations~\cite{} of bubble wall collisions.
+\begin{equation}
+S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
+\end{equation}
+The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.
+Depending on the model, \draftnote{How does it depend on the model?
+What goes into the below equation?} the various hidden sectors can phase transition at different scales and therefore temperatures, cause a shift in the GW spectrum's peak frequency given by~\cite{},
+
+\begin{equation}
+f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}}
+\end{equation}
+
+\draftnote{\st{Define $g_*$}} Where $g_*$  is calculated using Eq.(12) \draftnote{Use Latex tags for equation referencing!}, although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.
+Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
+In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$.
+As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{GW}^{*}(f)$, will redshift to today's value $\Omega_{GW}^{0}(f) = \mathcal{A}\, \Omega_{GW}^{*}((a_{0}/a) f) $.
+The Redshift factor, $\mathcal{A}$, is related to the ratio of scale factors at the time of production and observation, and only scales with the relativistic degrees of freedom.
+\draftnote{ $ \mathcal{A} = a_{0}/a$??} Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,
+
+\begin{equation}
+\Omega_{GW}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{GW}^{i,*}((a_{0}/a)_{i} f) 
+\end{equation}
+
+It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within Nnatrualness or other decoupled hidden sector models.
+In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar.
+This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.
+We can also see that the frequency dependence in the spectrum takes the form of $f/f_{p}$, this causes a cancellation of the redshifting factors in the ratios.
+As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
+This is seen in figures \ref{}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
+The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
+Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.
+
 \begin{figure}[tb]
@@
 \end{figure*}
-Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  The three leading order contributions to the GW power spectrum are as follows:
-\begin{itemize}
-\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration.
-With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$.
-\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ \draftnote{\st{Define $\beta$ somewhere}} enhanced gravitational waves.
-With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
-\item \textbf{Magnetohydrodynamics contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves.
-With efficiency factor $\kappa_{
-turb} \approx 0.1 \kappa_{v} $.
-\end{itemize}
-The total gravitational wave power spectrum \draftnote{Is $\Omega$ really a power spectrum? Isn't just an energy density?} is a linear combination of the three contributions,
-\begin{equation}
-h^2\Omega_{GW} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
-\end{equation}
-In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$.
-As shown in section IV, the mass spectrum from the dark QCD chiral breaking sectors is such that the runaway bubble condition is satisfied ($\alpha >\alpha_{\infty}$).
-In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{GW} \approx h^2\Omega_{\phi}$.
-The form of the GW power spectrum at the time of nucleation is given as,
 
-\begin{equation}
-h^2\Omega_{GW}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
-\end{equation}
-Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
-$S(f)$ is the  frequency spectrum, and a parametric from has been found through numerical simulations of bubble wall collisions.
-\begin{equation}
-S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
-\end{equation}
-The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.
-Depending on the model, the various hidden sectors can phase transition at different scales and therefore temperatures, cause a shift in the GW spectrum's peak frequency given by,
+\subsection{Detection of Stochastic Graviational Waves}
 
-\begin{equation}
-f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}}
-\end{equation}
-
-\draftnote{\st{Define $g_*$}} Where $g_*$  is calculated using Eq.(12), although, due to the lack of substantial reheating into the hidden sectors, the first term is dominant.
-Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
-In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$.
-As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{GW}^{*}(f)$, will redshift to today's value $\Omega_{GW}^{0}(f) = \mathcal{A}\, \Omega_{GW}^{*}((a_{0}/a) f) $.
-\draftnote{\st{Define $\mathcal{A}$}}.The Redshift factor,$\mathcal{A}$, is related to the ratio of scale factors at the time of production and observation, and only scales with the relativistic degrees of freedom.
-Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,
-
-\begin{equation}
-\Omega_{GW}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{GW}^{i,*}((a_{0}/a)_{i} f) 
-\end{equation}
-
-It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within Nnatrualness or other decoupled hidden sector models.
-In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar.
-This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.
-We can also see that the frequency dependence in the spectrum takes the form of $f/f_{p}$, this causes a cancellation of the redshifting factors in the ratios.
-As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
-This is seen in figures \ref{}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
-The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
-Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.
+Put description of calculation of experimental curves here.
 

### 2019-08-26 gwnnDraft02.tex
more minor edits
new plots
email address
added additional refs and fixed some minor points

@@
 PaulSmith3@cmail.carleton.ca \\
+Dylan.linthorne@carleton.ca \\
+stolar@physics.carleton.ca
 }
@@
 Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
-This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu,}.
+This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu,Bertone:2019irm,Caputo:2019wsd,Helmboldt:2019pan,Fairbairn:2019xog,Bai:2018dxf,Baldes:2018emh,Croon:2018erz,Geller:2018mwu,Heikinheimo:2018esa,Aoki:2017aws,Bernal:2017kxu,Acharya:2017szw,Tsumura:2017knk,Dienes:2016vei,Hardy:2016mns,Addazi:2016fbj,Jaeckel:2016jlh}.
 
@@
 This is in good agreement with the $2\sigma$ bounds from studies of the Cosmic Microwave Background (CMB) by Planck combined with baryon acoustic oscillations (BAO) measurements \cite{Aghanim:2018eyx}:
-\begin{equation}\label{eqn:NeffBounds}
+\begin{equation}\label{eqn:neffBounds}
 N_{eff} = 2.99^{+0.34}_{-0.33}.
@@
 
-Future CMB experiments~\cite{} will improve the bound from Eq.~(\label{eqn:NeffBounds}) by about an order of magnitude.
+Future CMB experiments~\cite{Abazajian:2016yjj} will improve the bound from Eq.~(\ref{eqn:neffBounds}) by about an order of magnitude.
 This could significantly reduce the allowed temperature ratio of any hidden sector, or alternatively could provide evidence for such sectors in a way that is complementary to the gravitational wave signatures described below.
@@
 This means that for sectors with small and moderate $i$, we can use Eqs.~(\ref{eqn:exoticFM}) and~(\ref{eq:ith_pion_mass}) to see that the pions will be non-relativistic  leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.
-\draftnote{Pions are not decoupled at BBN time, does this in any way affect the analysis?} For very large $i$, the pions can be much lighter, but those sectors also have very little energy in them in the standard reheating scenario.
+For very large $i$, the pions can be much lighter, but those sectors also have very little energy in them in the standard reheating scenario.
 
@@
 This increase is typically not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.
-
-\draftnote{What is temperature ratio for random reheating scenario?}
 
@@
 In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the cirtical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale.
+
  %of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}.

### 2019-09-03 gwnnDraft02.tex
signal updated

--- 2019-08-23 gwnnDraft02.tex
@@
 PaulSmith3@cmail.carleton.ca \\
+Dylan.linthorne@carleton.ca \\
 }
@@
 %
-\begin{equation}
+\begin{equation}\label{eqn:EuclideanAction}
 S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg],
 \end{equation}
-\draftnote{What is $\phi$?} where the time component has been integrated out due to finite temperature effects.
+where the time component has been integrated out due to finite temperature effects.
 The system has solutions with a $O(3)$ symmetry.
+$\phi$ is the symmetry breaking scalar feild with a non-zero vev.
+In the case of the chiral phase transition, the scalar field breaking the SU$(6)_{R}$ $ \times$ SU$(6)_{L}$ chiral symmetry is the effective dark quark condensate $\phi \sim \langle q\bar{q} \rangle$.
 We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood.
-Some authors~\cite{} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining $SU(N)$ .
+Some authors~\cite{} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining SU$(N)$ .
 
 The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
-A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation,
+Assuming that the SM is radiation dominated, A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation,
 \begin{equation}
-\alpha = \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
+\alpha     \equiv  \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
 \label{eq:alpha}
@@
 \draftnote{What about the energy in photons, neutrinos, etc?}
-The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) \draftnote{define $g_*$}.
+The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors.
 It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
-\begin{equation}
+\begin{equation}\label{eqn:RelaDOF}
 g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
@@
 In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$.
-Some authors \cite{bai, etc} have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian for $SU(6)_{L} \times SU(6)_{R}$ breaking.
+Some authors \cite{bai, etc} have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian for $\textrm{SU(6)}_{L} \times \textrm{SU(6)}_{R}$ breaking.
 We take the optimistic scenario,
@@
 \begin{equation}
-\alpha \approx \xi^{4} \approx \bigg( \frac{\Lambda_{d}}{T_{\gamma}^{nuc}}\bigg)^4
+\alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4
 \end{equation}
@@
 where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition.
-Another important parameter to characterize the phase transition is its inverse timescale \draftnote{define $\beta$}
+Another important parameter to characterize the phase transition is its inverse timescale, $\beta$.
+The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),
+
 \begin{equation}
-\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
+\beta  \equiv \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
+\end{equation}
+
+The ratio of $\beta$ and the hubble constant, at the time of nucleation, $H$ controls the strength of the GW signal,
+
+\begin{equation}
+\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dT}\bigg|_{T = T^{nuc}}
 \end{equation}
@@
 
-Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  The energy in gravitational waves can be parameterized by \draftnote{Define $\Omega$ here}
+Gravitational waves are produced with contributions from different components of the SFOPT's evolution.
+The spectral energy density in gravitational waves can be parameterized by $\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{\textrm{d} \rho_{\textrm{GW}}(f) }{\textrm{dlog}(f)}$, where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density to not over close the universe.
 The three leading order contributions to the GW power spectrum are as follows:
@@
 With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$.
-\draftnote{Define $\alpha_{\infty}$}
-\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ \draftnote{\st{Define $\beta$ somewhere}} enhanced gravitational waves.
+\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves.
 With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
-\item \textbf{Magnetohydrodynamics contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves.
+\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves.
 With efficiency factor $\kappa_{
@@
 \end{itemize}
-The total gravitational wave power spectrum \draftnote{Is $\Omega$ really a power spectrum? Isn't just an energy density?} is a linear combination of the three contributions,
-\begin{equation}
-h^2\Omega_{GW} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
-\end{equation}
-In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$.
 
-\draftnote{Properly stich these paragraphs in here.}
-These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
+Where $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
 Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh},
@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition. 
+Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
 
-It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.
-
-Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+The total gravitational wave signal is a linear combination of the three contributions,
+\begin{equation}
+h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
+\end{equation}
+In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$.
 
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
-Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.
-
-As shown in section IV, the mass spectrum from the dark QCD chiral breaking sectors is such that the runaway bubble condition is satisfied ($\alpha >\alpha_{\infty}$).
-In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{GW} \approx h^2\Omega_{\phi}$.
+Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
+In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
 The form of the GW power spectrum at the time of nucleation is given as,
@@
 \begin{equation}
-h^2\Omega_{GW}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
+h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
 \end{equation}
 Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
-$S(f)$ is the frequency spectrum, \draftnote{What is the difference between $S(f)$ and $\Omega(f)$?} and a parametric from has been found through numerical simulations~\cite{} of bubble wall collisions.
-\begin{equation}
+$S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{} of bubble wall collisions.
+\begin{equation}\label{eqn::spectralshape}
 S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
@@
 The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.
-Depending on the model, \draftnote{How does it depend on the model?
-What goes into the below equation?} the various hidden sectors can phase transition at different scales and therefore temperatures, cause a shift in the GW spectrum's peak frequency given by~\cite{},
+The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{},
 
@@
 
-\draftnote{\st{Define $g_*$}} Where $g_*$  is calculated using Eq.(12) \draftnote{Use Latex tags for equation referencing!}, although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.
+Where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.
 Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
 In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$.
-As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{GW}^{*}(f)$, will redshift to today's value $\Omega_{GW}^{0}(f) = \mathcal{A}\, \Omega_{GW}^{*}((a_{0}/a) f) $.
-The Redshift factor, $\mathcal{A}$, is related to the ratio of scale factors at the time of production and observation, and only scales with the relativistic degrees of freedom.
-\draftnote{ $ \mathcal{A} = a_{0}/a$??} Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,
+As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $.
+The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{},
 
+\begin{equation}\label{eqn::redshifting}
+\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2
+\end{equation}
+where $a$ ($a_{0}$)  and $H$ ($H_{0}$) are the scale factor and Hubble constant at the time of nucleation (observation), respectfully.
+Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW signal that would be measured today is given by the coherent sum,
 \begin{equation}
-\Omega_{GW}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{GW}^{i,*}((a_{0}/a)_{i} f) 
+\Omega_{\textrm{GW}}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
 \end{equation}
-
 It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within Nnatrualness or other decoupled hidden sector models.
@@
 This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.
-We can also see that the frequency dependence in the spectrum takes the form of $f/f_{p}$, this causes a cancellation of the redshifting factors in the ratios.
-As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
-This is seen in figures \ref{}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
-The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
-Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.
 
-\begin{figure}[tb]
+\begin{figure}[h!]
 \centering
@@
 The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+\label{fig::Nnatural}
 \end{figure}
+Applying this to the standard reheating scenario of Nnatrualness, introduced in [], we get GW signals as seen in figure (\ref{fig::Nnatural}).
+Plotted are the individual contributions to the signal from each phase transistioned sector, as well as the coherent sum of all sectors.
+Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal.
+The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in the following section.
+Notice that the total signal is dominated by the first sectors contribution.
+This is caused by the quartic temperature ratio suppression in Eq.
+(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors.
+Such a suppression leads to standard Nnatrualness evading future detector thresholds by a few orders of magnitude in units of energy density.
+This is not the case if we neglect the standard reheaton scenario and consider the generalized reheating scenarios of section [ref].
+
+Assuming all else equal, we use the temperature schemes from Eq.
+(\ref{eqn:energyDensityAllowed}) to produce the plots in figure (\ref{fig:Haa}).
+In all cases, the summed GW signal is detectable by one or more proposed interferometers.
+The frequency dependence in Eq.
+\ref{eqn::spectralshape} takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
+As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
+This is seen in figure (\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
+The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
+Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.
 
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
 \label{fig:Haa}
@@
 
-Put description of calculation of experimental curves here.
+A unpolarized stocastic gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA).
+These interferometers/PTAs quote their experimental sensistivies in terms of spectral noise curves, $S_{\textrm{eff}}(f)$, which can be translated into units of energy density through $h^2 \Omega_{\textrm{eff}}(f) = \frac{2\pi^2}{3H^2}f^3 S_{\textrm{eff}}(f)$.
+The cross correlated SNR for a specefied experimental setup is~\cite{}
+\begin{equation}\label{eqn::SNR}
+\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2,
+\end{equation}
+Where $T$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
+
+GW signals produced from an early cosmological phase transition would be seen as a stocastic background.
+Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{}.
+the PSI curves are constructed using information from the power law form of the signal,
+\begin{equation}
+h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}
+\end{equation}
+where $\beta$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities.
+
+The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\beta \in (-8,-7,-6, ...
+, 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$.
+Each curve will lay tangent to the PSI curve, more formally,
+\begin{equation}
+h^2 \Omega_{\textrm{PLI}} = \max\limits_{\beta}\bigg[ h^2 \Omega_{\beta}\bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}  \bigg].
+\end{equation}
 

### 2019-09-03 gwnnDraft02.tex
signal updated

@@
 \newcommand{\draftnote}[1]{{\bf\color{blue} #1}}
-
 \newcommand{\cO}{{\cal O}}
@@
 \newcommand{\cM}{{\cal M}}
-
 %References  
@@
 \newcommand{\tref}[1]{Table~\ref{tab:#1}}
-
 %\title{\LARGE{{\bf{Piled up gravitational waves:} \\
@@
 \author{{\bf {Paul Archer-Smith, Dylan Linthorne, and Daniel Stolarski}}}
-
 \affiliation{
@@
 }
-
 \email{
@@
 Dylan.linthorne@carleton.ca \\
+stolar@physics.carleton.ca
 }
-
 \begin{abstract}
@@
 \end{abstract}
-
 \maketitle
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:intro} 
-
 The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe.
@@
 Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.
-
 Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
-This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu,}.
-
+This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu,Bertone:2019irm,Caputo:2019wsd,Helmboldt:2019pan,Fairbairn:2019xog,Bai:2018dxf,Baldes:2018emh,Croon:2018erz,Geller:2018mwu,Heikinheimo:2018esa,Aoki:2017aws,Bernal:2017kxu,Acharya:2017szw,Tsumura:2017knk,Dienes:2016vei,Hardy:2016mns,Addazi:2016fbj,Jaeckel:2016jlh}.
 In this work, we explore the possibility of having multiple decoupled hidden sectors.
@@
 others?).
-
 Motivated by solutions to the hierachy problem, we consider hidden sectors with the same particle content as the Standard Model that have all dimensionless couplings (defined at some high scale) equal to those of the Standard Model.
@@
 This simple ansatz can lead to very rich phenomenology and interesting gravitational wave spectra, but we stress that it is only a starting point for exploring the space of theories with multiple hidden sectors.
-
 In this setup, there are two qualitatively different kinds of sectors:
@@
 We will also explore alternative parameterizations of reheating that satisfy this condition.
-
 In all the above models, there is some energy in the hidden sectors, and these sectors undergo thermal evolution independent of the SM sector.
@@
 This does not occur at either the electroweak or QCD phase transition in the SM, but as we will show, it does happen in some standard sectors, and in \textit{all} exotic sectors that reheat above the QCD phase transition.
-
 This work is organized as follows...
@@
 \label{sec:nn}
-
 %Beginning with the work of Pedro Schwaller \cite{Schwaller:2015tja} and continuing through the work of many others \cite{everyoneelse}, strong first order phase transitions for SU(N) dark sectors with arbitrary numbers of flavours have been explored as a source of gravitational waves.
@@
 \ref{sec:dQCD}.
-
 %\subsection{NNaturalness}
-
 We consider the following Lagrangian as in~\cite{Arkani-Hamed:2016rle}:
@@
 The one exception to this is that ``our" sector must consist of the Standard Model.
-
 From the above Lagrangians, the Higgs in sectors with $i \geq 0$ will get a vev given by:
@@
 \ref{sec:dQCD}.
-
 The ``exotic sectors'' with $i<0$ provide a radical departure from our own.
@@
 \ref{sec:gw}.
-
 \section{QCD Phase Transition}
@@
 %\end{figure*}
-
 We now study the nature of the QCD phase transition across the different sectors.
@@
 In the SM, the up and down quarks are light, but the strange is not sufficiently light for an SFOPT.
-
 % The results of these studies on the nature of QCD phase transitions is summarized in the so-called ``Columbia" plot (Fig.
@@
 Both the Yang-Mills and massless limit arguments can be generalized to SU$(N \geq 3)$: coupling both with the additional restriction that we avoid the conformal window indicates that strong first order phase transitions can occur if we have $n = 0$ (pure Yang-Mills) or $3 \leq n < 4N$ (light quark limit) very light flavours.
-
 For the standard sectors in our setup, the quark masses increase with increasing vev, so for sufficiently large $i$, all the quarks will be heavier than $\Lambda_{QCD}$,\footnote{$\Lambda_{QCD}$ does vary with $i$, but the sensitivity is very weak as we will see below.} and those large $i$ sectors will undergo an SFOPT if they are reheated above the the confinement scale.
@@
 Conversely, exotic sectors with zero vev feature six very light quarks, so \textit{all} the exotic sectors undergo SFOPT at the temperature of QCD confinement. 
-
 We now calculate the QCD confinement scale for each sector following the same procedure as \cite{Cui:2011wk}.
@@
 In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 5$ in $\overline{MS}$~\cite{PhysRevD.98.030001}.
-
 Because we've set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at high scales for all sectors.
@@
 \end{equation}
-
 Suppressing the $i$'s for notational cleanliness, we can arrive at similar relations at the bottom and charm thresholds
@@
 The process terminates when $\Lambda_i$ for a given scale is larger than the next quark mass threshold (i.e running the scale down arrives at the $\Lambda_{QCD}$ phase transition before reaching the next quark mass scale).
-
 In cosmological terms, we can envision a sector's thermal history unfolding where as the plasma cools below each quark mass threshold, said quarks are frozen out.
 At a certain point, the sector arrives at the QCD phase transition and confinement occurs (provided there are light enough quarks to confine) --- if this occurs when $\geq 3$ quarks are at a much lower scale or all quarks have already frozen out, we get the desired phase transition.
-
 \subsection{Standard Sectors}
-
 As shown in Eq.~(\ref{eqn:vevs}), for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$.
@@
 This, of course, begs the question: at what index $i$ do said phase transitions begin?
-
 %The actual boundary of region of interest on the Columbia plot is not precisely known and further lattice simulations are required to determine exactly where in parameter space cross-over transitions end and first order transitions begin.
@@
 Assuming the up and down quarks of each sector to be of roughly the same scale, we determine what sector $i$ features $\kappa m_u^i \approx \Lambda_{QCD}$.
-
 Using the methods outlined in the prior section we determine $\Lambda_{QCD}$ to have a relevant value of 
@@
 As we will see in Sec.~\ref{sec:reheat}, in the original Nnaturalness setup~\cite{Arkani-Hamed:2016rle}, the energy dumped into the $i$th sector scales as $i^{-1}$, so there will will not be enough energy in the sectors with $i>i^c$ to see a signature of these phase transitions.
-
 %This critical index demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
@@
 As a result, \textcolor{green}{As we will show below?} the gravitational waves generated by the standard large $i$ sectors in $N$naturalness will not generate detectable signatures.
-
 However, if we move away from the original $N$naturalness reheating mechanism and begin exploring mirror sectors with large vevs and with relative energy densities $\rho_i / \rho_{SM} \sim 10\%$, a possibility allowed by current constraints, we can have sectors with relatively high dark QCD scales that produce detectable gravitational waves.
@@
 \ref{sec:gw}.
-
 \subsection{Exotic Sectors}
-
 In every exotic sector the fermion masses are exceptionally light: their masses are generated by dimension six operators with the Higgs integrated out as shown in Eq.~(\ref{eqn:exoticFM}), and are therefore all below the confinement scale.
@@
 These sectors all have six light fermions, so a strong first order phase transition occurs for all exotic sectors at this temperature.
-
 The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6) \,\times$ SU$(6) \rightarrow\,$ SU$(6)$ and thus 35 pseudo-Goldstone bosons (pions).
@@
 Here, $a$ and $b$ denote the component quark flavours. 
-
 \section{Reheating N Sectors}
 \label{sec:reheat}
-
 %\begin{figure*}[tb]
@@
 %\end{figure*}
-
 A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by cosmological constraints, particularly those from number of effective neutrinos ($N_{eff}$).
@@
 Our focus is primarily the production of gravitational waves from multiple sectors and a fermion reheaton does not change the scaling of the energy density of the exotic sectors and thus does not affect expected gravitational wave profiles.
-
 In order to maintain the naturalness of our SM sector, the reheaton coupling is taken to be universal to every sector's Higgs.
@@
 If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$ then we construct a model that behaves as desired.
-
 The appropriate Lagrangian for a scalar reheaton $\phi$ is: 
@@
 with $C_i$ representing numerical coefficients, $g$ the weak coupling constant, and $W^{\mu\nu}$ the SU$(2)$ field strength tensor.
-
 Immediately from Eq.
@@
 with $r_s$ being the ratio of the energy density of the first additional standard sector over the energy density of our sector.
-
 For the exotic sectors, Eq.~(\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$ and is also loop supressed. 
@@
 \end{equation} 
-
 As a final note, in this setup the reheating temperature of the SM, $T_{RH}$, has an upper bound on the order of the weak scale.
@@
 Thus we only consider relatively low reheating temperatures $\lesssim 100$ GeV.
-
 Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we also consider a more general parameterization where sectors are reheated ``randomly" as opposed to in relation to the Higgs mass parameter.
@@
 For these models, the reheating mechanism remains undefined and the results of this section are completely irrelevant.
-
 \section{Constraints}
 \label{sec:constraints}
-
 %\begin{figure}
@@
 %\end{figure}
-
 In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom.
@@
 The effective number of neutrino species, $N_{eff}$, is impacted by these contributions and, as such, is the strictest constraint that must be dealt with when studying these type of multi-phase transition models.
-
 The SM predicts that $N^{SM}_{eff} = 3.046$ \cite{Mangano:2005cc}.
 This is in good agreement with the $2\sigma$ bounds from studies of the Cosmic Microwave Background (CMB) by Planck combined with baryon acoustic oscillations (BAO) measurements \cite{Aghanim:2018eyx}:
-\begin{equation}\label{eqn:NeffBounds}
+\begin{equation}\label{eqn:neffBounds}
 N_{eff} = 2.99^{+0.34}_{-0.33}.
@@
 Because the constraints on $N_{eff}$ are stronger at photon decoupling than at BBN, we can focus purely on the constraints provided by the former.
-
-Future CMB experiments~\cite{} will improve the bound from Eq.~(\label{eqn:NeffBounds}) by about an order of magnitude.
+Future CMB experiments~\cite{Abazajian:2016yjj} will improve the bound from Eq.~(\ref{eqn:neffBounds}) by about an order of magnitude.
 This could significantly reduce the allowed temperature ratio of any hidden sector, or alternatively could provide evidence for such sectors in a way that is complementary to the gravitational wave signatures described below.
-
 For fully decoupled sectors that never enter (or reenter) thermal equilibrium with our sector, we obtain additional contributions to $N^{SM}_{eff}$ \cite{Breitbach:2018ddu}
@@
 This sector would have an energy density $\rho \sim 0.036\, \rho_{\rm SM}$.
-
 %\draftnote{Maybe give what the temperature ratio should be for one standard (or exotic) sector to not be excluded.} 
@@
 \textcolor{green}{$\xi=0.5$ and $g=2$ is not excluded.}
-
 \subsection{Exotic Sector Contributions}
-
 %The original $N$naturalness paper focused on the (stronger) $N_{eff}$ constraints from the additional standard sectors and ignored the exotic sectors altogether \cite{Arkani-Hamed:2016rle}; in contrast, we take the opposite approach.
 Since we're more interested in a more general scenario with multiple dark phase transitions, we focus in on whether zero vev sectors can dodge these $N_{eff}$ bounds.
-
 We begin by computing the constraints on exotic sectors; these are significantly weaker than those for standard sectors~\cite{Arkani-Hamed:2016rle}. 
@@
 This means that for sectors with small and moderate $i$, we can use Eqs.~(\ref{eqn:exoticFM}) and~(\ref{eq:ith_pion_mass}) to see that the pions will be non-relativistic  leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.
-\draftnote{Pions are not decoupled at BBN time, does this in any way affect the analysis?} For very large $i$, the pions can be much lighter, but those sectors also have very little energy in them in the standard reheating scenario.
-
+For very large $i$, the pions can be much lighter, but those sectors also have very little energy in them in the standard reheating scenario.
 %Since all additional sectors are colder than our own, by the time photon decoupling occurs ($T_\gamma \sim 0.39 \,\ev$), the pions of all of these sectors will, in accordance with Eq.~(\ref{eqn:gmor}), have a much higher mass than the sector temperature and thus will have frozen out long before --- leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.
 \draftnote{Pions are not decoupled at BBN time, does this in any way affect the analysis?}
-
 Coupling the number of effective degrees of freedom per sector with the energy density scaling of $\sim 1/m_H^4$ as in Eq.~(\ref{eq:reheat_exotic}) means that the zero vev sectors have small temperature ratios.
@@
 Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.
-
 It should be noted that modifying the exotic sectors' structure (e.g.
@@
 This increase is typically not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.
-
-\draftnote{What is temperature ratio for random reheating scenario?}
-
 \subsection{Generalized Reheating Scenarios}
-
 The generalization of possible reheating mechanisms mentioned in section~\ref{sec:reheat} --- where the reheating mechanism no longer depends on the higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study.
@@
 Crucially, despite this analysis being limited to mirror sectors with large Higgs masses, this analysis pertains to any strong, confining phase transition at high scales.
-
 Since $N_{eff}$ constraints remain our strongest cosmological bounds for massive standard sectors, our starting point for exploring the limits of high transition temperatures is Eq.~(\ref{eqn:DeltaNeff}).
@@
 where all the hidden sectors have the same temperature as one another.
-
 Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own.
 In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the cirtical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale.
-
  %of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}.
@@
 Yes.}
-
 \section{Gravitational Wave Signals}

### 2019-09-12 gwnnDraft02.tex
more references

@@
 We explore the possibility of detecting gravitational waves generated by 1st order phase transitions in multiple dark sectors.
-Nnaturalness is taken as a sample model that features multiple additional sectors, many of which undergo phase transitions that produce gravitational waves.
+$N$naturalness is taken as a sample model that features multiple additional sectors, many of which undergo phase transitions that produce gravitational waves.
 We examine the cosmological history of this framework and determine the gravitational wave profiles generated.
-These profiles are checked against projections of next generation gravitational wave experiments, demonstrating that Nnaturalness can indeed produce unique gravitational wave signatures that will be probed by these future experiments.
+These profiles are checked against projections of next generation gravitational wave experiments, demonstrating that $N$naturalness can indeed produce unique gravitational wave signatures that will be probed by these future experiments.
 \end{abstract}
@@
 In this work, we explore the possibility of having multiple decoupled hidden sectors.
-Large numbers of hidden sectors can solve the hierarchy problem as in the Dvali Redi model~\cite{Dvali:2009ne} or in the more recently explored Nnaturalness~\cite{Arkani-Hamed:2016rle} framework, or in the orbifold Higgs models (maybe?\cite{}).
+Large numbers of hidden sectors can solve the hierarchy problem as in the Dvali Redi model~\cite{Dvali:2009ne} or in the more recently explored $N$naturalness~\cite{Arkani-Hamed:2016rle} framework, or in the orbifold Higgs models (maybe?\cite{}).
 They can also be motivated by dark matter considerations (dynamical dark matter?
@@
 We have taken for simplicity that there equal numbers sectors with positive and negative $m_H^2$, but this assumption does not affect our analysis.
-This Nnaturalness framework can be generalized: the various sectors can possess a wide range of particle content that can be freely selected by the model builder.
+This $N$naturalness framework can be generalized: the various sectors can possess a wide range of particle content that can be freely selected by the model builder.
 The one exception to this is that ``our" sector must consist of the Standard Model.
@@
 As shown in Eq.~(\ref{eqn:vevs}), for standard sectors with increasing index $i$ the vevs of said sectors increase $v_i\propto \sqrt{i}$.
-This leads to increasingly heavy particle spectra for higher sectors --- eventually leading to sectors that are essentially pure Yang-Mills that featuring strong first order phase transitions.
+This leads to increasingly heavy particle spectra for higher sectors --- eventually leading to sectors that are essentially pure Yang-Mills that feature strong first order phase transitions.
 This, of course, begs the question: at what index $i$ do said phase transitions begin?
@@
 \end{equation}
-As we will see in Sec.~\ref{sec:reheat}, in the original Nnaturalness setup~\cite{Arkani-Hamed:2016rle}, the energy dumped into the $i$th sector scales as $i^{-1}$, so there will will not be enough energy in the sectors with $i>i^c$ to see a signature of these phase transitions.
+As we will see in Sec.~\ref{sec:reheat}, in the original $N$naturalness setup~\cite{Arkani-Hamed:2016rle}, the energy dumped into the $i$th sector scales as $i^{-1}$, so there will will not be enough energy in the sectors with $i>i^c$ to see a signature of these phase transitions.
 %This critical index demonstrates that even in the most extreme cases, where first order phase transitions occur with the up quark an order of magnitude less than $\Lambda_{QCD}$, the critical index is still $\sim 1000$.
@@
 Since $N_{eff}$ constraints remain our strongest cosmological bounds for massive standard sectors, our starting point for exploring the limits of high transition temperatures is Eq.~(\ref{eqn:DeltaNeff}).
-Assuming heavy, standard sectors (with the only relativistic particles being photons and neutrinos) we can saturate the bounds of Eq.~(\ref{eqn:NeffBounds}) and solve for the maximum temperature allowed for any number of sectors:
+Assuming heavy, standard sectors (with the only relativistic particles being photons and neutrinos) we can saturate the bounds of Eq.~(\ref{eqn:neffBounds}) and solve for the maximum temperature allowed for any number of sectors:
 \begin{equation}\label{eqn:energyDensityAllowed}
@@
 We now turn to the gravitational wave signatures of our setup.
-At high temperature, each of the hidden sectors has QCD in the quark/gluon phase, but at temperatures around $\Lambda_{\rm QCD,i}$, the sector undergoes a phase transition into the hadron phase, where we compute $\Lambda_{\rm QCD,i}$ for the different sectors in Sec.~\ref{sec:dQCD}.
-As discussed in that section, this phase transition will be strongly first order (SFOPT) if certain regions of parameter space, which will generate gravitational waves.
+At high temperatures, each of the hidden sectors has QCD in the quark/gluon phase, but at temperatures around $\Lambda_{\rm QCD,i}$, the sector undergoes a phase transition into the hadronic phase, where we compute $\Lambda_{\rm QCD,i}$ for the different sectors in Sec.~\ref{sec:dQCD}.
+As discussed in that section, this phase transition will be strongly first order (SFOPT) for certain numbers of light degrees of freedom, which will generate gravitational waves.
+This differs from QCD within the SM sector, as the PT is a crossover and not first order~\cite{Fodor:2001pe}.
 
@@
 
-A SFOPT proceeds through bubble nucleation, where bubbles of the hadron form in the vacuum of quark phase.
+A SFOPT proceeds through bubble nucleation, where bubbles of the hadronic phase form in the vacuum of the quark phase.
 These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.
-These bubbles are described by the following Euclidean action~\cite{}
+These bubbles are described by the following Euclidean action~\cite{Linde:1981zj}
 %
@@
 \end{equation}
-where the time component has been integrated out due to finite temperature effects.
-The system has solutions with a $O(3)$ symmetry.
-$\phi$ is the symmetry breaking scalar feild with a non-zero vev.
-In the case of the chiral phase transition, the scalar field breaking the SU$(6)_{R}$ $ \times$ SU$(6)_{L}$ chiral symmetry is the effective dark quark condensate $\phi \sim \langle q\bar{q} \rangle$.
-We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood.
-Some authors~\cite{} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining SU$(N)$ .
+where the time component has been integrated out due to nucleation occuring, not in vaccum, but in a finite temperature plasma.
+$\phi$ is the symmetry breaking scalar field with a non-zero VEV.
+In the case of the chiral phase transition, the scalar field breaking the SU$(6)_{R}$ $ \times$ SU$(6)_{L}$ chiral symmetry is the effective quark condensate $\phi_{i} \sim \langle q\bar{q} \rangle_{i}$ of the respective sector.
+We leave the thermalized potential $V(\phi, T)$ general., as previous stated, an exact QCD potential at the time of the chiral phase transition is not well understood outside of lattice results.
+Some authors~\cite{Bai:2018dxf} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining SU$(N)$.
 
 The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
-Assuming that the SM is radiation dominated, A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation,
+Assuming that the SM sector is radiation dominated, A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation ~\citep{Espinosa:2010hh} ,
 \begin{equation}
@@
 with $\epsilon$ being calculable from the scalar potential.
-Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  $\epsilon$ should approximately be equal to the energy density of the hidden sector going through the PT.
-\draftnote{What about the energy in photons, neutrinos, etc?}
+Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent head, $\epsilon$ should correspond to the energy density of the hidden sector going through the PT.
 The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors.
@@
 with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}).
-The bounds from effective number of neutrinos mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$.
+The bounds from effective number of neutrinos ~\citep{} mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$.
 In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$.
-Some authors \cite{bai, etc} have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian for $\textrm{SU(6)}_{L} \times \textrm{SU(6)}_{R}$ breaking.
-We take the optimistic scenario,
+Authors \citep{Bai:2018dxf} who have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian have found various upper bounds.
+We take the optimistic scenario where the numerator is bounded above by the symmetry breaking scale,
 %
@@
 where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition.
-Another important parameter to characterize the phase transition is its inverse timescale, $\beta$.
+Another important parameter to characterize the phase transition is its inverse timescale, $\beta$ ~\citep{Caprini:2015zlo}.
 The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),
@@
 
-The ratio of $\beta$ and the hubble constant, at the time of nucleation, $H$ controls the strength of the GW signal,
+The ratio of $\beta$ and the Hubble constant, at the time of nucleation, $H$ controls the strength of the GW signal,
 
@@
 Gravitational waves are produced with contributions from different components of the SFOPT's evolution.
-The spectral energy density in gravitational waves can be parameterized by $\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{\textrm{d} \rho_{\textrm{GW}}(f) }{\textrm{dlog}(f)}$, where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density to not over close the universe.
+It is commonplace to parameterize the spectral energy density in gravitational waves   by $\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{\textrm{d} \rho_{\textrm{GW}}(f) }{\textrm{dlog}(f)}$ \citep{PhysRevD.75.043507}, where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density to not over close the universe.
 The three leading order contributions to the GW power spectrum are as follows:
@@
 \item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration.
-With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$.
+With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514}.
 \item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves.
-With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
+With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$~\citep{PhysRevLett.112.041301}.
 \item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves.
 With efficiency factor $\kappa_{
-turb} \approx 0.1 \kappa_{v} $.
+turb} \approx 0.1 \kappa_{v} $~\citep{PhysRevD.74.063521}.
 \end{itemize}
@@
 In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
-The form of the GW power spectrum at the time of nucleation is given as,
+The form of the GW power spectrum at the time of nucleation is given by ~\citep{Breitbach:2018ddu},
 
@@
 As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $.
-The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{},
+The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},
 
@@
 \end{equation}
-It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within Nnatrualness or other decoupled hidden sector models.
+It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within $N$natrualness or other decoupled hidden sector models.
 In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar.
@@
 \caption{ All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
 \label{fig::Nnatural}
 \end{figure}
-Applying this to the standard reheating scenario of Nnatrualness, introduced in [], we get GW signals as seen in figure (\ref{fig::Nnatural}).
-Plotted are the individual contributions to the signal from each phase transistioned sector, as well as the coherent sum of all sectors.
+Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in figure~(\ref{fig::Nnatural}).
+Plotted are the individual contributions to the signal from each phase transitioned sector, as well as the coherent sum of all sectors.
 Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal.
@@
 (\ref{eq:alpha}) and the large temperature gaps between adjacent sectors.
-Such a suppression leads to standard Nnatrualness evading future detector thresholds by a few orders of magnitude in units of energy density.
-This is not the case if we neglect the standard reheaton scenario and consider the generalized reheating scenarios of section [ref].
+Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density.
+This is not the case if we neglect the standard reheaton scenario and consider the more generalized reheating scenarios of section~\ref{sec:constraints}.
 
 Assuming all else equal, we use the temperature schemes from Eq.
-(\ref{eqn:energyDensityAllowed}) to produce the plots in figure (\ref{fig:Haa}).
+(\ref{eqn:energyDensityAllowed}) to produce the plots in figure~(\ref{fig:Haa}).
 In all cases, the summed GW signal is detectable by one or more proposed interferometers.
-The frequency dependence in Eq.
-\ref{eqn::spectralshape} takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
+The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
 As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
-This is seen in figure (\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
+This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
 The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
 \label{fig:Haa}
@@
 These interferometers/PTAs quote their experimental sensistivies in terms of spectral noise curves, $S_{\textrm{eff}}(f)$, which can be translated into units of energy density through $h^2 \Omega_{\textrm{eff}}(f) = \frac{2\pi^2}{3H^2}f^3 S_{\textrm{eff}}(f)$.
-The cross correlated SNR for a specefied experimental setup is~\cite{}
+The cross correlated SNR for a specefied experimental setup is~\cite{PhysRevD.59.102001}
 \begin{equation}\label{eqn::SNR}
@@
 GW signals produced from an early cosmological phase transition would be seen as a stocastic background.
-Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{}.
+Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}.
 the PSI curves are constructed using information from the power law form of the signal,

### 2019-09-12 gwnnDraft02.tex
refs and signal updates

@@
 \begin{equation}
-\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dT}\bigg|_{T = T^{nuc}}
+\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dT}\bigg|_{T = T^{nuc}}.
 \end{equation}
 
+Due to the lack of a analytic potential, we take $\beta/H$ to a standard value currently seen in the field.
+Again, there has been a lot of work in recent years looking to estimate $\beta/H$ using models such as chiral effective theories and PNJ~\citep{}.
+Although, these studies claim a large range of values and thus a consenes has yet been reached.
 \subsection{Production of Gravitational Waves}
@@
 \item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration.
-With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514}.
+With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514, Huber_2008}.
 \item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves.
@@
 Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
-$S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{} of bubble wall collisions.
+$S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
 \begin{equation}\label{eqn::spectralshape}
@@
 The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.
-The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{},
+The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{Huber_2008},
 
@@
 \includegraphics[scale=.3]{Nnatral.png} 
-\caption{ All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
+\caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}.
+All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
 The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
@@
 These interferometers/PTAs quote their experimental sensistivies in terms of spectral noise curves, $S_{\textrm{eff}}(f)$, which can be translated into units of energy density through $h^2 \Omega_{\textrm{eff}}(f) = \frac{2\pi^2}{3H^2}f^3 S_{\textrm{eff}}(f)$.
-The cross correlated SNR for a specefied experimental setup is~\cite{PhysRevD.59.102001}
+If the experiment uses a single (multiple) detector, the auto-correlated (cross-correlated) SNR is used in comparing to the threshold value $\rho_{th}$.
+LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
+The auto-correlated and cross-correlated SNR are explictely given as~\cite{PhysRevD.59.102001},
 \begin{equation}\label{eqn::SNR}
-\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2,
+\begin{split}
+\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
+\\
+\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
+\end{split}
 \end{equation}
@@
 
+The spectral noise curves used to create the PSI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
+We have assumed a observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
+
 \section{Conclusion}

### 2019-09-13 gwnnDraft02.tex
more references & updates

@@
 
-Due to the lack of a analytic potential, we take $\beta/H$ to a standard value currently seen in the field.
-Again, there has been a lot of work in recent years looking to estimate $\beta/H$ using models such as chiral effective theories and PNJ~\citep{}.
+Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field.
+There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan}.
 Although, these studies claim a large range of values and thus a consenes has yet been reached.
@@
 If the experiment uses a single (multiple) detector, the auto-correlated (cross-correlated) SNR is used in comparing to the threshold value $\rho_{th}$.
-LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
 The auto-correlated and cross-correlated SNR are explictely given as~\cite{PhysRevD.59.102001},
@@
 \end{equation}
-Where $T$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
+Where $T$ is the exposure time of the experiment.
+The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
+LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
 
@@
 The spectral noise curves used to create the PSI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
-We have assumed a observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
+We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
 

### 2019-09-20 gwnnDraft02.tex
drafting and references

@@
 The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe.
-Future experiments~\cite{Crowder:2005nr,Harry:2006fi,Sathyaprakash:2012jk,2017arXiv170200786A,Seto:2001qf,Sato:2017dkf,Janssen:2014dka} will greatly expand the frequency range observable.
-Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Caprini:2015zlo,Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Mazumdar:2018dfl}.
+Future experiments~\cite{Seto:2001qf,Crowder:2005nr,Harry:2006fi,Sathyaprakash:2012jk,Janssen:2014dka,2017arXiv170200786A,Sato:2017dkf} will greatly expand the frequency range observable.
+Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}.
 Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.
 Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
-This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Breitbach:2018ddu,Bertone:2019irm,Caputo:2019wsd,Helmboldt:2019pan,Fairbairn:2019xog,Bai:2018dxf,Baldes:2018emh,Croon:2018erz,Geller:2018mwu,Heikinheimo:2018esa,Aoki:2017aws,Bernal:2017kxu,Acharya:2017szw,Tsumura:2017knk,Dienes:2016vei,Hardy:2016mns,Addazi:2016fbj,Jaeckel:2016jlh}.
+This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Jaeckel:2016jlh,Addazi:2016fbj,Hardy:2016mns,Dienes:2016vei,Tsumura:2017knk,Acharya:2017szw,Bernal:2017kxu,Aoki:2017aws,Heikinheimo:2018esa,Geller:2018mwu,Croon:2018erz,Baldes:2018emh,Bai:2018dxf,Breitbach:2018ddu,Fairbairn:2019xog,Helmboldt:2019pan,Caputo:2019wsd,Bertone:2019irm}.
 In this work, we explore the possibility of having multiple decoupled hidden sectors.
-Large numbers of hidden sectors can solve the hierarchy problem as in the Dvali Redi model~\cite{Dvali:2009ne} or in the more recently explored $N$naturalness~\cite{Arkani-Hamed:2016rle} framework, or in the orbifold Higgs models (maybe?\cite{}).
-They can also be motivated by dark matter considerations (dynamical dark matter?
-others?).
+Large numbers of hidden sectors can solve the hierarchy problem as in the Dvali Redi model~\cite{Dvali:2009ne}, in the more recently explored $N$naturalness~\cite{Arkani-Hamed:2016rle} framework, or in orbifold Higgs models~\cite{Craig:2014aea,Craig:2014roa}.
+They can also be motivated by dark matter considerations~\cite{Dienes:2011ja,Dienes:2011sa,Dienes:2016vei}.
 Motivated by solutions to the hierachy problem, we consider hidden sectors with the same particle content as the Standard Model that have all dimensionless couplings (defined at some high scale) equal to those of the Standard Model.
@@
 This does not occur at either the electroweak or QCD phase transition in the SM, but as we will show, it does happen in some standard sectors, and in \textit{all} exotic sectors that reheat above the QCD phase transition.
+
 This work is organized as follows...
@@
 In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom.
-Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons of these sectors can also be relativistic.
+Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons \draftnote{can't have quarks and baryons} of these sectors can also be relativistic.
 In $N$naturalness this feature is realized quite dramatically: each of the $N$ of sectors possess relativistic degrees of freedom.
@@
 At high temperatures, each of the hidden sectors has QCD in the quark/gluon phase, but at temperatures around $\Lambda_{\rm QCD,i}$, the sector undergoes a phase transition into the hadronic phase, where we compute $\Lambda_{\rm QCD,i}$ for the different sectors in Sec.~\ref{sec:dQCD}.
-As discussed in that section, this phase transition will be strongly first order (SFOPT) for certain numbers of light degrees of freedom, which will generate gravitational waves.
-This differs from QCD within the SM sector, as the PT is a crossover and not first order~\cite{Fodor:2001pe}.
+As discussed in that section, this phase transition will be strongly first order (SFOPT) for certain numbers of light quarks, which will generate gravitational waves.
+This differs from QCD in the SM sector, as the PT is a crossover and not first order~\cite{Fodor:2001pe}.
 
@@
 $\phi$ is the symmetry breaking scalar field with a non-zero VEV.
-In the case of the chiral phase transition, the scalar field breaking the SU$(6)_{R}$ $ \times$ SU$(6)_{L}$ chiral symmetry is the effective quark condensate $\phi_{i} \sim \langle q\bar{q} \rangle_{i}$ of the respective sector.
-We leave the thermalized potential $V(\phi, T)$ general., as previous stated, an exact QCD potential at the time of the chiral phase transition is not well understood outside of lattice results.
-Some authors~\cite{Bai:2018dxf} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining SU$(N)$.
+In the case of the chiral phase transition, the scalar field breaking the SU$(N_f)_{R}$ $ \times$ SU$(N_f)_{L}$ chiral symmetry is the effective quark condensate $\phi_{i} \sim \langle q\bar{q} \rangle_{i}$ of the respective sector.
+We leave the thermalized potential $V(\phi, T)$ general.
+As previously stated, an exact QCD potential at the time of the chiral phase transition is not well understood outside of lattice results.
+In~\cite{Bai:2018dxf} chiral effective Lagrangian was used to calculate a low energy thermalized potential for confining SU$(N)$.
 
 The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
-Assuming that the SM sector is radiation dominated, A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation ~\citep{Espinosa:2010hh} ,
+Assuming that the SM sector is radiation dominated, a quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation~\citep{Espinosa:2010hh} ,
 \begin{equation}
@@
 In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$.
-Authors \citep{Bai:2018dxf} who have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian have found various upper bounds.
+The work of~\citep{Bai:2018dxf} calculated $\alpha$ with an effective chiral Lagrangian have found various upper bounds.
 We take the optimistic scenario where the numerator is bounded above by the symmetry breaking scale,
@@
 where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition.
-Another important parameter to characterize the phase transition is its inverse timescale, $\beta$ ~\citep{Caprini:2015zlo}.
+Another important parameter to characterize the phase transition is its inverse timescale, $\beta$~\citep{Caprini:2015zlo}.
 The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),
@@
 
-Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field.
+Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field~\cite{}.
 There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan}.
-Although, these studies claim a large range of values and thus a consenes has yet been reached.
+\draftnote{Are there other papers?
+One paper is not a lot of work}.
+Although, these studies claim a large range of values and thus a consensus has \draftnote{not?} yet been reached.
 \subsection{Production of Gravitational Waves}
@@
 Gravitational waves are produced with contributions from different components of the SFOPT's evolution.
-It is commonplace to parameterize the spectral energy density in gravitational waves   by $\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{\textrm{d} \rho_{\textrm{GW}}(f) }{\textrm{dlog}(f)}$ \citep{PhysRevD.75.043507}, where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density to not over close the universe.
-The three leading order contributions to the GW power spectrum are as follows:
+It is commonplace to parameterize the spectral energy density in gravitational waves by~\citep{PhysRevD.75.043507}
+\begin{equation}
+\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{d \rho_{\textrm{GW}}(f) }{d \textrm{\,log}(f)} , 
+\end{equation}
+where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density. The three leading order contributions to the GW power spectrum are as follows:
 \begin{itemize}
@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition. 
-Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
+Exotic sectors feature no baryons \draftnote{why??} and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \draftnote{isn't that what we're talking about?}\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
 
@@
 Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
-In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
-The form of the GW power spectrum at the time of nucleation is given by ~\citep{Breitbach:2018ddu},
+In this case, the efficiency factors for sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
+The form of the GW power spectrum at the time of nucleation is given by~\citep{Breitbach:2018ddu},
 
@@
 \end{equation}
-Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
+\draftnote{Why is there a * on the $\Omega$?} Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
 $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
@@
 The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{Huber_2008},
+%
+\begin{equation}
+f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
+\end{equation}
+%
+where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.
 
-\begin{equation}
-f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}}
-\end{equation}
-
-Where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.
 Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
@@
 \end{equation}
-It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within $N$natrualness or other decoupled hidden sector models.
-In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar.
+It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within $N$natrualness or other decoupled hidden sector models.\draftnote{what?} In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar.
 This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).
+\draftnote{The sum curve and the i=5 curve aren't visible.}  }
 \label{fig::Nnatural}
@@
 Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal.
-The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in the following section.
+The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in Section~\ref{sec:detection}.
 Notice that the total signal is dominated by the first sectors contribution.
-This is caused by the quartic temperature ratio suppression in Eq.
-(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors.
+This is caused by the quartic temperature ratio suppression in Eq.~(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors.
 Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density.
-This is not the case if we neglect the standard reheaton scenario and consider the more generalized reheating scenarios of section~\ref{sec:constraints}.
+This is not the case if we consider the more generalized reheating scenarios of section~\ref{sec:constraints}.
 
-Assuming all else equal, we use the temperature schemes from Eq.
-(\ref{eqn:energyDensityAllowed}) to produce the plots in figure~(\ref{fig:Haa}).
+\draftnote{I think we need more details on the scenarios that go into making those plots.} Assuming all else equal, we use the temperature schemes from Eq.~(\ref{eqn:energyDensityAllowed}) to produce the plots in figure~(\ref{fig:Haa}).
 In all cases, the summed GW signal is detectable by one or more proposed interferometers.
@@
 \subsection{Detection of Stochastic Graviational Waves}
+\label{sec:detection}
 

### 2019-09-20 gwnnDraft02.tex
a few quick changes

@@
 In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom.
-Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and baryons \draftnote{can't have quarks and baryons} of these sectors can also be relativistic.
+Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and heavy bosons of these sectors can also be relativistic.
 In $N$naturalness this feature is realized quite dramatically: each of the $N$ of sectors possess relativistic degrees of freedom.
@@
 The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures.
-The bottom right (left) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ).
+The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ).
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
@@
 
+Gravitational wave signals continue to grow in importance as phenomenological si
+
+We can think of these results providing 
+This demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors --- whether there are 1, 5, or more hidden sectors
+
+Further, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.
+
+Questions, of course, still remain: how can the estimations of $\alpha$ and $\beta \ H$ be improved?
+
 %%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-20 gwnnDraft02.tex
pulling stuff

--- 2019-09-13 gwnnDraft02.tex
@@
 PaulSmith3@cmail.carleton.ca \\
-Dylan.linthorne@carleton.ca \\
+DylanLinthorne@cmai.carleton.ca \\
 stolar@physics.carleton.ca
@@
 These sectors all have six light fermions, so a strong first order phase transition occurs for all exotic sectors at this temperature.
-The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6) \,\times$ SU$(6) \rightarrow\,$ SU$(6)$ and thus 35 pseudo-Goldstone bosons (pions).
+The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6)_L \,\times$ SU$(6)_R \rightarrow\,$ SU$(6)$ and thus 35 pseudo-Goldstone bosons (pions).
 The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation~\cite{Gell-Mann,Schwartz:2013pla},
@@
 \begin{split}
-\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
+\rho^2 =  \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
 \\
-\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
+\rho^2 = 2 \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
 \end{split}
 \end{equation}
-Where $T$ is the exposure time of the experiment.
-The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
-LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
+Where $\mathcal{T}$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$. The Big Bang
+Observer (BBO)~\citep{PhysRevD.72.083005} and the DECi-hertz Interferometer Gravitational wave Observatory (DEICIGO)~\citep{Sato_2017} would be built from an array of multiple interferometers, where as  the Laser Interferometer Space Antenna (LISA)~\citep{Audley:2017drz} and B-DEICIGO (scaled down DECIGO)~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers.
 
@@
 , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$.
-Each curve will lay tangent to the PSI curve, more formally,
+Curves generated in this way will lay tangent to the PSI curve, more formally,
 \begin{equation}
@@
 The spectral noise curves used to create the PSI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
-We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
+We have assumed an observation time of $\mathcal{T} = 4 $ years for the interferometers and $\mathcal{T}= 5, 10, 20 $  years for the various stages of SKA.
 

### 2019-09-20 gwnnDraft02.tex
some fixes

--- 2019-09-20 gwnnDraft02.tex
@@
 \section{Gravitational Wave Signals}
-
 \label{sec:gw}
@@
 %Where $T_{i}$ is the temperature of the $i^{th}$ hidden sector, and $T_{\gamma}$ the temperature of the standard model (assuming radiation domination).
-
 We now turn to the gravitational wave signatures of our setup.
@@
 This differs from QCD in the SM sector, as the PT is a crossover and not first order~\cite{Fodor:2001pe}.
-
 %Right after reheating, the temperatures of the respective sectors are high leading to restoration of a given sector's symmetry.
@@
 Depending on the characteristics of the symmetry breaking, the phase transition may be strongly first ordered (SFOPT).
-
 A SFOPT proceeds through bubble nucleation, where bubbles of the hadronic phase form in the vacuum of the quark phase.
@@
 In~\cite{Bai:2018dxf} chiral effective Lagrangian was used to calculate a low energy thermalized potential for confining SU$(N)$.
-
 The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
@@
 The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),
-
 \begin{equation}
@@
 \end{equation}
-
 The ratio of $\beta$ and the Hubble constant, at the time of nucleation, $H$ controls the strength of the GW signal,
-
 \begin{equation}
@@
 \end{equation}
-
 Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field~\cite{}.
@@
 \label{sec:signals}
-
 Gravitational waves are produced with contributions from different components of the SFOPT's evolution.
@@
 \end{itemize}
-
 Where $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
@@
 Exotic sectors feature no baryons \draftnote{why??} and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \draftnote{isn't that what we're talking about?}\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
-
 The total gravitational wave signal is a linear combination of the three contributions,
@@
 In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$. 
-
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
@@
 In this case, the efficiency factors for sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
-The form of the GW power spectrum at the time of nucleation is given by~\citep{Breitbach:2018ddu},
-
+Quantities that are calculated at the time of nucleation are denoted with an asterisk (i.e $h^2\Omega_{\textrm{GW}}^*$), which are evolved to relate to their values at the time of observation.
+The form of the GW energy density at the time of nucleation is given by~\citep{Breitbach:2018ddu},
 \begin{equation}
@@
 \end{equation}
-\draftnote{Why is there a * on the $\Omega$?} Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
+Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
 $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
@@
 where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant. 
-
 Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
@@
 The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},
-
 \begin{equation}\label{eqn::redshifting}
@@
 \begin{equation}
-\Omega_{\textrm{GW}}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
+\Omega_{\textrm{GW}} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
 \end{equation}
@@
 This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.
-
 \begin{figure}[h!]
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).
-\draftnote{The sum curve and the i=5 curve aren't visible.}  }
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}
 \label{fig::Nnatural}
@@
 This is not the case if we consider the more generalized reheating scenarios of section~\ref{sec:constraints}.
-
 \draftnote{I think we need more details on the scenarios that go into making those plots.} Assuming all else equal, we use the temperature schemes from Eq.~(\ref{eqn:energyDensityAllowed}) to produce the plots in figure~(\ref{fig:Haa}).
@@
 Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.
-
 \begin{figure*}[tb]
@@
 \end{figure*}
-
 \subsection{Detection of Stochastic Graviational Waves}
 \label{sec:detection}
-
 A unpolarized stocastic gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA).
@@
 LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
-
 GW signals produced from an early cosmological phase transition would be seen as a stocastic background.
@@
 where $\beta$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities. 
-
 The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\beta \in (-8,-7,-6, ...
@@
 \end{equation}
-
 The spectral noise curves used to create the PSI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
 We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
-
 \section{Conclusion}
 \label{sec:conclusion}
-
 Gravitational wave signals continue to grow in importance as phenomenological si
-
 We can think of these results providing 
 This demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors --- whether there are 1, 5, or more hidden sectors 
-
 Further, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.  
-
 Questions, of course, still remain: how can the estimations of $\alpha$ and $\beta \ H$ be improved?
-
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \appendix
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliography{refs}
-
 \end{document}

### 2019-09-20 gwnnDraft02.tex
First draft of conclusion

--- 2019-09-20 gwnnDraft02.tex
@@
 PaulSmith3@cmail.carleton.ca \\
-DylanLinthorne@cmai.carleton.ca \\
+Dylan.linthorne@carleton.ca \\
 stolar@physics.carleton.ca
@@
 These sectors all have six light fermions, so a strong first order phase transition occurs for all exotic sectors at this temperature.
-The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6)_L \,\times$ SU$(6)_R \rightarrow\,$ SU$(6)$ and thus 35 pseudo-Goldstone bosons (pions).
+The confinement of these sectors directly leads to the production of both baryons and mesons as we have the spontaneous breaking of SU$(6) \,\times$ SU$(6) \rightarrow\,$ SU$(6)$ and thus 35 pseudo-Goldstone bosons (pions).
 The masses obtained through the phase transition can be approximated through the use of a generalization of the Gell-Mann--Oakes--Renner relation~\cite{Gell-Mann,Schwartz:2013pla},
@@
 \begin{split}
-\rho^2 =  \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
+\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
 \\
-\rho^2 = 2 \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
+\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
 \end{split}
 \end{equation}
-Where $\mathcal{T}$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$. The Big Bang
-Observer (BBO)~\citep{PhysRevD.72.083005} and the DECi-hertz Interferometer Gravitational wave Observatory (DEICIGO)~\citep{Sato_2017} would be built from an array of multiple interferometers, where as  the Laser Interferometer Space Antenna (LISA)~\citep{Audley:2017drz} and B-DEICIGO (scaled down DECIGO)~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers.
+Where $T$ is the exposure time of the experiment.
+The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
+LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
 
@@
 , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$.
-Curves generated in this way will lay tangent to the PSI curve, more formally,
+Each curve will lay tangent to the PSI curve, more formally,
 \begin{equation}
@@
 The spectral noise curves used to create the PSI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
-We have assumed an observation time of $\mathcal{T} = 4 $ years for the interferometers and $\mathcal{T}= 5, 10, 20 $  years for the various stages of SKA.
+We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
 
@@
 
-Gravitational wave signals continue to grow in importance as phenomenological si
+As detection capabilities increase, gravitational wave signals continue to grow in importance as phenomenological signatures that can offer us a unique glimpse into the universe as it was in the early epochs.
+The space-based interferometers planned for the next generation of GW experiments will be sensitive enough to begin searching for signals of the cataclysmic disruption of space-time due to SFOPT.
+As we inch closer to these measurements becoming available, it becomes important to develop ways to analyze and understand this data.
 
-We can think of these results providing 
-This demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors --- whether there are 1, 5, or more hidden sectors
+Here, we examined several scenarios (including $N$naturalness) that involve multiple hidden sectors and calculated the GW profiles present.
+Our GW projections unambiguously demonstrate that scenarios with multiple hidden sector SFOPTs can begin to be probed by next generation experiments.
+Further, our results provide a framework for understanding and using GW signals in two opposite ways: first as a unique signal for specific theories featuring multiple SFOPTs and also as a way to explain signals that deviate from a standard power law spectrum.
 
-Further, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.
+In the former case, this demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors.
+Whether a model predicts of the presence of 1, 5, or more hidden sectors, any SFOPT can potentially contribute a GW signal and the sum of these signals can create a unique GW background; ultimately providing another means to test and constrain theories.
 
-Questions, of course, still remain: how can the estimations of $\alpha$ and $\beta \ H$ be improved?
+Shifting to the latter scenario, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.
+Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario --- and gently guide us in the direction of multiple hidden sectors.
+
+%Questions, of course, still abound: how can the %estimations of $\alpha$ and $\beta/H$ be improved?
 

### 2019-09-20 gwnnDraft02.tex
fixed minor abstract point

@@
 We examine the cosmological history of this framework and determine the gravitational wave profiles generated.
-These profiles are checked against projections of next generation gravitational wave experiments, demonstrating that $N$naturalness can indeed produce unique gravitational wave signatures that will be probed by these future experiments.
+These profiles are checked against projections of next generation gravitational wave experiments, demonstrating that multiple hidden sectors can indeed produce unique gravitational wave signatures that will be probed by these future experiments.
 \end{abstract}

### 2019-09-23 gwnnDraft02.tex
add

--- 2019-09-20 gwnnDraft02.tex
@@
 The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors.
-It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
+It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities)
 \begin{equation}\label{eqn:RelaDOF}
-g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
+g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4,
 \end{equation}
@@
 The work of~\citep{Bai:2018dxf} calculated $\alpha$ with an effective chiral Lagrangian have found various upper bounds.
-We take the optimistic scenario where the numerator is bounded above by the symmetry breaking scale,
+We take the optimistic scenario where the numerator is bounded above by the symmetry breaking scale
 %
 \begin{equation}
-\alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4
+\alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4,
 \end{equation}
@@
 \begin{equation}
-\beta  \equiv \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
+\beta  \equiv \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}.
 \end{equation}
@@
 Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field~\cite{}.
-There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan}.
+There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan,Bai:2018dxf}.
 \draftnote{Are there other papers?
 One paper is not a lot of work}.
-Although, these studies claim a large range of values and thus a consensus has \draftnote{not?} yet been reached.
+Although, these studies claim a large range of values and thus a consensus has not yet been reached.
 \subsection{Production of Gravitational Waves}
@@
 Exotic sectors feature no baryons \draftnote{why??} and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \draftnote{isn't that what we're talking about?}\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
-The total gravitational wave signal is a linear combination of the three contributions,
+The total gravitational wave signal is a linear combination of the three contributions:
 \begin{equation}
-h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
+h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} .
 \end{equation}

### 2019-09-25 gwnnDraft02.tex

@@
 Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}.
-Thus searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.
+Thus, searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.
 Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
@@
 The process terminates when $\Lambda_i$ for a given scale is larger than the next quark mass threshold (i.e running the scale down arrives at the $\Lambda_{QCD}$ phase transition before reaching the next quark mass scale).
-In cosmological terms, we can envision a sector's thermal history unfolding where as the plasma cools below each quark mass threshold, said quarks are frozen out.
+In cosmological terms, we can envision a sector's thermal history unfolding, whereas the plasma cools below each quark mass threshold and said quarks are frozen out.
 At a certain point, the sector arrives at the QCD phase transition and confinement occurs (provided there are light enough quarks to confine) --- if this occurs when $\geq 3$ quarks are at a much lower scale or all quarks have already frozen out, we get the desired phase transition.
@@
 From Eq.~(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector.
-If we take Higgs vevs as high as the GUT scale $\sim 10^{16}$ GeV, then we can gave confinement scales as high as $\sim 38 \,\gev$.
+If we take Higgs vevs as high as the GUT scale $\sim 10^{16}$ GeV, then we can get confinement scales as high as $\sim 38 \,\gev$.
 The signals of this sector and other test cases like it are explored in Sec.
@@
 %\end{figure}
-In general, the multi-hidden sector models explored here feature feature of huge number of (nearly) massless degrees of freedom.
+In general, the multi-hidden sector models explored feature a huge number of (nearly) massless degrees of freedom.
 Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and heavy bosons of these sectors can also be relativistic.
@@
 The ratio of $\beta$ and the Hubble constant, at the time of nucleation, $H$ controls the strength of the GW signal,
-\begin{equation}
-\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dT}\bigg|_{T = T^{nuc}}.
+\begin{equation}\label{eqn:BH}
+\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dT}\bigg|_{T = T^{nuc}_h}.
 \end{equation}
-Due to the lack of an analytic potential, we take $\beta/H$ to be a standard value currently seen in the field~\cite{}.
-There has been a lot of work in recent years in the estimation of $\beta/H$ using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models~\citep{Helmboldt:2019pan,Bai:2018dxf}.
-\draftnote{Are there other papers?
-One paper is not a lot of work}.
-Although, these studies claim a large range of values and thus a consensus has not yet been reached.
+Due to the lack of a general analytic QCD potential, it is not possible to use Eq.~(\ref{eqn:BH}) to calculate $\beta/H$.
+There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} which predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments are riddled with assumptions on the potential.
+In more recent work, some authors~\citep{Helmboldt:2019pan,Bai:2018dxf} have attempted to estimate it using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models.
+These studies claim a large range of values and thus a consensus has not yet been reached.
+Under these circumstances, we take the optimistic case in which $\beta/H$ is of order $\mathcal{O}(10)$.
 \subsection{Production of Gravitational Waves}
@@
 \begin{equation}
-\Omega_{\textrm{GW}} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
+\Omega_{\textrm{GW}} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) .
 \end{equation}
-It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within $N$natrualness or other decoupled hidden sector models.\draftnote{what?} In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar.
-This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.
+We assume that the parameters of the SFOPT do not differ between sectors: the relativistic degrees of freedom, phase transition rate, and the dark QCD scale, are all similar.
+This makes the redshifting factor $\mathcal{A}^i$ independent of sector number.
 \begin{figure}[h!]
@@
 \label{sec:conclusion}
-Gravitational wave signals continue to grow in importance as phenomenological si
-We can think of these results providing 
-This demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors --- whether there are 1, 5, or more hidden sectors 
-Further, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.  
-Questions, of course, still remain: how can the estimations of $\alpha$ and $\beta \ H$ be improved?
+
+As detection capabilities increase, gravitational wave signals continue to grow in importance as phenomenological signatures that can offer us a unique glimpse into the universe as it was in the early epochs.
+The space-based interferometers planned for the next generation of GW experiments will be sensitive enough to begin searching for signals of the cataclysmic disruption of space-time due to SFOPT.
+As we inch closer to these measurements becoming available, it becomes important to develop ways to analyze and understand this data.
+
+Here, we examined several scenarios (including $N$naturalness) that involve multiple hidden sectors and calculated the GW profiles present.
+Our GW projections unambiguously demonstrate that scenarios with multiple hidden sector SFOPTs can begin to be probed by next generation experiments.
+Further, our results provide a framework for understanding and using GW signals in two opposite ways: first as a unique signal for specific theories featuring multiple SFOPTs and also as a way to explain signals that deviate from a standard power law spectrum.
+
+In the former case, this demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors.
+Whether a model predicts of the presence of 1, 5, or more hidden sectors, any SFOPT can potentially contribute a GW signal and the sum of these signals can create a unique GW background; ultimately providing another means to test and constrain theories.
+
+Shifting to the latter scenario, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.
+Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario --- and gently guide us in the direction of multiple hidden sectors.
+
+%Questions, of course, still abound: how can the %estimations of $\alpha$ and $\beta/H$ be improved?
+
 %%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-25 gwnnDraft02.tex
edits (Dylan)

@@
 Therefore, the hidden sectors cannot be in thermal equilibrium at any time, and the physics of reheating must dump energy preferentially in the Standard Model sector.
-This can be accomplished in multifield inflation models~\cite{} and with the reheaton method~\cite{Arkani-Hamed:2016rle}.
+This can be accomplished with primodial axion-like particle (ALP) models~\cite{MARSH20161,PhysRevLett.121.201303} and with the reheaton method~\cite{Arkani-Hamed:2016rle}.
 We will also explore alternative parameterizations of reheating that satisfy this condition.
@@
 with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}).
-The bounds from effective number of neutrinos ~\citep{} mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$.
+The bounds from effective number of neutrinos~\citep{Aghanim:2018eyx} mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$.
 In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$.
@@
 Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
-In this case, the efficiency factors for sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
+In this case, the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
 Quantities that are calculated at the time of nucleation are denoted with an asterisk (i.e $h^2\Omega_{\textrm{GW}}^*$), which are evolved to relate to their values at the time of observation.
@@
 In all cases, the summed GW signal is detectable by one or more proposed interferometers.
-The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
+When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
 As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.

### 2019-09-26 gwnnDraft02.tex
minor corrections

@@
 This does not occur at either the electroweak or QCD phase transition in the SM, but as we will show, it does happen in some standard sectors, and in \textit{all} exotic sectors that reheat above the QCD phase transition.
-This work is organized as follows...
+This work is organized as follows: section \ref{sec:nn} introduces the particle content of the model, section \ref{sec:dQCD} discusses the phase transition behaviour of the both the standard and exotic sectors present, section \ref{sec:reheat} lays out hidden sector reheating, section \ref{sec:constraints} applies constraints from cosmological observables allowing for the calculation of gravitational wave signatures in section \ref{sec:gw}, and, finally, section \ref{sec:conclusion} ties everything up.
 
@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition. 
-Exotic sectors feature no baryons \draftnote{why??} and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \draftnote{isn't that what we're talking about?}\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
+Generalized heavy standard sectors feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
 The total gravitational wave signal is a linear combination of the three contributions:

### 2019-09-26 gwnnDraft02.tex
pull

--- 2019-09-25 gwnnDraft02.tex
@@
 The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),
-\begin{equation}
+\begin{equation}\label{eqn:Beta}
 \beta  \equiv \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}.
 \end{equation}
-The ratio of $\beta$ and the Hubble constant, at the time of nucleation, $H$ controls the strength of the GW signal,
+The ratio of $\beta$ and the Hubble constant $H$, at the time of nucleation, controls both the strength and peak frequency of the GW signal.
+Using Eq.~(\ref{eqn:Beta}) it can be expressed explicitly as,
 \begin{equation}\label{eqn:BH}
@@
 Due to the lack of a general analytic QCD potential, it is not possible to use Eq.~(\ref{eqn:BH}) to calculate $\beta/H$.
-There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} which predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments are riddled with assumptions on the potential.
+There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} which predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments are based on assumptions concerning the potential.
 In more recent work, some authors~\citep{Helmboldt:2019pan,Bai:2018dxf} have attempted to estimate it using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models.
@@
 In all cases, the summed GW signal is detectable by one or more proposed interferometers.
-When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
+When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$.
+The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
 As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.

### 2019-09-26 gwnnDraft02.tex
smaller changes

@@
 Therefore, the hidden sectors cannot be in thermal equilibrium at any time, and the physics of reheating must dump energy preferentially in the Standard Model sector.
-This can be accomplished with primodial axion-like particle (ALP) models~\cite{MARSH20161,PhysRevLett.121.201303} and with the reheaton method~\cite{Arkani-Hamed:2016rle}.
+This can be accomplished using inflationary axion-like particle (ALP) models~\cite{MARSH20161,PhysRevLett.121.201303} or the reheaton method~\cite{Arkani-Hamed:2016rle}.
 We will also explore alternative parameterizations of reheating that satisfy this condition.

### 2019-09-27 gwnnDraft02.tex
edits

@@
 PaulSmith3@cmail.carleton.ca \\
-Dylan.linthorne@carleton.ca \\
+DylanLinthorne@cmail.carleton.ca \\
 stolar@physics.carleton.ca
@@
 Therefore, the hidden sectors cannot be in thermal equilibrium at any time, and the physics of reheating must dump energy preferentially in the Standard Model sector.
-This can be accomplished using inflationary axion-like particle (ALP) models~\cite{MARSH20161,PhysRevLett.121.201303} or the reheaton method~\cite{Arkani-Hamed:2016rle}.
+This can be accomplished using inflationary axion-like particles (ALP)~\cite{MARSH20161,PhysRevLett.121.201303} or the reheaton method~\cite{Arkani-Hamed:2016rle}.
 We will also explore alternative parameterizations of reheating that satisfy this condition.
@@
 We view the parameterization of Eq.~(\ref{eqn:massParam}) as a random distribution in theory space up to the cutoff $\Lambda$, therefore this setup solves the hierarchy problem if $r \sim \mathcal{O}(1)$~\cite{Arkani-Hamed:2016rle}\footnote{Constraints require $r$ to be somewhat smaller than 1.} and our sector is the one that that has the smallest absolute value of the Higgs mass parameter.
-We have taken for simplicity that there equal numbers sectors with positive and negative $m_H^2$, but this assumption does not affect our analysis.
+We have taken for simplicity that there are equal numbers of sectors with positive and negative $m_H^2$, but this assumption does not affect our analysis.
 This $N$naturalness framework can be generalized: the various sectors can possess a wide range of particle content that can be freely selected by the model builder.
@@
 The ``exotic sectors'' with $i<0$ provide a radical departure from our own.
-$m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
+$m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$\draftnote{~\cite{}}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
 The mass of fundamental fermions are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet.

### 2019-09-30 gwnnDraft02.tex
Modified conclusion and added scenario details.

--- 2019-09-26 gwnnDraft02.tex
@@
 The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),
-\begin{equation}\label{eqn:Beta}
+\begin{equation}
 \beta  \equiv \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}.
 \end{equation}
-The ratio of $\beta$ and the Hubble constant $H$, at the time of nucleation, controls both the strength and peak frequency of the GW signal.
-Using Eq.~(\ref{eqn:Beta}) it can be expressed explicitly as,
+The ratio of $\beta$ and the Hubble constant, at the time of nucleation, $H$ controls the strength of the GW signal,
 \begin{equation}\label{eqn:BH}
@@
 Due to the lack of a general analytic QCD potential, it is not possible to use Eq.~(\ref{eqn:BH}) to calculate $\beta/H$.
-There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} which predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments are based on assumptions concerning the potential.
+There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} which predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments are riddled with assumptions on the potential.
 In more recent work, some authors~\citep{Helmboldt:2019pan,Bai:2018dxf} have attempted to estimate it using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models.
@@
 Such a suppression leads to standard $N$natrualness evading future detector thresholds by a few orders of magnitude in units of energy density.
+
 This is not the case if we consider the more generalized reheating scenarios of section~\ref{sec:constraints}.
-\draftnote{I think we need more details on the scenarios that go into making those plots.} Assuming all else equal, we use the temperature schemes from Eq.~(\ref{eqn:energyDensityAllowed}) to produce the plots in figure~(\ref{fig:Haa}).
+Once the restriction that small vevs are preferentially reheated has been lifted, we can explore a landscape of standard sectors with much heavier particles (specifically quarks) and, as shown in section~\ref{sec:dQCD}, the SFOPT these entail.
+The key phenomenological constraint on such sectors is $\Delta N_{eff}$, giving us a maximum allowed temperature ratio (when compared to the SM) for each reheated hidden sector: Eq.~(\ref{eqn:energyDensityAllowed}) shows the maximum temperature ratios for specific numbers of additional hidden sectors.
+There are four scenarios that we examine here:
+\begin{itemize}
+\item \textbf{Maximized signal:} A single additional heavy hidden sector which saturates all current experimental bounds.
+In the $N$naturalness framework this is equivalent to reheating a standard sector with $i\sim 10^{16}$ up to the maximum allowed temperature ratio.
+\item \textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have higgs vevs that are split by a factor of $\sqrt{10^3}$, leading to a large difference in the frequency of their gravitational wave signals.
+In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{15}$ up to the maximum allowed temperature ratio.
+\item \textbf{Medium split scenario:} Similar to the previous case: these sectors have higgs vevs that are split by a factor of $\sqrt{10}$, resulting in a much smaller difference in the frequency of their gravitational wave signals.
+In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{13}$ up to the maximum allowed temperature ratio.
+\item \textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are $\sim \sqrt{3}$ larger than the previous sector.
+\end{itemize}
+The GW results of these cases are presented in figure~(\ref{fig:Haa}).
 In all cases, the summed GW signal is detectable by one or more proposed interferometers.
-When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$.
-The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
+When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
 As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
@@
 Here, we examined several scenarios (including $N$naturalness) that involve multiple hidden sectors and calculated the GW profiles present.
-Our GW projections unambiguously demonstrate that scenarios with multiple hidden sector SFOPTs can begin to be probed by next generation experiments.
+Our GW projections demonstrate that although vanilla $N$naturalness is not projected to be detectable in the near future, more generalized scenarios with multiple hidden sector SFOPTs are in an observable region and will begin to be probed by next generation space experiments.
+Both cases feature important parts of their GW signals in the void between frequencies detectable by pulsar timing arrays and space-based interferometers --- providing theoretical impetus for new experiments capable of probing this region of frequency space.
+
 Further, our results provide a framework for understanding and using GW signals in two opposite ways: first as a unique signal for specific theories featuring multiple SFOPTs and also as a way to explain signals that deviate from a standard power law spectrum.
@@
 Shifting to the latter scenario, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.
-Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario --- and gently guide us in the direction of multiple hidden sectors.
+Individual SFOPT are understood to create GW that are assumed to follow an approximate power law.
+The multiple transitions that occur in the models outlined here create signals that do not respect this trend: although the individual GW do obey approximate power laws, their sum does not --- leading to a unique signal indicating so-called dark complexity.
+Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors.
 

### 2019-09-30 gwnnDraft02.tex
A lot of grammar and consistency fixing.

@@
 The ``exotic sectors'' with $i<0$ provide a radical departure from our own.
-$m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
+$m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{Arkani-Hamed:2016rle}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
 The mass of fundamental fermions are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet.
@@
 Dark photons and dark neutrinos abound in these sectors and, assuming a relatively high reheat temperature, the leptons, quarks, and heavy bosons of these sectors can also be relativistic.
-In $N$naturalness this feature is realized quite dramatically: each of the $N$ of sectors possess relativistic degrees of freedom.
+In $N$naturalness this feature is realized quite dramatically: each of the $N$ sectors possess relativistic degrees of freedom.
 The presence of these particles can have two main effects: extra relativistic particles can alter the expansion history of the universe through changes to the energy density or hidden sectors can feature annihilations that reheat the photons or neutrinos of our sector near Big Bang Nucleosynthesis (BBN) and affect the light element abundances.
@@
 \end{equation}
-for any \draft{check} decoupled hidden sector~\cite{Arkani-Hamed:2016rle}.
+for any decoupled hidden sector~\cite{Arkani-Hamed:2016rle}.
 Because the constraints on $N_{eff}$ are stronger at photon decoupling than at BBN, we can focus purely on the constraints provided by the former.
@@
 with $T_{RH_{E1}}/T_{RH}$ being the ratio of the reheat temperatures of the 1st exotic sector and our own sector ($0.06$ in standard $N$naturalness with $r = 1$).
-This sum is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$.
-Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$; well under current CMB bounds.
+This sum is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$ to $\Delta N_{eff}$.
+Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$, well under current CMB bounds.
 It should be noted that modifying the exotic sectors' structure (e.g.
@@
 We now turn to the gravitational wave signatures of our setup.
-At high temperatures, each of the hidden sectors has QCD in the quark/gluon phase, but at temperatures around $\Lambda_{\rm QCD,i}$, the sector undergoes a phase transition into the hadronic phase, where we compute $\Lambda_{\rm QCD,i}$ for the different sectors in Sec.~\ref{sec:dQCD}.
+At high temperatures, each of the hidden sectors has QCD in the quark/gluon phase, but at temperatures around $\Lambda_{\rm QCD,i}$, the $i^{\mathrm{th}}$ sector undergoes a phase transition into the hadronic phase that we computed for the different sectors in Sec.~\ref{sec:dQCD}.
 As discussed in that section, this phase transition will be strongly first order (SFOPT) for certain numbers of light quarks, which will generate gravitational waves.
@@
 \end{equation}
-where the time component has been integrated out due to nucleation occuring, not in vaccum, but in a finite temperature plasma.
-$\phi$ is the symmetry breaking scalar field with a non-zero VEV.
+where the time component has been integrated out due to nucleation occuring not in vaccum but in a finite temperature plasma.
+$\phi$ is the symmetry breaking scalar field with a non-zero vev.
 In the case of the chiral phase transition, the scalar field breaking the SU$(N_f)_{R}$ $ \times$ SU$(N_f)_{L}$ chiral symmetry is the effective quark condensate $\phi_{i} \sim \langle q\bar{q} \rangle_{i}$ of the respective sector.
@@
 The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
-Assuming that the SM sector is radiation dominated, a quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation~\citep{Espinosa:2010hh} ,
+Assuming that the SM sector is radiation dominated, a quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition, $\epsilon$, to the energy density of radiation, at the time of nucleation~\citep{Espinosa:2010hh} ,
 \begin{equation}
@@
 with $\epsilon$ being calculable from the scalar potential.
-Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent head, $\epsilon$ should correspond to the energy density of the hidden sector going through the PT.
+Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent heat, $\epsilon$ should correspond to the energy density of the hidden sector going through the PT.
 The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors.
@@
 With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$~\citep{PhysRevLett.112.041301}.
-\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves.
+\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: Turbulence within the plasma, left over from the sound wave propagation, will produce gravitational waves.
 With efficiency factor $\kappa_{
@@
 \end{equation}
-where $a$ ($a_{0}$)  and $H$ ($H_{0}$) are the scale factor and Hubble constant at the time of nucleation (observation), respectfully.
+where $a$ ($a_{0}$)  and $H$ ($H_{0}$) are the scale factor and Hubble constant at the time of nucleation (observation), respectively.
 Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW signal that would be measured today is given by the coherent sum,
@@
 
-This is not the case if we consider the more generalized reheating scenarios of section~\ref{sec:constraints}.
+This is not the case if we consider the more generalized reheating scenarios of Sec.~\ref{sec:constraints}.
 Once the restriction that small vevs are preferentially reheated has been lifted, we can explore a landscape of standard sectors with much heavier particles (specifically quarks) and, as shown in section~\ref{sec:dQCD}, the SFOPT these entail.
@@
 The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
-Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.
+Eventually, a temperature limit will be reached where two (or multiple) distinct peaks will be visible, provided that the amplitudes are comparable.
 \begin{figure*}[tb]

### 2019-09-30 gwnnDraft02.tex
edits

--- 2019-09-30 gwnnDraft02.tex
@@
 \end{equation}
-In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$. 
+In essence, this is a linear combination of the individual spectral shapes weighted by a power of their efficiency factors $\kappa^q$. 
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
@@
 \end{equation}
-Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
+Where we have assumed an optimistic bubble wall velocity of $v \sim 1$ for runaway bubbles.
 $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
@@
 As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $.
-The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},
+The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837}, given by:
 \begin{equation}\label{eqn::redshifting}
-\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2
+\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2,
 \end{equation}
@@
 This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
-The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
-Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.
+The broadening can be substantial if the hidden sectors transition between a large gap of time.
+Assuming that the amplitudes of individual contributions are comparable, a temperature gap limit exists at which two or more individual peaks could be resolved.
 \begin{figure*}[tb]
@@
 \begin{split}
-\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
+\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)},
 \\
-\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
+\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)},
 \end{split}
 \end{equation}
-Where $T$ is the exposure time of the experiment.
+where $T$ is the exposure time of the experiment.
 The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
@@
 Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}.
-the PSI curves are constructed using information from the power law form of the signal,
+The PSI curves are constructed using information from the power law form of the signal,
 \begin{equation}
-h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}
+h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta},
 \end{equation}

### 2019-10-01 gwnnDraft02.tex

--- 2019-09-30 gwnnDraft02.tex
@@
 This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
-The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
-Eventually, a temperature limit will be reached where two (or multiple) distinct peaks will be visible, provided that the amplitudes are comparable.
+The broadening can be substantial if the hidden sectors transition between a large gap of time.
+Assuming that the amplitudes of individual contributions are comparable, a temperature gap limit exists at which two or more individual peaks could be resolved.
+
 \begin{figure*}[tb]

### 2019-10-01 gwnnDraft02.tex
Added scenario details.

--- 2019-09-30 gwnnDraft02.tex
@@
 %
-\begin{equation}
+\begin{equation}\label{eqn:alpha2}
 \alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4,
@@
 %
-\begin{equation}
+\begin{equation}\label{eqn:peakFrequency}
 f_{p} = 3.8 \times 10^{-8} \, \textrm{Hz}\, \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
@@
 This is not the case if we consider the more generalized reheating scenarios of Sec.~\ref{sec:constraints}.
-Once the restriction that small vevs are preferentially reheated has been lifted, we can explore a landscape of standard sectors with much heavier particles (specifically quarks) and, as shown in section~\ref{sec:dQCD}, the SFOPT these entail.
-The key phenomenological constraint on such sectors is $\Delta N_{eff}$, giving us a maximum allowed temperature ratio (when compared to the SM) for each reheated hidden sector: Eq.~(\ref{eqn:energyDensityAllowed}) shows the maximum temperature ratios for specific numbers of additional hidden sectors.
+Once the restriction that sectors with small higgs' masses are preferentially reheated has been lifted, we can explore a much more vast landscape of hidden sectors than are allowed in the vanilla case.
+Here, we construct several different scenarios that are both detectable and demonstrate a variety of gravitational wave profiles.
+Specifically, we explore scenarios that lead to a deviation in the peak behaviour of the total GW signal (the convolution of stochastic GW from individual SFOPT) from a standard power law signal.
+
+It should be noted that the key phenomenological constraint on all of these models is $\Delta N_{eff}$, giving us a maximum allowed temperature ratio (when compared to the SM) for each reheated hidden sector: Eq.~(\ref{eqn:energyDensityAllowed}) shows the maximum temperature ratios for specific numbers of additional hidden sectors.
+Due to the rather harsh scaling of the GW strength, $\alpha$, with temperature ratio (Eq.~(\ref{eqn:alpha2})), we take the optimistic approach of keeping the temperature ratio as high as possible for all of the hidden sectors.
+
+In all our examined cases, we focus on heavy standard sectors --- pure Yang-Mills sectors with much heavier particles (specifically quarks) and, as shown in Sec.~\ref{sec:dQCD}, the SFOPT these entail.
+The reason for this arises from Eq.~(\ref{eqn:peakFrequency}): every exotic sector features a phase transition that occurs at $\Lambda_{ex} \sim 90$ MeV.
+If we maximize the allowed temperature ratio, this gives us a (SM) photon temperature, $T_{\gamma}$, that places our signal directly into the void between the detection region of pulsar timing arrays and space-based interferometers (see Sec.~\ref{sec:detection}).
+The location of the peak can be changed by dropping the temperature ratio, but the adjustment required to end up with a signal with an appropriate peak frequency makes the overall signal too weak to detect.
+In accordance with Sec.~\ref{sec:dQCD}, standard sectors can have much higher temperature phase transitions.
+As such, maintaining the maximum allowed temperature ratio between the hidden sector(s) and the SM gives a much larger photon temperature and a proportionally larger peak frequency; ultimately allowing for detection by space-based interferometers.
+
 There are four scenarios that we examine here:
@@
 \item \textbf{Maximized signal:} A single additional heavy hidden sector which saturates all current experimental bounds.
+The SM photon bath temperature at the time of the hidden sector PT is $87$ GeV.
 In the $N$naturalness framework this is equivalent to reheating a standard sector with $i\sim 10^{16}$ up to the maximum allowed temperature ratio.
-\item \textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have higgs vevs that are split by a factor of $\sqrt{10^3}$, leading to a large difference in the frequency of their gravitational wave signals.
+\item \textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have higgs vevs that are split by a factor of $\sqrt{10^3} = (v_{h1})/(v_{h2})$.
+This results in a difference in the scale of the SFOPTs leading to the SM photon bath temperature changing a large amount during the time between the PTs.
+This, in turn, leads to a large separation in the peak frequency of their gravitational wave signals.
 In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{15}$ up to the maximum allowed temperature ratio.
-\item \textbf{Medium split scenario:} Similar to the previous case: these sectors have higgs vevs that are split by a factor of $\sqrt{10}$, resulting in a much smaller difference in the frequency of their gravitational wave signals.
+\item \textbf{Medium split scenario:} Similar to the previous case: these sectors have higgs vevs that are split by a factor of $\sqrt{10}= (v_{h1})/(v_{h2})$, resulting in a much smaller difference in the peak frequency of their gravitational wave signals.
 In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{13}$ up to the maximum allowed temperature ratio.
-\item \textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are $\sim \sqrt{3}$ larger than the previous sector.
+\item \textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are $\sqrt{3} \sim (v_{hi})/(v_{h(i+1)})$ larger than the previous sector.
 \end{itemize}

### 2019-10-01 gwnnDraft02.tex
SKA

--- 2019-10-01 gwnnDraft02.tex
@@
 We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
+In the case of the PTA experiments, the sensitivity curves are dependent on how frequently the pulsar's timing residuals, $\delta t$, are measured.
+When using Eq.~(\ref{eqn::SNR}) to construct the PSI curves for SKA, the upper integration bound is inversely proportional to pulsar's timing residual, $f_{min} = 1/\delta t$.
+In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations.
+If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right.
 \section{Conclusion}

### 2019-10-01 gwnnDraft02.tex
SKA update

@@
 This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Jaeckel:2016jlh,Addazi:2016fbj,Hardy:2016mns,Dienes:2016vei,Tsumura:2017knk,Acharya:2017szw,Bernal:2017kxu,Aoki:2017aws,Heikinheimo:2018esa,Geller:2018mwu,Croon:2018erz,Baldes:2018emh,Bai:2018dxf,Breitbach:2018ddu,Fairbairn:2019xog,Helmboldt:2019pan,Caputo:2019wsd,Bertone:2019irm}.
+
 In this work, we explore the possibility of having multiple decoupled hidden sectors.
@@
 This does not occur at either the electroweak or QCD phase transition in the SM, but as we will show, it does happen in some standard sectors, and in \textit{all} exotic sectors that reheat above the QCD phase transition.
+
 This work is organized as follows: section \ref{sec:nn} introduces the particle content of the model, section \ref{sec:dQCD} discusses the phase transition behaviour of the both the standard and exotic sectors present, section \ref{sec:reheat} lays out hidden sector reheating, section \ref{sec:constraints} applies constraints from cosmological observables allowing for the calculation of gravitational wave signatures in section \ref{sec:gw}, and, finally, section \ref{sec:conclusion} ties everything up.
@@
 In~\cite{Bai:2018dxf} chiral effective Lagrangian was used to calculate a low energy thermalized potential for confining SU$(N)$.
+
 The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
@@
 where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition.
+
 Another important parameter to characterize the phase transition is its inverse timescale, $\beta$~\citep{Caprini:2015zlo}.

### 2019-10-01 gwnnDraft02.tex
SKA update
Added in more details

--- 2019-10-01 gwnnDraft02.tex
@@
 \end{equation}
-In essence, this is a linear combination of the individual spectral shapes weighted by a power of their efficiency factors $\kappa^q$. 
+In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$. 
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
@@
 \end{equation}
-Where we have assumed an optimistic bubble wall velocity of $v \sim 1$ for runaway bubbles.
+Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
 $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
@@
 As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $.
-The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837}, given by:
+The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},
 \begin{equation}\label{eqn::redshifting}
-\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2,
+\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2
 \end{equation}
@@
 This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
-The broadening can be substantial if the hidden sectors transition between a large gap of time.
-Assuming that the amplitudes of individual contributions are comparable, a temperature gap limit exists at which two or more individual peaks could be resolved.
-
+The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
+Eventually, a temperature limit will be reached where two (or multiple) distinct peaks will be visible, provided that the amplitudes are comparable.
 \begin{figure*}[tb]
@@
 \begin{split}
-\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)},
+\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
 \\
-\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)},
+\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
 \end{split}
 \end{equation}
-where $T$ is the exposure time of the experiment.
+Where $T$ is the exposure time of the experiment.
 The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
@@
 Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}.
-The PSI curves are constructed using information from the power law form of the signal,
+the PSI curves are constructed using information from the power law form of the signal,
 \begin{equation}
-h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta},
+h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}
 \end{equation}
@@
 We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
-In the case of the PTA experiments, the sensitivity curves are dependent on how frequently the pulsar's timing residuals, $\delta t$, are measured.
-When using Eq.~(\ref{eqn::SNR}) to construct the PSI curves for SKA, the upper integration bound is inversely proportional to pulsar's timing residual, $f_{min} = 1/\delta t$.
-In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations.
-If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right.
 \section{Conclusion}
@@
 
-Further, our results provide a framework for understanding and using GW signals in two opposite ways: first as a unique signal for specific theories featuring multiple SFOPTs and also as a way to explain signals that deviate from a standard power law spectrum.
+Further, our results provide a framework for understanding and using GW signals in two different ways: first as a unique signal for specific theories featuring multiple SFOPTs and also as a challenge to broaden the understanding of GW detector sensitivity.
 
 In the former case, this demonstrates the power of GW signals to probe deep into the unknown arena of complex hidden sectors.
-Whether a model predicts of the presence of 1, 5, or more hidden sectors, any SFOPT can potentially contribute a GW signal and the sum of these signals can create a unique GW background; ultimately providing another means to test and constrain theories.
+Individual SFOPT are understood to create GW that are assumed to follow an approximate power law.
+If a model predicts of the presence of 2, 5, or more additional sectors, or features a single extra sector with multiple PTs, deviations from a standard power law can occur.
+The multiple transitions that occur in the models outlined here create signals that follow this trend: although the individual GW do obey approximate power laws, their sum does not --- leading to a unique signal indicating so-called dark complexity.
+Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors.
+ultimately providing another means to test and constrain theories.
 
-Shifting to the latter scenario, should a stochastic GW background be detected, deviations from a standard power law curve would indicate a more complicated hidden sector.
-Individual SFOPT are understood to create GW that are assumed to follow an approximate power law.
-The multiple transitions that occur in the models outlined here create signals that do not respect this trend: although the individual GW do obey approximate power laws, their sum does not --- leading to a unique signal indicating so-called dark complexity.
-Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors.
+Shifting to the other part of our framework, our results leads to the question "are current experiments able to probe non power law signals?" For frequency ranges away from the peak of the total GW signals the quoted detection thresholds should hold: the signals fall off in a fashion identical to a power law.
+However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law.
+This points to the need for future work to better understand detection prospects for the next generation of GW detectors.
 

### 2019-10-01 gwnnDraft02.tex

--- 2019-10-01 gwnnDraft02.tex
@@
 Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}.
-The PSI curves are constructed using information from the power law form of the signal,
+The PLI curves are constructed using information from the power law form of the signal,
 \begin{equation}

### 2019-10-01 gwnnDraft02.tex
minor changes

--- 2019-10-01 gwnnDraft02.tex
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa (blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
 \label{fig:Haa}
@@
 Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}.
-the PSI curves are constructed using information from the power law form of the signal,
+the PLI curves are constructed using information from the power law form of the signal,
 \begin{equation}
@@
 , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$.
-Each curve will lay tangent to the PSI curve, more formally,
+Each curve will lay tangent to the PLI curve, more formally,
 \begin{equation}
@@
 \end{equation}
-The spectral noise curves used to create the PSI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
+The spectral noise curves used to create the PLI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
 We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.

### 2019-10-01 gwnnDraft02.tex
pull stuff

--- 2019-10-01 gwnnDraft02.tex
@@
 
-Shifting to the other part of our framework, our results leads to the question "are current experiments able to probe non power law signals?" For frequency ranges away from the peak of the total GW signals the quoted detection thresholds should hold: the signals fall off in a fashion identical to a power law.
+Shifting to the other part of our framework, our results leads to the question ``are current experiments able to probe non power law signals?" For frequency ranges away from the peak of the total GW signals the quoted detection thresholds should hold: the signals fall off in a fashion identical to a power law.
 However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law.

### 2019-10-01 gwnnDraft02.tex
minor changes.
fig caption fixes.

--- 2019-10-01 gwnnDraft02.tex
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa (blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}
 \label{fig::Nnatural}
@@
 \begin{minipage}[c]{\textwidth}
+\includegraphics[width=.45\textwidth ]{highest.png}
+\hfill
 \includegraphics[width=.45\textwidth]{TwoFar.png} 
@@
 \includegraphics[width=.45\textwidth]{TwoMed.png} 
-\hfill
-\includegraphics[width=.45\textwidth ]{highest.png}
 \hfill
@@
 The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures.
-The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ).
+The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$).
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.

### 2019-10-01 gwnnDraft02.tex
more small things.

@@
 \end{figure}
-Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in figure~(\ref{fig::Nnatural}).
+Applying this to the standard reheating scenario of $N$natrualness, introduced in~\ref{sec:reheat}, we get GW signals as seen in Fig.~\ref{fig::Nnatural}.
 Plotted are the individual contributions to the signal from each phase transitioned sector, as well as the coherent sum of all sectors.
@@
 \end{itemize}
-The GW results of these cases are presented in figure~(\ref{fig:Haa}).
+The GW results of these cases are presented in Fig.~\ref{fig:Haa}.
 In all cases, the summed GW signal is detectable by one or more proposed interferometers.
-When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
+When relaxing the assumptions on $\beta/H$, the scenarios in Fig.~\ref{fig:Haa} are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
 As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
-This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
+This is seen in Fig.~\ref{fig:Haa}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
 The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).
@@
 \end{equation}
-The spectral noise curves used to create the PLI curves shown in figures~(\ref{fig::Nnatural}) and ~(\ref{fig:Haa}) where taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
+The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
 We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.

### 2019-10-01 gwnnDraft02.tex

--- 2019-10-01 gwnnDraft02.tex
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa (blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}
 \label{fig::Nnatural}
@@
 \begin{minipage}[c]{\textwidth}
-\includegraphics[width=.45\textwidth ]{highest.png}
-\hfill
 \includegraphics[width=.45\textwidth]{TwoFar.png} 
@@
 \includegraphics[width=.45\textwidth]{TwoMed.png} 
+\hfill
+\includegraphics[width=.45\textwidth ]{highest.png}
 \hfill
@@
 The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures.
-The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$).
+The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ).
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
@@
 %Questions, of course, still abound: how can the %estimations of $\alpha$ and $\beta/H$ be improved?
+
+\section*{Acknowledgement}
+We thank Djuna Croon, Yang Bai and Yuhsin Tsai  for helpful discussions.
+P.A.S.
+and D.L.
+Both thank the 2018 Theoretical Advanced Study Institute in Elementary Particle Physics Program (TASI) for setting up a platform for discussion which seeded the genesis of this project.
+This work was supported by the Natural Sciences and Engineering Research Council of
+Canada (NSERC). D.L. acknowledges support from the NSERC Postgraduate Scholarships-Doctoral Program (PGS D).
 

### 2019-10-01 gwnnDraft02.tex

--- 2019-10-01 gwnnDraft02.tex
@@
 
+\section*{Acknowledgement}
+We thank Djuna Croon, Yang Bai and Yuhsin Tsai  for helpful discussions.
+P.A.S.
+and D.L.
+Both thank the 2018 Theoretical Advanced Study Institute in Elementary Particle Physics Program (TASI) for setting up a platform for discussion which seeded the genesis of this project.
+This work was supported by the Natural Sciences and Engineering Research Council of
+Canada (NSERC). D.L. acknowledges support from the NSERC Postgraduate Scholarships-Doctoral Program (PGS D).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-10-02 gwnnDraft02.tex
drafting in sects 1-5

@@
 This simple ansatz can lead to very rich phenomenology and interesting gravitational wave spectra, but we stress that it is only a starting point for exploring the space of theories with multiple hidden sectors.
+
 In this setup, there are two qualitatively different kinds of sectors:
@@
 As in~\cite{Arkani-Hamed:2016rle}, we assume that the standard sector with the smallest absolute value of $m_H^2$ is the Standard Model.
-\item \textbf{Exotic Sectors}: Those with  $m_H^2 > 0$.
-In this case, electroweak symmetry breaking is preserved below the mass of the Higgs, and broken by the confinement of QCD~\cite{Arkani-Hamed:2016rle,Pisarski:1983ms}.
+\item \textbf{Exotic Sectors}: Those with  $m_H^2 > 0$. In this case, electroweak symmetry is preserved below the mass of the Higgs, and broken by the confinement of QCD~\cite{Susskind:1978ms}.
 \end{itemize}
@@
 We will also explore alternative parameterizations of reheating that satisfy this condition.
+
 In all the above models, there is some energy in the hidden sectors, and these sectors undergo thermal evolution independent of the SM sector.
@@
 The condition for these transitions to leave imprints on the stochastic gravitational wave spectrum is that they strongly first order phase transitions (SFOPT)~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080}.
-This does not occur at either the electroweak or QCD phase transition in the SM, but as we will show, it does happen in some standard sectors, and in \textit{all} exotic sectors that reheat above the QCD phase transition.
+This does not occur at either the electroweak or QCD phase transition in the SM, but as we will show, it does happen for the QCD phase transition in some standard sectors and in \textit{all} exotic sectors that reheat above the QCD phase transition.
 
@@
 \end{equation}
-where $\Lambda$ is some high scale cutoff, $N$ is the number of sectors, and $r$ mass parameter in the SM in units of $\Lambda_H^2/N$.
+where $\Lambda$ is some high scale cutoff, $N$ is the number of sectors, and $r$ is the mass parameter in the SM in units of $\Lambda_H^2/N$.
 We view the parameterization of Eq.~(\ref{eqn:massParam}) as a random distribution in theory space up to the cutoff $\Lambda$, therefore this setup solves the hierarchy problem if $r \sim \mathcal{O}(1)$~\cite{Arkani-Hamed:2016rle}\footnote{Constraints require $r$ to be somewhat smaller than 1.} and our sector is the one that that has the smallest absolute value of the Higgs mass parameter.
@@
 The one exception to this is that ``our" sector must consist of the Standard Model.
+
 From the above Lagrangians, the Higgs in sectors with $i \geq 0$ will get a vev given by:
@@
 %As mentioned above, half of all sectors in this model feature a Higgs mass parameter such that $m_H^2 < 0$. 
-The ``standard sectors'' with $i>0$ feature electroweak symmetry breaking just like in the SM, however the vevs produced scale with the changing mass parameter: $v_i \sim v_{\rm SM}\sqrt{i}$.
-As the masses scale with the vev, this leads to the masses of the $W$, $Z$ and fermions within each sector increasing with $i$.
-The consequences of this on the confinement scale of QCD in the $i \geq 1$ sectors is further discussed in Sec.
+The ``standard sectors'' with $i>0$ feature electroweak symmetry breaking just like in the SM, however the vevs scale with the changing mass parameter: $v_i \sim v_{\rm SM}\sqrt{i}$.
+This means that the masses of the fermions and the $W$ and $Z$ will also increase proportional to $\sqrt{i}$.
+The consequences of this scaling on the confinement scale of QCD in the $i \geq 1$ sectors is further discussed in Sec.
 \ref{sec:dQCD}.
+
 The ``exotic sectors'' with $i<0$ provide a radical departure from our own.
-$m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{Arkani-Hamed:2016rle}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
+$m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{Susskind:1978ms}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
 The mass of fundamental fermions are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet.
@@
 Crucially, this results in the production of gravitational waves.
-This is the physical signature we're interested in exploring within this paper; the calculation and results are presented in Sec.
+This is the physical signature we explore in this paper; the calculation and results are presented in Sec.
 \ref{sec:gw}.
@@
 In the SM, it is known that the phase transition is a crossover and does lead to gravitational wave signals~\cite{Aoki:2006we,Bhattacharya:2014ara}.
-In the general case with 3 or more colours, the phase transition can be strongly first order in two regimes~\cite{Panero:2009tv,SVETITSKY1982423,Pisarski:1983ms}:
+In the general case with 3 or more colours, the phase transition can be strongly first order in two regimes~\cite{SVETITSKY1982423,Pisarski:1983ms,Panero:2009tv}:
 \begin{itemize}
@@
 Conversely, exotic sectors with zero vev feature six very light quarks, so \textit{all} the exotic sectors undergo SFOPT at the temperature of QCD confinement.
+
 We now calculate the QCD confinement scale for each sector following the same procedure as \cite{Cui:2011wk}.
@@
 In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 5$ in $\overline{MS}$~\cite{PhysRevD.98.030001}.
-Because we've set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at high scales for all sectors.
+Because we have set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at high scales for all sectors.
 However, since the masses of the quarks in each sector are different, we end up with a unique running of the coupling for each sector.
@@
 In cosmological terms, we can envision a sector's thermal history unfolding, whereas the plasma cools below each quark mass threshold and said quarks are frozen out.
-At a certain point, the sector arrives at the QCD phase transition and confinement occurs (provided there are light enough quarks to confine) --- if this occurs when $\geq 3$ quarks are at a much lower scale or all quarks have already frozen out, we get the desired phase transition.
+At a certain point, the sector arrives at the QCD phase transition and confinement occurs --- if this occurs when $\geq 3$ quarks are at a much lower scale or all quarks have already frozen out, we get the desired phase transition.
+
 \subsection{Standard Sectors}
@@
 \end{equation}
+where $m_q$ without a superscript is the mass of $q$ in the SM.
 We take the sector with SFOPT to be the ones when the mass of the up quark, down quark, and QCD phase transition scale are all comparable:
@@
 From Eq.~(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector.
-If we take Higgs vevs as high as the GUT scale $\sim 10^{16}$ GeV, then we can get confinement scales as high as $\sim 38 \,\gev$.
+If we take Higgs vevs as high as the GUT scale $\sim 10^{16}$ GeV, then we can get confinement scales as high as $\sim 38 \,\gev$ \draftnote{is there a way to get this value parametrically?}.
 The signals of this sector and other test cases like it are explored in Sec.
 \ref{sec:gw}.
+
 \subsection{Exotic Sectors}
@@
 Here, $a$ and $b$ denote the component quark flavours.
+
 \section{Reheating N Sectors}
@@
 A key issue within $N$naturalness is how to predominantly gift energy density to our own sector so as to not be immediately excluded by cosmological constraints, particularly those from number of effective neutrinos ($N_{eff}$).
-In~\cite{Arkani-Hamed:2016rle} this is done through the introduction of a post-inflationary field called the ``reheaton".
+Here we review the results of~\cite{Arkani-Hamed:2016rle}.
+Reheating occurs through the introduction a ``reheaton'' field.
 After inflation, the reheaton field possess the majority of the energy density of the Universe.
@@
 Our focus is primarily the production of gravitational waves from multiple sectors and a fermion reheaton does not change the scaling of the energy density of the exotic sectors and thus does not affect expected gravitational wave profiles.
+
 In order to maintain the naturalness of our SM sector, the reheaton coupling is taken to be universal to every sector's Higgs.
@@
 with $r_s$ being the ratio of the energy density of the first additional standard sector over the energy density of our sector.
-For the exotic sectors, Eq.~(\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$ and is also loop supressed. 
+For the exotic sectors, Eq.~(\ref{eqn:nnEffLag}) indicates a matrix element scaling $\cM_{m_H^2>0} \sim 1/m_{H_i}^2$ and is also loop suppressed. 
 %As the Feynman diagram (Fig.~\ref{fig:reheatonDecays}) shows, the reheaton decays to exotic sectors are loop suppressed, 
@@
 \end{equation}
+
 As a final note, in this setup the reheating temperature of the SM, $T_{RH}$, has an upper bound on the order of the weak scale.
-If this bound is not observed, the SM Higgs mass would have major thermal corrections --- leading to the branching ratios into other sectors being problematically large~\citep{Arkani-Hamed:2016rle}.
+If this bound is not observed, the SM Higgs mass would have large thermal corrections --- leading to the branching ratios into other sectors being problematically large~\citep{Arkani-Hamed:2016rle}.
 Thus we only consider relatively low reheating temperatures $\lesssim 100$ GeV.
-Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we also consider a more general parameterization where sectors are reheated ``randomly" as opposed to in relation to the Higgs mass parameter.
-This allows us to explore more a broader model space with multiple dark sectors at a huge range of scales.
-For these models, the reheating mechanism remains undefined and the results of this section are completely irrelevant.
-\section{Constraints}
+Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we also consider a more generic parameterization where the reheating temperature of each sector is a free parameter and is in general uncorrelated with the Higgs mass parameter.
+This allows us to explore a broader model space with multiple dark sectors at a huge range of scales.
+For these models, the reheating mechanism remains unspecified\section{Constraints}
 \label{sec:constraints}
@@
 For a dark sector with one relativistic degree of freedom, its temperature must be $\sim 0.6\, T_{\rm SM}$ to not be excluded.
-This sector would have an energy density $\rho \sim 0.036\, \rho_{\rm SM}$.
+This sector would have an energy density $\rho \sim 0.036\, \rho_{\rm SM}$ \draftnote{Explain why this isn't $.6^4$}.
 %\draftnote{Maybe give what the temperature ratio should be for one standard (or exotic) sector to not be excluded.} 
@@
 \textcolor{green}{$\xi=0.5$ and $g=2$ is not excluded.}
+
 \subsection{Exotic Sector Contributions}

### 2019-10-02 gwnnDraft02.tex
acknowledgements

@@
 \section*{Acknowledgement}
-We thank Djuna Croon, Yang Bai and Yuhsin Tsai  for helpful discussions.
+We thank Yang Bai, Djuna Croon, Kevin Earl, and Yuhsin Tsai for helpful discussions.
 P.A.S.
 and D.L.
-Both thank the 2018 Theoretical Advanced Study Institute in Elementary Particle Physics Program (TASI) for setting up a platform for discussion which seeded the genesis of this project.
-This work was supported by the Natural Sciences and Engineering Research Council of
+both thank the 2018 Theoretical Advanced Study Institute in Elementary Particle Physics Program (TASI) for setting up a platform for discussion which seeded the genesis of this project.
+This work was supported in part by the Natural Sciences and Engineering Research Council of
 Canada (NSERC). D.L. acknowledges support from the NSERC Postgraduate Scholarships-Doctoral Program (PGS D).

### 2019-10-02 gwnnDraft02.tex
Added standard sector neffective

--- 2019-10-02 gwnnDraft02.tex
@@
 From Eq.~(\ref{eqn:lambda2}) we can determine the confinement scale of an arbitrary mirror sector.
-If we take Higgs vevs as high as the GUT scale $\sim 10^{16}$ GeV, then we can get confinement scales as high as $\sim 38 \,\gev$ \draftnote{is there a way to get this value parametrically?}.
+If we take Higgs vevs as high as the GUT scale $\sim 10^{16}$ GeV, then we can use Eq.~(\ref{eqn:lambda2adj}) to get confinement scales as high as $\sim 38 \,\gev$.
 The signals of this sector and other test cases like it are explored in Sec.
@@
 This allows us to explore a broader model space with multiple dark sectors at a huge range of scales.
-For these models, the reheating mechanism remains unspecified\section{Constraints}
+For these models, the reheating mechanism remains unspecifie.d\section{Constraints}
 \label{sec:constraints}
@@
 \end{equation} 
-For a dark sector with one relativistic degree of freedom, its temperature must be $\sim 0.6\, T_{\rm SM}$ to not be excluded.
-This sector would have an energy density $\rho \sim 0.036\, \rho_{\rm SM}$ \draftnote{Explain why this isn't $.6^4$}.
+For a dark sector with one relativistic degree of freedom, its temperature must be $T_{DS}\sim 0.6\, T_{\rm SM}$ to not be excluded. Applying the energy density formula \cite{Trodden:2004st},
+\begin{equation}
+\rho_i = \frac{\pi^2}{30}g_i T_i^4,
+\end{equation}
+to both said dark sector and the SM then taking the ratio indicates that the dark sector would have an energy density $\rho \sim 0.038\, \rho_{\rm SM}$. 
 %\draftnote{Maybe give what the temperature ratio should be for one standard (or exotic) sector to not be excluded.} 
@@
 This increase is typically not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.
+
+\subsection{Standard Sector Contributions}
+
+Within the context of vanilla $N$naturalness, the majority of contributions arise from standard sectors.
+This is explored in a sufficient amount of depth in \cite{Arkani-Hamed:2016rle}; here we briefly summarize these arguments.
+All additional standard sectors are very similar to our own: they have the same particle content and couplings and differ only by the higgs mass.
+As our sector is taken to be the lightest so as to be preferentially reheated, every other standard sector features an earlier freeze-out of their respective particles.
+This ultimately leads to each sector having at most the same number of relativistic degrees of freedom as the SM.
+
+ \cite{Arkani-Hamed:2016rle} expresses the standard sector contributions as:
+\begin{equation}
+\Delta N_{eff} = \frac{1}{\rho^{us}_\nu} \sum_{i\neq us}. \rho_i.
+\end{equation}
+In the case that the reheaton is lighter than the lightest higgs (ours), this can be expressed as
+\begin{equation}
+\begin{split}
+\Delta N_{eff} &\sim \sum^{N_b}_{i=1}\frac{1}{2i+1}+\frac{y_c^2}{y_b^2}\sum^{N_c}_{i=N_b + 1}\frac{1}{2i+1}\\
+& \simeq \frac{1}{2}\left(\log 2N_b + \frac{y_c^2}{y_b^2}\log \frac{N_c}{N_b}\right)
+\end{split}
+\end{equation}
+with $y_{c,b}$ representing the charm and bottom yukawa couplings and 
+\begin{equation}
+N_{b,c} = \left(\frac{m_\phi^2}{8m^2_{b,c}}-\frac{1}{2}\right)
+\end{equation}
+with $m_\phi$ being the mass of the reheaton.
+
+Application of these results indicates that for a majority of the parameter space, vanilla $N$naturalness requires fine-tuning ($r$ in Eq.~(\ref{eqn:vevs}) set to a value $< 1$).
+Numerical results for the fine-tuning required for various reheaton masses were presented in \cite{Arkani-Hamed:2016rle}.
+
 \subsection{Generalized Reheating Scenarios}
+
 The generalization of possible reheating mechanisms mentioned in section~\ref{sec:reheat} --- where the reheating mechanism no longer depends on the higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study.

### 2019-10-02 gwnnDraft02.tex
fixing the messed up merge
secs 5-6

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction} 
@@
 \ref{sec:gw}.
+
 \section{QCD Phase Transition}
@@
 We now calculate the QCD confinement scale for each sector following the same procedure as \cite{Cui:2011wk}.
-First, due to the parameters of each sector being taken to be identical save for the higgs mass squared (thus $v \neq v_i$, where $v$ is the SM vev), we assume that the strong coupling of every sector is identical at some high scale.
+First, due to the parameters of each sector being taken to be identical save for the Higgs mass squared (thus $v \neq v_i$, where $v$ is the SM vev), we assume that the strong coupling of every sector is identical at some high scale.
 Using the one-loop running, the $\beta$ function can be solved:
@@
 Immediately from Eq.
-(\ref{eqn:nnEffLag}), we can see that the matrix element for decays into standard sectors is inversely proportional to that sectors higgs mass, $\cM_{m_H^2 < 0} \sim 1/m_{h_i}$ (since $v\sim m_H$).
+(\ref{eqn:nnEffLag}), we can see that the matrix element for decays into standard sectors is inversely proportional to that sectors Higgs mass, $\cM_{m_H^2 < 0} \sim 1/m_{h_i}$ (since $v\sim m_H$).
 %The Feynman diagram for this process is presented in Fig. \ref{fig:reheatonDecays}. 
@@
 This allows us to explore a broader model space with multiple dark sectors at a huge range of scales.
-For these models, the reheating mechanism remains unspecifie.d\section{Constraints}
+For these models, the reheating mechanism remains unspecified.
+
+\section{Constraints}
 \label{sec:constraints}
@@
 It should be noted that modifying the exotic sectors' structure (e.g.
-adjusting the exotic sectors to have a lower higgs mass squared or clustering multiple hidden sectors close to the first exotic one) leads to a $\Delta N_{eff}$ contribution that is larger than the base $N$naturalness case.
+adjusting the exotic sectors to have a lower Higgs mass squared or clustering multiple hidden sectors close to the first exotic one) leads to a $\Delta N_{eff}$ contribution that is larger than the base $N$naturalness case.
 This increase is typically not excluded by current bounds, indicating a large degree of liberty in the structure and number of exotic hidden sectors.
@@
 Within the context of vanilla $N$naturalness, the majority of contributions arise from standard sectors.
-This is explored in a sufficient amount of depth in \cite{Arkani-Hamed:2016rle}; here we briefly summarize these arguments.
-All additional standard sectors are very similar to our own: they have the same particle content and couplings and differ only by the higgs mass.
+This is explored in detail in \cite{Arkani-Hamed:2016rle}; here we briefly summarize these arguments.
+All additional standard sectors are very similar to our own: they have the same particle content and couplings and differ only by the Higgs mass.
 As our sector is taken to be the lightest so as to be preferentially reheated, every other standard sector features an earlier freeze-out of their respective particles.
@@
 
- \cite{Arkani-Hamed:2016rle} expresses the standard sector contributions as:
+In \cite{Arkani-Hamed:2016rle}, the standard sector contributions are expressed as:
 \begin{equation}
-\Delta N_{eff} = \frac{1}{\rho^{us}_\nu} \sum_{i\neq us}. \rho_i.
+\Delta N_{eff} = \frac{1}{\rho^{us}_\nu} \sum_{i\neq us} \rho_i.
 \end{equation}
-In the case that the reheaton is lighter than the lightest higgs (ours), this can be expressed as
+In the case that the reheaton is lighter than the lightest Higgs (ours), this can be expressed as
 \begin{equation}
@@
 
-Application of these results indicates that for a majority of the parameter space, vanilla $N$naturalness requires fine-tuning ($r$ in Eq.~(\ref{eqn:vevs}) set to a value $< 1$).
+Application of these results indicates that for a majority of the parameter space, vanilla $N$naturalness requires mild fine-tuning ($r$ in Eq.~(\ref{eqn:vevs}) set to a value $\lesssim 1$).
 Numerical results for the fine-tuning required for various reheaton masses were presented in \cite{Arkani-Hamed:2016rle}.
@@
 
-The generalization of possible reheating mechanisms mentioned in section~\ref{sec:reheat} --- where the reheating mechanism no longer depends on the higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study.
+The generalization of possible reheating mechanisms mentioned in section~\ref{sec:reheat} --- where the reheating mechanism no longer depends on the Higgs' mass parameter of a given sector --- opens up a wide range of hidden sectors for study.
 Specifically, this allows mirror sectors with large Higgs vevs to be reheated to significant energy densities and thus produce gravitational waves with enough power to be detected.
@@
 Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own.
-In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the cirtical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale.
+In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the cirtical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale as long as their temperatures are below the bounds presented here.
  %of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}.
@@
 Yes.}
+
 \section{Gravitational Wave Signals}
@@
 Due to the lack of a general analytic QCD potential, it is not possible to use Eq.~(\ref{eqn:BH}) to calculate $\beta/H$.
-There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} which predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments are riddled with assumptions on the potential.
+There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} which predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments make specific assumptions about the potential.
 In more recent work, some authors~\citep{Helmboldt:2019pan,Bai:2018dxf} have attempted to estimate it using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models.
 These studies claim a large range of values and thus a consensus has not yet been reached.
-Under these circumstances, we take the optimistic case in which $\beta/H$ is of order $\mathcal{O}(10)$.
+Under these circumstances, we take the optimistic case in which $\beta/H$ is $\mathcal{O}(10)$.
+
 \subsection{Production of Gravitational Waves}
 \label{sec:signals}
+
 Gravitational waves are produced with contributions from different components of the SFOPT's evolution.
@@
 \end{equation}
-where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density. The three leading order contributions to the GW power spectrum are as follows:
+where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density. The total gravitational wave signal is a linear combination of three leading contributions:
+\begin{equation}
+h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} .
+\end{equation}
+In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$. 
+The three leading order contributions to the GW power spectrum are as follows:
 \begin{itemize}
@@
 \end{itemize}
-Where $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
+The parameter $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$.
 Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh},
@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
-Generalized heavy standard sectors feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
-The total gravitational wave signal is a linear combination of the three contributions:
-\begin{equation}
-h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} .
-\end{equation}
-In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$. 
+
+\draftnote{Somewhere the argument as to how exotic sectors produce runaway bubbles got lost. Should probably put that here. Also, do we want to define runaway, or is it obvious?}
+Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
@@
 In this case, the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
-Quantities that are calculated at the time of nucleation are denoted with an asterisk (i.e $h^2\Omega_{\textrm{GW}}^*$), which are evolved to relate to their values at the time of observation.
+
 The form of the GW energy density at the time of nucleation is given by~\citep{Breitbach:2018ddu},
@@
 \end{equation}
-Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
+where quantities such as $\Omega_{\textrm{GW}}^*$ that are calculated at the time of nucleation are denoted with an asterisk.
+These must then be evolved to relate to their values at the time of observation.
+Where we have assumed \draftnote{isn't this the definition of runaway?} an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
 $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
@@
 where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.
+
 Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT.
-In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$.
+In the models presented in this paper, we consider a subset of $N$ hidden sectors that undergo a phase transition at a SM temperature of $T_{\gamma}^{i}$.
 As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $.
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa (blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa (blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).
+Details of these curves are given in Sec.~\ref{sec:detection}.}
 \label{fig::Nnatural}
@@
 
-This is not the case if we consider the more generalized reheating scenarios of Sec.~\ref{sec:constraints}.
-Once the restriction that sectors with small higgs' masses are preferentially reheated has been lifted, we can explore a much more vast landscape of hidden sectors than are allowed in the vanilla case.
+This is not the case if we consider more generalized reheating scenarios.
+Once the restriction that sectors with small Higgs masses are preferentially reheated has been lifted, we can explore a much more vast landscape of hidden sectors than are allowed in the vanilla case.
 Here, we construct several different scenarios that are both detectable and demonstrate a variety of gravitational wave profiles.
@@
 It should be noted that the key phenomenological constraint on all of these models is $\Delta N_{eff}$, giving us a maximum allowed temperature ratio (when compared to the SM) for each reheated hidden sector: Eq.~(\ref{eqn:energyDensityAllowed}) shows the maximum temperature ratios for specific numbers of additional hidden sectors.
-Due to the rather harsh scaling of the GW strength, $\alpha$, with temperature ratio (Eq.~(\ref{eqn:alpha2})), we take the optimistic approach of keeping the temperature ratio as high as possible for all of the hidden sectors.
+Due to the rather harsh scaling of the GW strength, $\alpha$, with temperature ratio shown in Eq.~(\ref{eqn:alpha2}), we take the optimistic approach of keeping the temperature ratio as high as allowed by CMB data for all of the hidden sectors.
 
-In all our examined cases, we focus on heavy standard sectors --- pure Yang-Mills sectors with much heavier particles (specifically quarks) and, as shown in Sec.~\ref{sec:dQCD}, the SFOPT these entail.
+In the following, we focus on heavy standard sectors --- pure Yang-Mills sectors with much heavier particles (specifically quarks) and, as shown in Sec.~\ref{sec:dQCD}, the SFOPT these entail.
 The reason for this arises from Eq.~(\ref{eqn:peakFrequency}): every exotic sector features a phase transition that occurs at $\Lambda_{ex} \sim 90$ MeV.
-If we maximize the allowed temperature ratio, this gives us a (SM) photon temperature, $T_{\gamma}$, that places our signal directly into the void between the detection region of pulsar timing arrays and space-based interferometers (see Sec.~\ref{sec:detection}).
+If we maximize the allowed temperature ratio, this gives us a (SM) photon temperature, $T_{\gamma}$, that places our signal directly in the frequency void between the detection region of pulsar timing arrays and space-based interferometers (see Sec.~\ref{sec:detection}).
 The location of the peak can be changed by dropping the temperature ratio, but the adjustment required to end up with a signal with an appropriate peak frequency makes the overall signal too weak to detect.
-In accordance with Sec.~\ref{sec:dQCD}, standard sectors can have much higher temperature phase transitions.
+As shown in Sec.~\ref{sec:dQCD}, standard sectors can have much higher temperature phase transitions.
 As such, maintaining the maximum allowed temperature ratio between the hidden sector(s) and the SM gives a much larger photon temperature and a proportionally larger peak frequency; ultimately allowing for detection by space-based interferometers.
+There are four scenarios that we examine.
 
-There are four scenarios that we examine here:
-\begin{itemize}
-\item \textbf{Maximized signal:} A single additional heavy hidden sector which saturates all current experimental bounds.
+\textbf{Maximized signal:} A single additional heavy hidden sector reheated to a temperature that saturates current experimental bounds.
 The SM photon bath temperature at the time of the hidden sector PT is $87$ GeV.
 In the $N$naturalness framework this is equivalent to reheating a standard sector with $i\sim 10^{16}$ up to the maximum allowed temperature ratio.
-\item \textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have higgs vevs that are split by a factor of $\sqrt{10^3} = (v_{h1})/(v_{h2})$.
+
+\textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have Higgs vevs that are split by a factor of 
+\begin{equation}
+ \frac{v_{h1}}{v_{h2}} = \sqrt{10^3}.
+\end{equation}
 This results in a difference in the scale of the SFOPTs leading to the SM photon bath temperature changing a large amount during the time between the PTs.
@@
 In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{15}$ up to the maximum allowed temperature ratio.
-\item \textbf{Medium split scenario:} Similar to the previous case: these sectors have higgs vevs that are split by a factor of $\sqrt{10}= (v_{h1})/(v_{h2})$, resulting in a much smaller difference in the peak frequency of their gravitational wave signals.
+
+\textbf{Medium split scenario:} Similar to the previous case: these sectors have Higgs vevs that are split by a factor of 
+ \begin{equation}
+ \frac{v_{h1}}{v_{h2}} = \sqrt{10},
+\end{equation}
+resulting in a much smaller difference in the peak frequency of their gravitational wave signals.
 In the $N$naturalness framework this is equivalent to reheating two standard sectors, one with $i\sim 10^{12}$ and another with $i\sim 10^{13}$ up to the maximum allowed temperature ratio.
-\item \textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are $\sqrt{3} \sim (v_{hi})/(v_{h(i+1)})$ larger than the previous sector.
-\end{itemize}
+
+\textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are 
+\begin{equation}
+ (v_{hi})/(v_{h(i+1)}) \sim \sqrt{3} 
+\end{equation}
+ larger than the previous sector.
+
 The GW results of these cases are presented in Fig.~\ref{fig:Haa}.
 In all cases, the summed GW signal is detectable by one or more proposed interferometers.
-When relaxing the assumptions on $\beta/H$, the scenarios in Fig.~\ref{fig:Haa} are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
-As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.
+When changing the assumptions on $\beta/H$, the scenarios in Fig.~\ref{fig:Haa} are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$.
+\draftnote{Give more details about what happens for changing $\beta$}
+
+The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors.
+As multiple sectors phase transition at different times, and therefore different SM photon temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$ given in Eq.~(\ref{eqn:peakFrequency}).
 This is seen in Fig.~\ref{fig:Haa}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
@@
 Eventually, a temperature limit will be reached where two (or multiple) distinct peaks will be visible, provided that the amplitudes are comparable.
+
 \begin{figure*}[tb]
@@
 \end{figure*}
+
 \subsection{Detection of Stochastic Graviational Waves}
@@
 Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}.
-the PLI curves are constructed using information from the power law form of the signal,
+The PLI curves are constructed using information from the power law form of the signal,
 \begin{equation}
@@
 In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations.
-If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right.
+If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
+
 \section{Conclusion}
@@
 \section*{Acknowledgement}
+
 We thank Yang Bai, Djuna Croon, Kevin Earl, and Yuhsin Tsai for helpful discussions.
@@
 both thank the 2018 Theoretical Advanced Study Institute in Elementary Particle Physics Program (TASI) for setting up a platform for discussion which seeded the genesis of this project.
-This work was supported in part by the Natural Sciences and Engineering Research Council of
-Canada (NSERC). D.L. acknowledges support from the NSERC Postgraduate Scholarships-Doctoral Program (PGS D).
+This work was supported in part by the Natural Sciences and Engineering Research Council of Canada (NSERC).
+D.L.
+acknowledges support from the NSERC Postgraduate Scholarships-Doctoral Program (PGS D).
 

### 2019-10-02 gwnnDraft02.tex
refs

@@
 The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe.
-Future experiments~\cite{Seto:2001qf,Crowder:2005nr,Harry:2006fi,Sathyaprakash:2012jk,Janssen:2014dka,2017arXiv170200786A,Sato:2017dkf} will greatly expand the frequency range observable.
+Future experiments~\cite{Danzmann:1994mma,Seto:2001qf,Crowder:2005nr,PhysRevD.72.083005,Harry:2006fi,Sathyaprakash:2012jk,Janssen:2014dka,Audley:2017drz,2017arXiv170200786A,Sato:2017dkf,Sato_2017,10.1093/ptep/pty078} will greatly expand the frequency range observable.
 Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}.
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa (blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa~\citep{Audley:2017drz} (blue), DECIO (light blue)~\citep{10.1093/ptep/pty078}, BBO (red)~\citep{PhysRevD.72.083005} , SKA~\cite{Janssen:2014dka} 5-year (purple), SKA 10-year (orange), SKA 20-year (green).
+}
 \label{fig:Haa}
@@
 \end{equation}
-The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
+The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
 We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.

### 2019-10-02 gwnnDraft02.tex
small edits

@@
 The form of the GW energy density at the time of nucleation is given by~\citep{Breitbach:2018ddu},
-\begin{equation}
+\begin{equation}\label{eqn::GWengdensity}
 h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
@@
 These must then be evolved to relate to their values at the time of observation.
-Where we have assumed \draftnote{isn't this the definition of runaway?} an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
+Where  $v \sim 1$ for runaway bubbles.
 $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
@@
 When changing the assumptions on $\beta/H$, the scenarios in Fig.~\ref{fig:Haa} are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$.
-\draftnote{Give more details about what happens for changing $\beta$}
+As $\beta/H$ increases (decreases) the peak frequency moves to higher (lower) frequencies, dictated by Eq.~(\ref{eqn:peakFrequency}), where as the amplitude decreases (increases) shown in Eq.~(\ref{eqn::GWengdensity}).
 
@@
 \label{sec:detection}
-A unpolarized stocastic gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA).
+A \textit{stochastic} gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA).
 These interferometers/PTAs quote their experimental sensistivies in terms of spectral noise curves, $S_{\textrm{eff}}(f)$, which can be translated into units of energy density through $h^2 \Omega_{\textrm{eff}}(f) = \frac{2\pi^2}{3H^2}f^3 S_{\textrm{eff}}(f)$.
@@
 \begin{split}
-\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
+\rho^2 =  \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
 \\
-\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
+\rho^2 = 2 \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
 \end{split}
 \end{equation}
-Where $T$ is the exposure time of the experiment.
+Where $\mathcal{T}$ is the exposure time of the experiment.
 The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
@@
 \begin{equation}
-h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}
+h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\gamma}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\gamma}
 \end{equation}
-where $\beta$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities. 
-The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\beta \in (-8,-7,-6, ...
+where $\gamma$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities. 
+The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\gamma \in (-8,-7,-6, ...
 , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$.
@@
 \begin{equation}
-h^2 \Omega_{\textrm{PLI}} = \max\limits_{\beta}\bigg[ h^2 \Omega_{\beta}\bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}  \bigg].
+h^2 \Omega_{\textrm{PLI}} = \max\limits_{\gamma}\bigg[ h^2 \Omega_{\gamma}\bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\gamma}  \bigg].
 \end{equation}
 The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
-We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
+We have assumed an observation time of $\mathcal{T} = 4 $ years for the interferometers and $\mathcal{T}= 5, 10, 20 $  years for the various stages of SKA.
 In the case of the PTA experiments, the sensitivity curves are dependent on how frequently the pulsar's timing residuals, $\delta t$, are measured.

### 2019-10-02 gwnnDraft02.tex
edits

@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
-
-\draftnote{Somewhere the argument as to how exotic sectors produce runaway bubbles got lost. Should probably put that here. Also, do we want to define runaway, or is it obvious?}
-Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness \footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
-Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+The exotic sectors have massless degrees of freedom pre-phase transition and pions and baryons with negligible masses post-phase transition, leading to small $\alpha_{\infty}$ from Eq.~(\ref{eqn:critPTstrength}).
+\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
+Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
 Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).

### 2019-10-02 gwnnDraft02.tex
small fixes

@@
 Here, we construct several different scenarios that are both detectable and demonstrate a variety of gravitational wave profiles.
-Specifically, we explore scenarios that lead to a deviation in the peak behaviour of the total GW signal (the convolution of stochastic GW from individual SFOPT) from a standard power law signal.
+Specifically, we explore scenarios that lead to a deviation in the peak behaviour of the total GW signal (the superposition of stochastic GW from individual SFOPT) from a standard power law signal.
 
@@
 As multiple sectors phase transition at different times, and therefore different SM photon temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$ given in Eq.~(\ref{eqn:peakFrequency}).
-This is seen in Fig.~\ref{fig:Haa}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum.
+This is seen in Fig.~\ref{fig:Haa}, where the spectrum peaks are shifted causing a peak broadening of the summed spectrum.
 The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature).

### 2019-10-03 gwnnDraft02.tex
refs

--- 2019-10-02 gwnnDraft02.tex
@@
 The form of the GW energy density at the time of nucleation is given by~\citep{Breitbach:2018ddu},
-\begin{equation}\label{eqn::GWengdensity}
+\begin{equation}
 h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
@@
 These must then be evolved to relate to their values at the time of observation.
-Where  $v \sim 1$ for runaway bubbles.
+Where we have assumed \draftnote{isn't this the definition of runaway?} an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles.
 $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
@@
 When changing the assumptions on $\beta/H$, the scenarios in Fig.~\ref{fig:Haa} are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$.
-As $\beta/H$ increases (decreases) the peak frequency moves to higher (lower) frequencies, dictated by Eq.~(\ref{eqn:peakFrequency}), where as the amplitude decreases (increases) shown in Eq.~(\ref{eqn::GWengdensity}).
+\draftnote{Give more details about what happens for changing $\beta$}
 
@@
 \label{sec:detection}
-A \textit{stochastic} gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA).
+A unpolarized stocastic gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA).
 These interferometers/PTAs quote their experimental sensistivies in terms of spectral noise curves, $S_{\textrm{eff}}(f)$, which can be translated into units of energy density through $h^2 \Omega_{\textrm{eff}}(f) = \frac{2\pi^2}{3H^2}f^3 S_{\textrm{eff}}(f)$.
@@
 \begin{split}
-\rho^2 =  \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
+\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}
 \\
-\rho^2 = 2 \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
+\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
 \end{split}
 \end{equation}
-Where $\mathcal{T}$ is the exposure time of the experiment.
+Where $T$ is the exposure time of the experiment.
 The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
@@
 \begin{equation}
-h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\gamma}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\gamma}
+h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}
 \end{equation}
-where $\gamma$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities. 
-The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\gamma \in (-8,-7,-6, ...
+where $\beta$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities. 
+The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\beta \in (-8,-7,-6, ...
 , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$.
@@
 \begin{equation}
-h^2 \Omega_{\textrm{PLI}} = \max\limits_{\gamma}\bigg[ h^2 \Omega_{\gamma}\bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\gamma}  \bigg].
+h^2 \Omega_{\textrm{PLI}} = \max\limits_{\beta}\bigg[ h^2 \Omega_{\beta}\bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}  \bigg].
 \end{equation}
 The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
-We have assumed an observation time of $\mathcal{T} = 4 $ years for the interferometers and $\mathcal{T}= 5, 10, 20 $  years for the various stages of SKA.
+We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA.
 In the case of the PTA experiments, the sensitivity curves are dependent on how frequently the pulsar's timing residuals, $\delta t$, are measured.
@@
 In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations.
-If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
+If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$~(\ref{fig:Haa}) are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
 
@@
 
-Here, we examined several scenarios (including $N$naturalness) that involve multiple hidden sectors and calculated the GW profiles present.
+Here, we examined scenarios including $N$naturalness that involve multiple hidden sectors and calculated the GW profiles present.
 Our GW projections demonstrate that although vanilla $N$naturalness is not projected to be detectable in the near future, more generalized scenarios with multiple hidden sector SFOPTs are in an observable region and will begin to be probed by next generation space experiments.
@@
 The multiple transitions that occur in the models outlined here create signals that follow this trend: although the individual GW do obey approximate power laws, their sum does not --- leading to a unique signal indicating so-called dark complexity.
-Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors.
-ultimately providing another means to test and constrain theories.
+Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors, ultimately providing another means to test and constrain theories.
 

### 2019-10-03 gwnnDraft02.tex

--- 2019-10-02 gwnnDraft02.tex
@@
 \end{equation}
-The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array.
+The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken 
+from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and~\citep{Breitbach:2018ddu, Janssen:2014dka} 
+for the SKA pulsar timing array. 
 We have assumed an observation time of $\mathcal{T} = 4 $ years for the interferometers and $\mathcal{T}= 5, 10, 20 $  years for the various stages of SKA. 

### 2019-10-03 gwnnDraft02.tex
changes to captions

@@
 \caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}.
+The curve corresponding to the sum of the sectors is approximately equal to the $i=1$ curve.
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa (blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).
-Details of these curves are given in Sec.~\ref{sec:detection}.}
+The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa~\citep{Audley:2017drz} (blue), DECIGO~\citep{10.1093/ptep/pty078} (light blue), BBO~\citep{PhysRevD.72.083005} (red), SKA~\cite{Janssen:2014dka} 5-year (purple), SKA 10-year (orange), SKA 20-year (green).
+}
 \label{fig::Nnatural}
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa~\citep{Audley:2017drz} (blue), DECIO (light blue)~\citep{10.1093/ptep/pty078}, BBO (red)~\citep{PhysRevD.72.083005} , SKA~\cite{Janssen:2014dka} 5-year (purple), SKA 10-year (orange), SKA 20-year (green).
+The shaded curves are the same as Fig.~\ref{fig::Nnatural}.
 }
@@
 The multiple transitions that occur in the models outlined here create signals that follow this trend: although the individual GW do obey approximate power laws, their sum does not --- leading to a unique signal indicating so-called dark complexity.
-Explicitly, a broadening or distortion of the signal around the peak frequency could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors, ultimately providing another means to test and constrain theories.
+Explicitly, a broadening or distortion of the signal around the peak frequency, precisely where the signal has the most energy, could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors, ultimately providing another means to test and constrain theories.
 
-Shifting to the other part of our framework, our results leads to the question ``are current experiments able to probe non power law signals?" For frequency ranges away from the peak of the total GW signals the quoted detection thresholds should hold: the signals fall off in a fashion identical to a power law.
+Shifting to the other part of our framework, our results leads to the question ``how well can experiments probe non power law signals?" For frequency ranges away from the peak of the total GW signals the quoted detection thresholds should hold: the signals fall off as a power law to a very good approximation.
 However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law.

### 2019-10-03 gwnnDraft02.tex
Added table

@@
 The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe.
-Future experiments~\cite{Danzmann:1994mma,Seto:2001qf,Crowder:2005nr,PhysRevD.72.083005,Harry:2006fi,Sathyaprakash:2012jk,Janssen:2014dka,Audley:2017drz,2017arXiv170200786A,Sato:2017dkf,Sato_2017,10.1093/ptep/pty078} will greatly expand the frequency range observable.
+Future experiments~\cite{Danzmann:1994mma,Seto:2001qf,Crowder:2005nr,PhysRevD.72.083005,Harry:2006fi,Janssen:2014dka,Audley:2017drz,2017arXiv170200786A,Sato_2017,10.1093/ptep/pty078} will greatly expand the frequency range observable.
 Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}.
@@
 As such, maintaining the maximum allowed temperature ratio between the hidden sector(s) and the SM gives a much larger photon temperature and a proportionally larger peak frequency; ultimately allowing for detection by space-based interferometers.
-There are four scenarios that we examine.
+There are four scenarios that we examine, with key parameters presented in Tab.~\ref{tab:cases}.
 
-\textbf{Maximized signal:} A single additional heavy hidden sector reheated to a temperature that saturates current experimental bounds.
+\begin{table*}[t]
+\begin{center}
+\begin{tabular}{ |p{3cm}||p{3cm}|p{3cm}|p{3cm}|p{3cm}|  }
+ \hline
+ \multicolumn{5}{|c|}{Parameters for multi-hidden sector scenarios} \\
+ \hline
+\multicolumn{5}{|c|}{Maximized signal} \\
+ \hline
+ Additional Sector & Higgs vev & $\Lambda^{ex}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & $N$naturalness index\\
+ \hline
+ 1 & 24.6 EeV  & 38.6 & 87.7 & $10^{16}$ \\
+ \hline
+\multicolumn{5}{|c|}{Large split scenario} \\
+ \hline
+ Additional Sector & Higgs vev & $\Lambda^{ex}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & $N$naturalness index\\
+ \hline
+ 1 & 246 PeV  & 10.8 & 30.3 & $10^{12}$ \\
+ 2 & 7.8 EeV  & 28.1 & 78.6 & $10^{15}$ \\
+ \hline
+ \multicolumn{5}{|c|}{Medium split scenario} \\
+ \hline
+ Additional Sector & Higgs vev & $\Lambda^{ex}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & $N$naturalness index\\
+ \hline
+ 1 & 246 PeV  & 10.8 & 30.3 & $10^{12}$ \\
+ 2 & 778 PeV  & 14.9 & 41.6 & $10^{13}$ \\
+ \hline
+ \multicolumn{5}{|c|}{Five sector scenario} \\
+ \hline
+ Additional Sector & Higgs vev & $\Lambda^{ex}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & $N$naturalness index\\
+ \hline
+ 1 & 246 PeV & 10.8 & 38.8 & $10^{12}$ \\
+ 2 & 426 PeV & 12.6 & 45.2 & $3*10^{12}$ \\
+ 3 & 778 PeV & 14.9 & 53.3 & $10^{13}$ \\
+ 4 & 1.3 EeV & 17.3 & 62.1 & $3*10^{13}$ \\
+ 5 & 2.5 EeV & 20.5 & 73.3 & $10^{14}$ \\
+ \hline
+\end{tabular}
+\caption{Outline of parameters used for the various multi-hidden sector scenarios.
+The higgs vev is the vev for the given additional sector, $\Lambda^{ex}_{QCD}$ is the QCD phase transition in the additional sector, and $T_\gamma$ is the temperature of the SM photon bath when the SFOPT occurs in the additional sector.}\label{tab:cases}
+\end{center}
+\end{table*}
+
+\begin{itemize}
+\item \textbf{Maximized signal:} A single additional heavy hidden sector reheated to a temperature that saturates current experimental bounds.
 The SM photon bath temperature at the time of the hidden sector PT is $87$ GeV.
@@
 
-\textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have Higgs vevs that are split by a factor of 
+\item \textbf{Large split scenario:} A scenario where two additional hidden sectors have been reheated --- these sectors have Higgs vevs that are split by a factor of 
 \begin{equation}
@@
 
-\textbf{Medium split scenario:} Similar to the previous case: these sectors have Higgs vevs that are split by a factor of 
+\item \textbf{Medium split scenario:} Similar to the previous case: these sectors have Higgs vevs that are split by a factor of 
  \begin{equation}
@@
 
-\textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are 
+\item \textbf{Five sector scenario:} Five sectors are reheated to the maximum allowed temperature ratio, each with vevs that are 
 \begin{equation}
@@
  larger than the previous sector.
+
+\end{itemize}
 

### 2019-10-03 gwnnDraft02.tex
adjusted table and edits

@@
 Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}.
-Thus, searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.
+Thus, searches for this background of gravitational waves can give direct information about the history of the universe before big bang nucleosynthesis.
 Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
@@
 \begin{itemize}
-\item \textbf{Standard Sectors}: Those with $m_H^2 < 0$ where electroweak symmetry is broken by the vacuum expectation value (VEV) of a fundamental scalar.
+\item \textbf{Standard Sectors}: Those with $m_H^2 < 0$ where electroweak symmetry is broken by the vacuum expectation value (vev) of a fundamental scalar.
 As in~\cite{Arkani-Hamed:2016rle}, we assume that the standard sector with the smallest absolute value of $m_H^2$ is the Standard Model.
@@
 \begin{center}
-\begin{tabular}{ |p{3cm}||p{3cm}|p{3cm}|p{3cm}|p{3cm}|  }
+\begin{tabular}{ |p{2cm}||p{3cm}|p{3cm}|p{3cm}|p{2cm}|  }
  \hline
- \multicolumn{5}{|c|}{Parameters for multi-hidden sector scenarios} \\
+ \multicolumn{5}{|c|}{Parameters for multi-hidden sector benchmarks} \\
  \hline
@@
  \hline
- Additional Sector & Higgs vev & $\Lambda^{ex}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & $N$naturalness index\\
+ Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
  \hline
- 1 & 24.6 EeV  & 38.6 & 87.7 & $10^{16}$ \\
+ 1 & $24.6 \times 10^{9}$ & 38.6 & 87.7 & $10^{16}$ \\
  \hline
-\multicolumn{5}{|c|}{Large split scenario} \\
+\multicolumn{5}{|c|}{Large split} \\
  \hline
- Additional Sector & Higgs vev & $\Lambda^{ex}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & $N$naturalness index\\
+ Sector & Higgs vev (GeV & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
  \hline
- 1 & 246 PeV  & 10.8 & 30.3 & $10^{12}$ \\
- 2 & 7.8 EeV  & 28.1 & 78.6 & $10^{15}$ \\
+ 1 & $246 \times 10^6$  & 10.8 & 30.3 & $10^{12}$ \\
+ 2 & $7.8 \times 10^9$  & 28.1 & 78.6 & $10^{15}$ \\
  \hline
- \multicolumn{5}{|c|}{Medium split scenario} \\
+ \multicolumn{5}{|c|}{Medium split} \\
  \hline
- Additional Sector & Higgs vev & $\Lambda^{ex}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & $N$naturalness index\\
+ Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
  \hline
- 1 & 246 PeV  & 10.8 & 30.3 & $10^{12}$ \\
- 2 & 778 PeV  & 14.9 & 41.6 & $10^{13}$ \\
+ 1 & $246 \times 10^{6}$ & 10.8 & 30.3 & $10^{12}$ \\
+ 2 & $778 \times 10^6$  & 14.9 & 41.6 & $10^{13}$ \\
  \hline
- \multicolumn{5}{|c|}{Five sector scenario} \\
+ \multicolumn{5}{|c|}{Five sectors} \\
  \hline
- Additional Sector & Higgs vev & $\Lambda^{ex}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & $N$naturalness index\\
+ Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
  \hline
- 1 & 246 PeV & 10.8 & 38.8 & $10^{12}$ \\
- 2 & 426 PeV & 12.6 & 45.2 & $3*10^{12}$ \\
- 3 & 778 PeV & 14.9 & 53.3 & $10^{13}$ \\
- 4 & 1.3 EeV & 17.3 & 62.1 & $3*10^{13}$ \\
- 5 & 2.5 EeV & 20.5 & 73.3 & $10^{14}$ \\
+ 1 & $246 \times 10^6$ & 10.8 & 38.8 & $10^{12}$ \\
+ 2 & $426 \times 10^6$ & 12.6 & 45.2 & $3*10^{12}$ \\
+ 3 & $778 \times 10^6$ & 14.9 & 53.3 & $10^{13}$ \\
+ 4 & $1.3 \times 10^9$ & 17.3 & 62.1 & $3*10^{13}$ \\
+ 5 & $2.5 \times 10^9$ & 20.5 & 73.3 & $10^{14}$ \\
  \hline
@@
 \caption{Outline of parameters used for the various multi-hidden sector scenarios.
-The higgs vev is the vev for the given additional sector, $\Lambda^{ex}_{QCD}$ is the QCD phase transition in the additional sector, and $T_\gamma$ is the temperature of the SM photon bath when the SFOPT occurs in the additional sector.}\label{tab:cases}
+The higgs vev is the vev for the given additional sector, $\Lambda^{AS}_{QCD}$ is the QCD phase transition in the additional sector, and $T_\gamma$ is the temperature of the SM photon bath when the SFOPT occurs in the additional sector.
+The index indicates the equivalent sector from the $N$naturalness model (Eq.~(\ref{eqn:vevs})).}\label{tab:cases}
 \end{center}

### 2019-10-03 gwnnDraft02.tex
new plots

--- 2019-10-03 gwnnDraft02.tex
@@
 \includegraphics[scale=.3]{Nnatral.png} 
-\caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}.
+\caption{ Gravitational wave spectral energy density for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}.
 The curve corresponding to the sum of the sectors is approximately equal to the $i=1$ curve.
@@
 \hfill
-\caption{ Gravitational wave power spectrum for various models.
-The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures.
-The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$).
-All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
+\caption{ Gravitational wave spectral energy density for the various scenarios found in Tab.~(\ref{tab:cases}).
+All contributions are assumed to be purely from runaway bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
 The shaded curves are the same as Fig.~\ref{fig::Nnatural}.

### 2019-10-03 gwnnDraft02.tex

--- 2019-10-03 gwnnDraft02.tex
@@
  \hline
- \multicolumn{5}{|c|}{Five sectors} \\
+ \multicolumn{5}{|c|}{Five sector} \\
  \hline
@@
  1 & $246 \times 10^6$ & 10.8 & 38.8 & $10^{12}$ \\
- 2 & $426 \times 10^6$ & 12.6 & 45.2 & $3*10^{12}$ \\
+ 2 & $426 \times 10^6$ & 12.6 & 45.2 & $3\times10^{12}$ \\
  3 & $778 \times 10^6$ & 14.9 & 53.3 & $10^{13}$ \\
- 4 & $1.3 \times 10^9$ & 17.3 & 62.1 & $3*10^{13}$ \\
+ 4 & $1.3 \times 10^9$ & 17.3 & 62.1 & $3\times10^{13}$ \\
  5 & $2.5 \times 10^9$ & 20.5 & 73.3 & $10^{14}$ \\
@@
 In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations.
-If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
+If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~\ref{fig::Nnatural} $\&$ \ref{fig:Haa} are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
 

### 2019-10-03 gwnnDraft02.tex
more fixes

@@
 The higgs vev is the vev for the given additional sector, $\Lambda^{AS}_{QCD}$ is the QCD phase transition in the additional sector, and $T_\gamma$ is the temperature of the SM photon bath when the SFOPT occurs in the additional sector.
-The index indicates the equivalent sector from the $N$naturalness model (Eq.~(\ref{eqn:vevs})).}\label{tab:cases}
+The index indicates the equivalent sector from the $N$naturalness model (Eq.~(\ref{eqn:vevs})).
+It should be noted that although the various sectors transition at different temperatures, they are all assumed to be reheated to the same initial temperature.}\label{tab:cases}
 \end{center}

### 2019-10-03 gwnnDraft02.tex
more table stuff

@@
 
-\subsection{Generalized Reheating Scenarios}
+\subsection{Generalized Reheating Scenarios}\label{sec:genReheat}
 
@@
  \hline
- Sector & Higgs vev (GeV & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
+ Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
  \hline
@@
 The index indicates the equivalent sector from the $N$naturalness model (Eq.~(\ref{eqn:vevs})).
-It should be noted that although the various sectors transition at different temperatures, they are all assumed to be reheated to the same initial temperature.}\label{tab:cases}
+It should be noted that although the various sectors transition at different temperatures, they are all assumed to be reheated to the same initial temperature as discussed in Sec.~\ref{sec:genReheat}.}\label{tab:cases}
 \end{center}

### 2019-10-03 gwnnDraft02.tex
small changes

@@
 This means that the masses of the fermions and the $W$ and $Z$ will also increase proportional to $\sqrt{i}$.
-The consequences of this scaling on the confinement scale of QCD in the $i \geq 1$ sectors is further discussed in Sec.
-\ref{sec:dQCD}.
+The consequences of this scaling on the confinement scale of QCD in the $i \geq 1$ sectors is further discussed in Sec.~\ref{sec:dQCD}.
 
@@
 As we will see, the extremely light quarks that appear in these sectors dramatically change the nature of the QCD phase transition --- unlike the SM, the transition is strongly first order.
-Again, this is further developed in Sec.
-\ref{sec:dQCD}.
+Again, this is further developed in Sec.~\ref{sec:dQCD}.
 Crucially, this results in the production of gravitational waves.
-This is the physical signature we explore in this paper; the calculation and results are presented in Sec.
-\ref{sec:gw}.
+This is the physical signature we explore in this paper; the calculation and results are presented in Sec.~\ref{sec:gw}.
 
@@
 \end{itemize}
-Light means mass small compared to the confinement scale $\Lambda_{QCD}$, but what that means quantitatively is not precisely determined.
+
+Light indicates a mass small compared to the confinement scale $\Lambda_{QCD}$, but what that means quantitatively is not precisely determined.
 In the SM, the up and down quarks are light, but the strange is not sufficiently light for an SFOPT.
@@
 This leads to increasingly heavy particle spectra for higher sectors --- eventually leading to sectors that are essentially pure Yang-Mills that feature strong first order phase transitions.
-This, of course, begs the question: at what index $i$ do said phase transitions begin?
+This, of course, prompts the question: at what index $i$ do said phase transitions begin?
 %The actual boundary of region of interest on the Columbia plot is not precisely known and further lattice simulations are required to determine exactly where in parameter space cross-over transitions end and first order transitions begin.
@@
 If we take Higgs vevs as high as the GUT scale $\sim 10^{16}$ GeV, then we can use Eq.~(\ref{eqn:lambda2adj}) to get confinement scales as high as $\sim 38 \,\gev$.
-The signals of this sector and other test cases like it are explored in Sec.
-\ref{sec:gw}.
+The signals of this sector and other test cases like it are explored in Sec.~\ref{sec:gw}.
 

### 2019-10-03 gwnnDraft02.tex
small edits

@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
-The exotic sectors have massless degrees of freedom pre-phase transition and pions and baryons with negligible masses post-phase transition, leading to small $\alpha_{\infty}$ from Eq.~(\ref{eqn:critPTstrength}).
-\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
-Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
-Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
+The exotic sectors have massless degrees of freedom pre-phase transition and pions and baryons with negligible masses post-phase transition, leading to small $\alpha_{\infty}$ from Eq.~(\ref{eqn:critPTstrength})\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
+Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+Explicitly, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
 In this case, the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
@@
 Here, we construct several different scenarios that are both detectable and demonstrate a variety of gravitational wave profiles.
-Specifically, we explore scenarios that lead to a deviation in the peak behaviour of the total GW signal (the superposition of stochastic GW from individual SFOPT) from a standard power law signal.
+Specifically, we explore benchmarks that lead to a deviation in the peak behaviour of the total GW signal (the superposition of stochastic GW from individual SFOPT) from a standard power law signal.
 
@@
 In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations.
-If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~\ref{fig::Nnatural} $\&$ \ref{fig:Haa} are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
+If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PLI curves in Figs.~\ref{fig::Nnatural} $\&$ \ref{fig:Haa} are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
 
@@
 
-Here, we examined scenarios including $N$naturalness that involve multiple hidden sectors and calculated the GW profiles present.
+Here, we examined scenarios, including $N$naturalness, that involve multiple hidden sectors and calculated the GW profiles present.
 Our GW projections demonstrate that although vanilla $N$naturalness is not projected to be detectable in the near future, more generalized scenarios with multiple hidden sector SFOPTs are in an observable region and will begin to be probed by next generation space experiments.

### 2019-10-03 gwnnDraft02.tex
added a comma

--- 2019-10-03 gwnnDraft02.tex
@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
-The exotic sectors have massless degrees of freedom pre-phase transition and pions and baryons with negligible masses post-phase transition, leading to small $\alpha_{\infty}$ from Eq.~(\ref{eqn:critPTstrength}).
-\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
-Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+The exotic sectors have massless degrees of freedom pre-phase transition and pions and baryons with negligible masses post-phase transition, leading to small $\alpha_{\infty}$ from Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
 Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
@@
 As such, maintaining the maximum allowed temperature ratio between the hidden sector(s) and the SM gives a much larger photon temperature and a proportionally larger peak frequency; ultimately allowing for detection by space-based interferometers.
-There are four scenarios that we examine, with key parameters presented in Tab.~\ref{tab:cases}.
 
@@
 
+There are four scenarios that we examine, with key parameters presented in Tab.~\ref{tab:cases}.
 \begin{itemize}

### 2019-10-03 gwnnDraft02.tex

--- 2019-10-03 gwnnDraft02.tex
@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
-The exotic sectors have massless degrees of freedom pre-phase transition and pions and baryons with negligible masses post-phase transition, leading to small $\alpha_{\infty}$ from Eq.~(\ref{eqn:critPTstrength})\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
-Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+The exotic sectors have massless degrees of freedom pre-phase transition and pions and baryons with negligible masses post-phase transition, leading to small $\alpha_{\infty}$ from Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.

### 2019-10-03 gwnnDraft02.tex
fixed discussion of eq 40.

--- 2019-10-03 gwnnDraft02.tex
@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
-The exotic sectors have massless degrees of freedom pre-phase transition and pions and baryons with negligible masses post-phase transition, leading to small $\alpha_{\infty}$ from Eq.~(\ref{eqn:critPTstrength})\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
+The exotic sectors have essentially massless degrees of freedom pre-phase transition and pions with negligible masses post-phase transition.
+Other composite particles, such as baryons, do gain a mass of the order of the transition; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength})\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
 Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.

### 2019-10-03 gwnnDraft02.tex
email
acknowledgements
minor changes sects 1-3

@@
 \begin{abstract}
-We explore the possibility of detecting gravitational waves generated by 1st order phase transitions in multiple dark sectors.
+We explore the possibility of detecting gravitational waves generated by first order phase transitions in multiple hidden sectors.
 $N$naturalness is taken as a sample model that features multiple additional sectors, many of which undergo phase transitions that produce gravitational waves.
@@
 Thus, searches for this background of gravitational waves can give direct information about the history of the universe before big bang nucleosynthesis.
-Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
+Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model (SM) as long they are reheated after inflation.
 This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Jaeckel:2016jlh,Addazi:2016fbj,Hardy:2016mns,Dienes:2016vei,Tsumura:2017knk,Acharya:2017szw,Bernal:2017kxu,Aoki:2017aws,Heikinheimo:2018esa,Geller:2018mwu,Croon:2018erz,Baldes:2018emh,Bai:2018dxf,Breitbach:2018ddu,Fairbairn:2019xog,Helmboldt:2019pan,Caputo:2019wsd,Bertone:2019irm}.
@@
 $m_H^2 > 0$ leads to no vev for the Higgs, and electroweak symmetry is only broken at very low scales due to the phase transition from free quarks to confinement at the QCD scale $\Lambda_{QCD}$~\cite{Susskind:1978ms}, and the masses of the $W$ and $Z$ are comparable to those of QCD resonances.
-The mass of fundamental fermions are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs multiplet.
+The mass of fundamental fermions are produced via four-fermion interactions generated after integrating out the SU$(2)$ Higgs doublet.
 This leads to very light fermions:
@@
 Due to the confining nature of QCD, the exact nature of the phase transition is often difficult to ascertain analytically and requires the study of lattice simulations.
-In the SM, it is known that the phase transition is a crossover and does lead to gravitational wave signals~\cite{Aoki:2006we,Bhattacharya:2014ara}.
+In the SM, it is known that the phase transition is a crossover and does not lead to gravitational wave signals~\cite{Aoki:2006we,Bhattacharya:2014ara}.
 In the general case with 3 or more colours, the phase transition can be strongly first order in two regimes~\cite{SVETITSKY1982423,Pisarski:1983ms,Panero:2009tv}:
@@
 \end{itemize}
-
+%
 Light indicates a mass small compared to the confinement scale $\Lambda_{QCD}$, but what that means quantitatively is not precisely determined.
@@
 where $n_f^i$ is the number of quark flavours with mass less than $\mu/2$ and $\Lambda^i$ is the scale where it would confine if all quarks remain massless.
-In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 5$ in $\overline{MS}$~\cite{PhysRevD.98.030001}.
+In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 6$ in $\overline{MS}$~\cite{PhysRevD.98.030001}.
 Because we have set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at high scales for all sectors.
@@
 \end{equation} 
-at the energy scale we're interested in.
-$\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a standard model value of $\Lambda^{(6)}_{MS} =(89 \pm 6)\, \mev$~\cite{PhysRevD.98.030001}.
-Rewriting Eq.~(\ref{eqn:lambda2}) in terms of standard model variables,
+at the energy scale we are interested in.
+$\Lambda^i_{(6)}$ is identical for all sectors and is taken to have a Standard Model value of $\Lambda^{(6)}_{MS} =(89 \pm 6)\, \mev$~\cite{PhysRevD.98.030001}.
+Rewriting Eq.~(\ref{eqn:lambda2}) in terms of Standard Model variables,
 \begin{equation}\label{eqn:lambda2adj}
@@
 \begin{equation}
-m_{\pi}^i \sim \sqrt{\frac{m_a^i+m_b^i}{m_u + m_d}} m_{\pi}.
+m_{\pi}^i \sim \sqrt{\frac{m_a^i+m_b^i}{m_u + m_d}}\, m_{\pi} \ll \Lambda_{ex}.
 \label{eq:ith_pion_mass}

### 2019-10-03 gwnnDraft02.tex
minor changes sects 4-5

@@
 \email{
-PaulSmith3@cmail.carleton.ca \\
+Paul.Smith3@carleton.ca \\
 Dylan.linthorne@carleton.ca \\
@@
 
-\section{Reheating N Sectors}
+\section{Reheating $N$ Sectors}
 \label{sec:reheat}
@@
 However, a large amount of the Universe's energy density must ultimately be deposited in our own sector for $N$naturalness to avoid instant exclusion.
-In order to accomplish this the decay width into each sector must drop as $\vert m_H\vert$ grows.
-If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$ then we construct a model that behaves as desired.
+In order to accomplish this, the decay width of the reheaton into each sector must drop as $\vert m_H\vert$ grows.
+If we insist that the reheaton is a gauge singlet that is both the dominant coupling to every sector's Higgs and lighter than the naturalness cutoff $\Lambda_H/\sqrt{N}$, then we construct a model that behaves as desired.
 The appropriate Lagrangian for a scalar reheaton $\phi$ is: 
@@
 Thus we only consider relatively low reheating temperatures $\lesssim 100$ GeV.
+
 Ultimately, after examining the gravitational wave case produced by standard $N$naturalness, we also consider a more generic parameterization where the reheating temperature of each sector is a free parameter and is in general uncorrelated with the Higgs mass parameter.
@@
 After the higgses freeze out, 4 degrees of freedom are lost; when the QCD phase transition occurs 35 bosonic degrees of freedom are gained while 72 fermionic are lost, leaving 56.75 effective degrees of freedom.
-At the time of photon decoupling ($T_\gamma \sim 0.39 \,\ev$) while the temperature of the exotic sectors is lower still.
+At the time of photon decoupling, $T_\gamma \sim 0.39 \;\ev$ while the temperature of the exotic sectors is lower.
 This means that for sectors with small and moderate $i$, we can use Eqs.~(\ref{eqn:exoticFM}) and~(\ref{eq:ith_pion_mass}) to see that the pions will be non-relativistic  leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.
@@
 This sum is dominated by $i=1$, the sector with the lowest Higgs mass (and thus the most energy density) gives us a contribution of $\mathcal{O} (10^{-4})$ to $\Delta N_{eff}$.
-Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$, well under current CMB bounds.
+Evolving the sectors thermal histories forward in time to the recombination era gives us a slightly larger value, but still of order $\mathcal{O}(10^{-4})$, well below current CMB bounds.
 It should be noted that modifying the exotic sectors' structure (e.g.
@@
 where all the hidden sectors have the same temperature as one another.
+
 Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own.
-In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the cirtical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale as long as their temperatures are below the bounds presented here.
+In terms of the $N$naturalness framework, this means we can get an SFOPT for QCD if we look at sectors with $i$ greater than the critical index of Eq.~(\ref{eqn:critIndex}) where all the quark masses are above the QCD confinement scale, as long as their temperatures are below the bounds presented here.
  %of looking at various different sectors above the critical index, as mentioned in Sec.~\ref{sec:dQCD}.
@@
 
-\section*{Acknowledgement}
+\section*{Acknowledgements}
 

### 2019-10-03 gwnnDraft02.tex
inset plots

@@
 Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}.
-Thus, searches for this background of gravitational waves can give direct information about the history of the universe before big bang nucleosynthesis.
+Thus, searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis.
 Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation.
@@
 \begin{itemize}
-\item \textbf{Standard Sectors}: Those with $m_H^2 < 0$ where electroweak symmetry is broken by the vacuum expectation value (vev) of a fundamental scalar.
+\item \textbf{Standard Sectors}: Those with $m_H^2 < 0$ where electroweak symmetry is broken by the vacuum expectation value (VEV) of a fundamental scalar.
 As in~\cite{Arkani-Hamed:2016rle}, we assume that the standard sector with the smallest absolute value of $m_H^2$ is the Standard Model.

### 2019-10-04 gwnnDraft02.tex
sec 6

@@
 These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.
-These bubbles are described by the following Euclidean action~\cite{Linde:1981zj}
+These bubbles are described by the following Euclidean action~\cite{Linde:1981zj}:
 %
@@
 The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.
-Assuming that the SM sector is radiation dominated, a quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition, $\epsilon$, to the energy density of radiation, at the time of nucleation~\citep{Espinosa:2010hh} ,
+Assuming that the SM sector is radiation dominated, a quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition, $\epsilon$, to the energy density of radiation, at the time of nucleation~\citep{Espinosa:2010hh},
 \begin{equation}
@@
 The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors.
-It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities)
+It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective energy densities
 \begin{equation}\label{eqn:RelaDOF}
@@
 Due to the lack of a general analytic QCD potential, it is not possible to use Eq.~(\ref{eqn:BH}) to calculate $\beta/H$.
-There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} which predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments make specific assumptions about the potential.
+There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} that predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments make specific assumptions about the potential.
 In more recent work, some authors~\citep{Helmboldt:2019pan,Bai:2018dxf} have attempted to estimate it using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models.
@@
 \begin{itemize}
-\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration.
-With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514, Huber_2008}.
-\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves.
-With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$~\citep{PhysRevLett.112.041301}.
-\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: Turbulence within the plasma, left over from the sound wave propagation, will produce gravitational waves.
-With efficiency factor $\kappa_{
+\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration, with efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$~\citep{PhysRevD.45.4514, Huber_2008}.
+\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves, with efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$~\citep{PhysRevLett.112.041301}.
+\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: Turbulence within the plasma, left over from the sound wave propagation, will produce gravitational waves with efficiency factor $\kappa_{
 turb} \approx 0.1 \kappa_{v} $~\citep{PhysRevD.74.063521}.
@@
 for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.
+
 The exotic sectors have essentially massless degrees of freedom pre-phase transition and pions with negligible masses post-phase transition.
-Other composite particles, such as baryons, do gain a mass of the order of the transition; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength})\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.
-Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+Other composite particles, such as baryons, do gain a mass of the order of $\Lambda_{\rm QCD}$; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
@@
 \end{equation}
-where quantities such as $\Omega_{\textrm{GW}}^*$ that are calculated at the time of nucleation are denoted with an asterisk.
-These must then be evolved to relate to their values at the time of observation.
-Where  $v \sim 1$ for runaway bubbles.
-$S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.
+where we use $v \sim 1$ for runaway bubbles.
+Quantities such as $\Omega_{\textrm{GW}}^*$ that are calculated at the time of nucleation are denoted with an asterisk, and they must then be evolved to relate to their values at the time of observation.
+$S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions:
 \begin{equation}\label{eqn::spectralshape}
-S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
+S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}.
 \end{equation}
@@
 %
-where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.
+where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}), although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant.
 
@@
 \includegraphics[scale=.3]{Nnatral.png} 
-\caption{ Gravitational wave spectral energy density for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}.
+\caption{ Gravitational wave spectral energy density (solid curves) for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}.
 The curve corresponding to the sum of the sectors is approximately equal to the $i=1$ curve.
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa~\citep{Audley:2017drz} (blue), DECIGO~\citep{10.1093/ptep/pty078} (light blue), BBO~\citep{PhysRevD.72.083005} (red), SKA~\cite{Janssen:2014dka} 5-year (purple), SKA 10-year (orange), SKA 20-year (green).
+The shaded dashed curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity as described in Section~\ref{sec:detection}.
+The ones on the right are space-based interferometers: Lisa~\citep{Audley:2017drz} (blue), DECIGO~\citep{10.1093/ptep/pty078} (light blue), BBO~\citep{PhysRevD.72.083005} (red).
+The ones on the left are for the pulsar timing array SKA~\cite{Janssen:2014dka} for exposure time of 5-year (purple), 10-year (orange), and 20-year (green).
 }
@@
 All contributions are assumed to be purely from runaway bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
+The inset is a closer look at the region around the peaks.
 The shaded curves are the same as Fig.~\ref{fig::Nnatural}.

### 2019-10-04 gwnnDraft02.tex
plot and kappa

@@
 It is commonplace to parameterize the spectral energy density in gravitational waves by~\citep{PhysRevD.75.043507}
-\begin{equation}
+\begin{equation}\label{eqn:SpectralEng}
 \Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{d \rho_{\textrm{GW}}(f) }{d \textrm{\,log}(f)} , 
@@
 \end{equation}
-In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$. 
 The three leading order contributions to the GW power spectrum are as follows:
@@
 Explicitly, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
+Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$.
 In this case, the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.

### 2019-10-04 gwnnDraft02.tex
added glueball stuff

--- 2019-10-04 gwnnDraft02.tex
@@
 The exotic sectors have essentially massless degrees of freedom pre-phase transition and pions with negligible masses post-phase transition.
-Other composite particles, such as baryons, do gain a mass of the order of $\Lambda_{\rm QCD}$; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.
+Other composite particles, such as baryons, do gain a mass of the order of $\Lambda_{\rm QCD}$; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales.
+They do, however, feature glueballs that obtain a mass of the order of the SFOPT and, just as in the case for exotic sectors above, feature small $\alpha_{\infty}$.
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
-Explicitly, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
+Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
 In this case, the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.

### 2019-10-04 gwnnDraft02.tex

@@
 Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
+Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$.
 In this case, the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.

### 2019-10-04 gwnnDraft02.tex
nitpicks of section 6

@@
 with $\epsilon$ being calculable from the scalar potential.
-Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent heat, $\epsilon$ should correspond to the energy density of the hidden sector going through the PT.
+Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  the latent heat $\epsilon$ should correspond to the energy density of the hidden sector going through the PT.
 The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors.
@@
 In more recent work, some authors~\citep{Helmboldt:2019pan,Bai:2018dxf} have attempted to estimate it using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models.
-These studies claim a large range of values and thus a consensus has not yet been reached.
+These studies claim a large range of values with no consensus reached on the precise order of the scaled inverse timescale.
 Under these circumstances, we take the optimistic case in which $\beta/H$ is $\mathcal{O}(10)$.
@@
 The exotic sectors have essentially massless degrees of freedom pre-phase transition and pions with negligible masses post-phase transition.
-Other composite particles, such as baryons, do gain a mass of the order of $\Lambda_{\rm QCD}$; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales.
+Other composite particles, such as baryons, do gain a mass of the order of $\Lambda_{ex}$; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales.
 They do, however, feature glueballs that obtain a mass of the order of the SFOPT and, just as in the case for exotic sectors above, feature small $\alpha_{\infty}$.
@@
 As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $.
-The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},
+The redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},
 \begin{equation}\label{eqn::redshifting}
@@
 In the case of the PTA experiments, the sensitivity curves are dependent on how frequently the pulsar's timing residuals, $\delta t$, are measured. 
-When using Eq.~(\ref{eqn::SNR}) to construct the PSI curves for SKA, the upper integration bound is inversely proportional to pulsar's timing residual, $f_{min} = 1/\delta t$.
+When using Eq.~(\ref{eqn::SNR}) to construct the PLI curves for SKA, the upper integration bound is inversely proportional to pulsar's timing residual, $f_{min} = 1/\delta t$.
 In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations.

### 2019-10-04 gwnnDraft02.tex
plot and kappa

@@
 It is commonplace to parameterize the spectral energy density in gravitational waves by~\citep{PhysRevD.75.043507}
-\begin{equation}\label{eqn:SpectralEng}
+\begin{equation}
 \Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{d \rho_{\textrm{GW}}(f) }{d \textrm{\,log}(f)} , 
@@
 where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density. The total gravitational wave signal is a linear combination of three leading contributions:
-\begin{equation}
+\begin{equation}\label{eqn:SpectralEng}
 h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} .
@@
 where $\gamma$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities.
+$h^2 \Omega_{\gamma} $ is the energy density calculated using Eq.~(\ref{eqn::SNR}) with spectral index $\gamma$  and reference frequency $f_{\textrm{ref}}$.
 The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\gamma \in (-8,-7,-6, ...

### 2019-10-04 gwnnDraft02.tex
plot and kappa

@@
 $h^2 \Omega_{\gamma} $ is the energy density calculated using Eq.~(\ref{eqn::SNR}) with spectral index $\gamma$  and reference frequency $f_{\textrm{ref}}$.
-The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\gamma \in (-8,-7,-6, ...
-, 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$.
+The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\gamma$ and for some fixed threshold value of $\rho_{th}$.
 Each curve will lay tangent to the PLI curve, more formally,

### 2019-10-04 gwnnDraft02.tex
plot and kappa

@@
 The PLI curves are constructed using information from the power law form of the signal,
-\begin{equation}
+\begin{equation}\label{eqn::PowerLaw}
 h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\gamma}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\gamma}
@@
 $h^2 \Omega_{\gamma} $ is the energy density calculated using Eq.~(\ref{eqn::SNR}) with spectral index $\gamma$  and reference frequency $f_{\textrm{ref}}$.
-The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\gamma$ and for some fixed threshold value of $\rho_{th}$.
+The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn::PowerLaw}), for various spectral indices $\gamma$ and for some fixed threshold value of $\rho_{th}$.
 Each curve will lay tangent to the PLI curve, more formally,

### 2019-10-04 gwnnDraft02.tex
even smaller nitpicks
abstract
changes in sec 6

@@
 Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
-Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$).
+%Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). 
 Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$.
@@
 The ones on the right are space-based interferometers: Lisa~\citep{Audley:2017drz} (blue), DECIGO~\citep{10.1093/ptep/pty078} (light blue), BBO~\citep{PhysRevD.72.083005} (red).
-The ones on the left are for the pulsar timing array SKA~\cite{Janssen:2014dka} for exposure time of 5-year (purple), 10-year (orange), and 20-year (green).
+The ones on the left are for the pulsar timing array SKA~\cite{Janssen:2014dka} for exposure time of 5-years (purple), 10-years (orange), and 20-years (green).
 }
@@
 Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal.
-The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in Section~\ref{sec:detection}.
-Notice that the total signal is dominated by the first sectors contribution.
+The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, and the construction of these curves is detailed in Section~\ref{sec:detection}.
+Notice that the total signal is dominated by the first sector's contribution.
 This is caused by the quartic temperature ratio suppression in Eq.~(\ref{eq:alpha}) and the large temperature gaps between adjacent sectors.
@@
 This is not the case if we consider more generalized reheating scenarios.
-Once the restriction that sectors with small Higgs masses are preferentially reheated has been lifted, we can explore a much more vast landscape of hidden sectors than are allowed in the vanilla case.
+Once the restriction that sectors with small Higgs masses are preferentially reheated has been lifted, we can explore a much more vast landscape of hidden sectors than are allowed in the reheaton case.
 Here, we construct several different scenarios that are both detectable and demonstrate a variety of gravitational wave profiles.
@@
 The index indicates the equivalent sector from the $N$naturalness model (Eq.~(\ref{eqn:vevs})).
-It should be noted that although the various sectors transition at different temperatures, they are all assumed to be reheated to the same initial temperature as discussed in Sec.~\ref{sec:genReheat}.}\label{tab:cases}
+It should be noted that although the various sectors undergo phase transitions at different temperatures, they are all assumed to be reheated to the same initial temperature.}\label{tab:cases}
 \end{center}
@@
 
+There are four scenarios that we examine, with key parameters presented in Tab.~\ref{tab:cases}. 
 \begin{itemize}
@@
 \end{itemize}
+%
+In all cases where multiple sectors are reheated, we assume for simplicity that all the hidden sectors are reheated to the same temperature.
 

### 2019-10-04 gwnnDraft02.tex
changes in sec 6.2 and 7

@@
 \begin{abstract}
-We explore the possibility of detecting gravitational waves generated by 1st order phase transitions in multiple dark sectors.
+We explore the possibility of detecting gravitational waves generated by first order phase transitions in multiple dark sectors.
 $N$naturalness is taken as a sample model that features multiple additional sectors, many of which undergo phase transitions that produce gravitational waves.
@@
 where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density. The total gravitational wave signal is a linear combination of three leading contributions:
-\begin{equation}\label{eqn:SpectralEng}
+\begin{equation}
 h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} .
@@
 \\
-\rho^2 = 2 \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}
+\rho^2 = 2 \mathcal{T} \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)},
 \end{split}
 \end{equation}
-Where $\mathcal{T}$ is the exposure time of the experiment.
+where $\mathcal{T}$ is the exposure time of the experiment.
 The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.
@@
 Here, we examined scenarios, including $N$naturalness, that involve multiple hidden sectors and calculated the GW profiles present.
-Our GW projections demonstrate that although vanilla $N$naturalness is not projected to be detectable in the near future, more generalized scenarios with multiple hidden sector SFOPTs are in an observable region and will begin to be probed by next generation space experiments.
+Our GW projections demonstrate that although $N$naturalness with the reheaton scenario presented in~\cite{Arkani-Hamed:2016rle} is not projected to be detectable in the near future, more generalized scenarios with multiple hidden sector SFOPTs are in an observable region and will begin to be probed by next generation space experiments.
 Both cases feature important parts of their GW signals in the void between frequencies detectable by pulsar timing arrays and space-based interferometers --- providing theoretical impetus for new experiments capable of probing this region of frequency space.
@@
 The multiple transitions that occur in the models outlined here create signals that follow this trend: although the individual GW do obey approximate power laws, their sum does not --- leading to a unique signal indicating so-called dark complexity.
-Explicitly, a broadening or distortion of the signal around the peak frequency, precisely where the signal has the most energy, could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors, ultimately providing another means to test and constrain theories.
+Explicitly, a broadening or distortion of the signal around the peak frequency, precisely where the signal has the most energy, could point to a multi-SFOPT scenario and gently guide us in the direction of multiple hidden sectors.
+%ultimately providing another means to test and constrain theories.
 
-Shifting to the other part of our framework, our results leads to the question ``how well can experiments probe non power law signals?" For frequency ranges away from the peak of the total GW signals the quoted detection thresholds should hold: the signals fall off as a power law to a very good approximation.
+Shifting to the other part of our framework, our results leads to the question ``how well can experiments probe non power law signals?" For frequency ranges away from the peak of the total, GW signals the quoted detection thresholds should hold: the signals fall off as a power law to a very good approximation.
 However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law.

### 2019-10-24 gwnnDraft02.tex
final changes
PRD updated submission

@@
 Large numbers of hidden sectors can solve the hierarchy problem as in the Dvali Redi model~\cite{Dvali:2009ne}, in the more recently explored $N$naturalness~\cite{Arkani-Hamed:2016rle} framework, or in orbifold Higgs models~\cite{Craig:2014aea,Craig:2014roa}.
-They can also be motivated by dark matter considerations~\cite{Dienes:2011ja,Dienes:2011sa,Dienes:2016vei}.
+They can also be motivated by dark matter considerations~\cite{Chialva_2013,Dienes:2011ja,Dienes:2011sa,Dienes:2016vei}.
 Motivated by solutions to the hierachy problem, we consider hidden sectors with the same particle content as the Standard Model that have all dimensionless couplings (defined at some high scale) equal to those of the Standard Model.
@@
 \end{equation}
-The three leading order contributions to the GW power spectrum are as follows:
+Each components is scaled by its own unique efficiency factor, $\kappa$. The three leading order contributions to the GW power spectrum are as follows:
 \begin{itemize}
@@
 However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law.
-This points to the need for future work to better understand detection prospects for the next generation of GW detectors.
+Work has been done \cite{alanne2019fresh} in examining GW signals using peak amplitudes and peak frequencies as the defining observables: this is rooted in the assumption that GW signals have a model-independent spectral shape.
+However, our results indicate that this assumption of model-independence cannot hold for all cases: sectors with similar (but different) transition temperatures can create either peak broadening or multi-hump features that differ significantly from a standard power law shape.
+This points to the need for future work to better understand where the power law approximation breaks down and how this affects detection prospects for the next generation of GW detectors.
 

### 2019-10-24 gwnnDraft02.tex
specified spectral shape around peak frequencies

@@
 However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law.
-Work has been done \cite{alanne2019fresh} in examining GW signals using peak amplitudes and peak frequencies as the defining observables: this is rooted in the assumption that GW signals have a model-independent spectral shape.
+Work has been done \cite{alanne2019fresh} in examining GW signals using peak amplitudes and peak frequencies as the defining observables: this is rooted in the assumption that GW signals have a model-independent spectral shape around peak frequencies.
 However, our results indicate that this assumption of model-independence cannot hold for all cases: sectors with similar (but different) transition temperatures can create either peak broadening or multi-hump features that differ significantly from a standard power law shape.

### 2020-01-09 gwnnDraft02.tex
Added in body text dealing with referee

@@
 Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$.
-In this case, the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.
+The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since $\alpha_{\infty}$ is small, this would typically lead to the a scenario where the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$: this is what we assume for the remainder of this section.
+It should be noted, however, that $\alpha$ can be small \cite{Bai:2018dxf,Helmboldt:2019pan}; this leads to the non-bubble collision contributions being important and changes the GW profile.
+This case and the gravitational waves it produces are examined in the appendix.
 

### 2020-01-16 gwnnDraft02.tex
non-runaway material

@@
 \usepackage{soul}
+\usepackage{appendix}
 \graphicspath{{./Figures/}}
@@
 The curve corresponding to the sum of the sectors is approximately equal to the $i=1$ curve.
-All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
+All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$.
+The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$.
 The shaded dashed curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity as described in Section~\ref{sec:detection}.
@@
 \caption{ Gravitational wave spectral energy density for the various scenarios found in Tab.~(\ref{tab:cases}).
-All contributions are assumed to be purely from runaway bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.
-The inset is a closer look at the region around the peaks.
+All contributions are assumed to be purely from runaway bubble collisions $\Omega_{\phi}$.
+The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$.
+The inset is a closer look at the region around the peaks for the $\beta/H  = 10$ case.
 The shaded curves are the same as Fig.~\ref{fig::Nnatural}.
@@
 
+\appendix
+\section*{Appendix: Non-runaway phase transitions}
+\label{sec:appendix}
+
+If the phase transition occurs in the non-runaway regime $(\alpha_{\infty} > \alpha)$, the dominant contributions to the GW energy densities are given by the sound wave $h^2\Omega_{v}$ and MHD $h^2\Omega_{v}$ components,
+\begin{equation}\label{eqn:Spectralnonrun}
+h^2\Omega_{\textrm{GW}} \approx  h^2\Omega_{v} + h^2\Omega_{turb}.
+\end{equation}
+
+\begin{figure*}[tb]
+\centering
+\begin{minipage}[c]{\textwidth}
+\includegraphics[width=.45\textwidth ]{MaxSW.png}
+\hfill
+\includegraphics[width=.45\textwidth]{LargeSW.png} 
+\hfill
+\includegraphics[width=.45\textwidth]{MedSW.png} 
+\hfill
+\includegraphics[width=.45\textwidth]{FiveSW.png} 
+\end{minipage}
+\hfill
+\caption{ Gravitational wave spectral energy density for the various scenarios found in Tab.~(\ref{tab:cases}).
+All contributions are assumed to be from a non-runaway phase transition with terminal velocity $v = 0.95$.
+The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$ .
+The shaded curves are the same as Fig.~\ref{fig::Nnatural}.
+In contrast to the runaway case, most scenarios evade the projected sensistivies of future experiments and therefore is the less optimal situation }
+\label{fig:Haasw}
+\end{figure*}
+
+The new contributions to the GW energy density take on a different form from Eq.~(\ref{eqn::GWengdensity}),
+
+\begin{equation}
+\begin{split}
+h^2\Omega_{v}^* = 1.6 \times 10^{-1} \, v  \, \bigg( \frac{\kappa_{v}\;  \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^1  S_{v}(f),
+\\
+h^2\Omega_{turb}^* = 2.01\times 10^{1} \, v \, \bigg( \frac{\kappa_{turb} \; \alpha}{1 + \alpha} \bigg)^{3/2} \bigg( \frac{H}{\beta} \bigg)^1  S_{turb}(f).
+\end{split}
+\end{equation}
+Where unlike the runaway case, we do not assume $v = 1$ due to the bubbles reaching a terminal velocity.
+The MHD effieceny factor is a fraction of the sound waves, $\kappa_{turb} = \epsilon\kappa_{v}$.
+Current similations have motivated a range of $\epsilon \sim 0.05 - 0.10$, where we take the optimistic case of $\epsilon = 0.10$.
+Both contributions have unique spectral shapes, given to be,
+
+\begin{equation}
+\begin{split}
+S_{v}(f) = (f/f_{p,v})^3\bigg(\frac{7}{4+3(f/f_{p,v})^2}\bigg)^{7/2},
+\\
+S_{turb}(f) = \frac{(f/f_{p,turb})^{3}}{(1 + f/f_{p,turb})^{11/3} (1 + 8\pi(f/H))}.
+\end{split}
+\end{equation}
+The MHD energy density has a spectral shape dependent on the hubble rate at the time of nucleation, $H$.
+Similar to the scalar spectral shape in Eq.~(\ref{eqn::spectralshape}), the frequencies are scaled by their respective temperature dependent peak frequency,
+
+\begin{equation}
+\begin{split}
+f_{p,v} = 1.9 \times 10^{-5} \, \textrm{Hz}\, \frac{1}{v} \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
+\\
+f_{p,turb} =  2.7 \times 10^{-5} \, \textrm{Hz}\, \frac{1}{v} \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
+\end{split}
+\end{equation}
+
+We evolve the frequencies and energy densities with the same redshift factors, Eq.~(\ref{eqn::redshifting}) from Sec~\ref{sec:gw}.
+Fig.~\ref{fig:Haasw} shows the sum of the GW energy density for the scenarios in Table~\ref{tab:cases}, but instead for the non-runaway case, with a terminal velocity of $v = 0.95$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-01-24 gwnnDraft02.tex
Fixed the figure names
Fixed missing units in section 3.
Found another typo.

@@
 where $n_f^i$ is the number of quark flavours with mass less than $\mu/2$ and $\Lambda^i$ is the scale where it would confine if all quarks remain massless.
-In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 5$ in $\overline{MS}$~\cite{PhysRevD.98.030001}.
+In the SM defined at scales well above all the quark masses, we have $\Lambda_{QCD} = 89 \pm 5$ MeV in $\overline{MS}$~\cite{PhysRevD.98.030001}.
 Because we have set the strong couplings equal at high scales, $\Lambda = \Lambda^i$ for all $i$ at high scales for all sectors.
@@
 Reheating occurs through the introduction a ``reheaton'' field.
-After inflation, the reheaton field possess the majority of the energy density of the Universe.
+After inflation, the reheaton field possesses the majority of the energy density of the Universe.
 Although this field can generically be either bosonic or fermionic, we reduce our scope to a scalar reheaton $\phi$.
@@
 \hfill
-\includegraphics[width=.45\textwidth]{LargeSW.png} 
+\includegraphics[width=.45\textwidth]{largeSW.png} 
 \hfill
@@
 \hfill
-\includegraphics[width=.45\textwidth]{FiveSW.png} 
+\includegraphics[width=.45\textwidth]{fiveSW.png} 
 \end{minipage}

### 2020-02-05 gwnnDraft02.tex
new max plot
made changes suggested by Daniel

@@
 They do, however, feature glueballs that obtain a mass of the order of the SFOPT and, just as in the case for exotic sectors above, feature small $\alpha_{\infty}$.
-Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime.
+
 %Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). 
 Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$.
-The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since $\alpha_{\infty}$ is small, this would typically lead to the a scenario where the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$: this is what we assume for the remainder of this section.
-It should be noted, however, that $\alpha$ can be small \cite{Bai:2018dxf,Helmboldt:2019pan}; this leads to the non-bubble collision contributions being important and changes the GW profile.
+The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since $\alpha_{\infty}$ is small, this would typically lead to the a scenario with runaway bublle walls where efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$: this is what we assume for the remainder of this section.
+It should be noted, however, that $\alpha$ can also be small \cite{Bai:2018dxf,Helmboldt:2019pan}; this leads to bubbles that are non-runaway (but $v_w \sim 1$ still \cite{Breitbach:2018ddu,Bodeker2017}) such that non-bubble collision contributions being important --- ultimately leading to significant changes to the GW profile.
 This case and the gravitational waves it produces are examined in the appendix.
@@
 All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$.
-The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$.
+The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$ (the sum of all sectors is roughly equal to the $i = 1$ curve and sectors beyond the first are below the range of this plot).
 The shaded dashed curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity as described in Section~\ref{sec:detection}.
@@
 The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$ .
+The top left figure shows the individua sound wave and MHD contributions.
 The shaded curves are the same as Fig.~\ref{fig::Nnatural}.

### 2020-02-05 gwnnDraft02.tex
beta/h change

@@
 There are dimensional arguments~\cite{Hogan:1984hx,Hogan:1986qda} that predict $\beta/H \sim 4 \textrm{Log}(M_{p}/ \Lambda_{QCD,i})$, although these arguments make specific assumptions about the potential.
-In more recent work, some authors~\citep{Helmboldt:2019pan,Bai:2018dxf} have attempted to estimate it using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models.
+In more recent work, some authors~\citep{Helmboldt:2019pan,Bai:2018dxf} have attempted to estimate it using first-order chiral effective theories and the Polyakov-Nambu-Jona-Lasinio (PNJL) models which motivates a $\beta/H$ of $\mathcal{O}(10^4)$.
 These studies claim a large range of values with no consensus reached on the precise order of the scaled inverse timescale.
-Under these circumstances, we take the optimistic case in which $\beta/H$ is $\mathcal{O}(10)$.
+Under these circumstances, our signal projections will consider both extremes of the parameter space where, $\beta/H \sim 10 - 10^4$.
+A more realistic scenario may exist in between both cases.
 

### 2020-02-06 refereeResponse.tex
referee response tex

%%%%%%%%%%%%%%%%% DO NOT CHANGE HERE %%%%%%%%%%%%%%%%%%%% {
\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}

\hypersetup{%
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% }

%%%%%%%%%%%%%%%%%%%%%%%% CHANGE HERE %%%%%%%%%%%%%%%%%%%% {
\newcommand\course{}
\newcommand\semester{Jan 2020}
\newcommand\hwnumber{}                 % <-- ASSIGNMENT #
\newcommand\NetIDa{}           % <-- YOUR NAME
\newcommand\NetIDb{}           % <-- STUDENT ID #
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% }

%%%%%%%%%%%%%%%%% DO NOT CHANGE HERE %%%%%%%%%%%%%%%%%%%% {
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDa}
\lhead{\NetIDa\\\NetIDb}                 
\chead{\textbf{\Large Referee Response \hwnumber}}
\rhead{\course \\ \semester}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% }

\begin{document}

We thank the referee for their valuable comments, and we have made changes to the manuscript to address them. The changes are labeled with respect to the points raised in the referee's report.

1) As the referee mentioned, there is a range of allowed values of the inverse transition time, $\beta/H$. According to the literature, the allowed range is roughly $10 < \beta/H < 10^4$. Originally, we only included the most optimistic scenario where this was taken to be $10$. We have added gravitational wave spectra for the other extreme of the range $\beta/H = 10^4$ in all of our plots. This demonstrates both the range in possible peak frequencies and signal strengths available for our phase transitions. We have also added a discussion of different values of $\beta/H$ in section VI as well as in ???.

2) We have expanded our analysis to include the possibility of sound wave and MHD contributions to the gravitational wave spectrum. We have added a discussion in Sec.~VI.A highlighting other possibilities, and we have added an appendix and Fig. 3 to quantitatively explore the gravitational wave signals where the bubbles are non-runaway and the sound wave and MHD contributions become important.  The results have a slightly different spectral profile and tend to produce a weaker but (in some cases) still detectable gravitational wave profile.

3)The plots have been relabeled and the capital I has been removed in order to increase clarity.

-Paul Archer-Smith, Dylan Linthorne, and Daniel Stolarski

\end{document}

### 2020-02-06 gwnnDraft02.tex
appendix refs

@@
 
-If the phase transition occurs in the non-runaway regime $(\alpha_{\infty} > \alpha)$, the dominant contributions to the GW energy densities are given by the sound wave $h^2\Omega_{v}$ and MHD $h^2\Omega_{v}$ components,
+If the phase transition occurs in the non-runaway regime $(\alpha_{\infty} > \alpha)$, the dominant contributions to the GW energy densities are given by the sound wave $h^2\Omega_{v}$ and MHD $h^2\Omega_{v}$ components \citep{Breitbach:2018ddu},
 \begin{equation}\label{eqn:Spectralnonrun}
@@
 
-The new contributions to the GW energy density take on a different form from Eq.~(\ref{eqn::GWengdensity}),
+The new contributions to the GW energy density take on a different form from Eq.~(\ref{eqn::GWengdensity}) \citep{Caprini:2015zlo},
 
@@
 The MHD effieceny factor is a fraction of the sound waves, $\kappa_{turb} = \epsilon\kappa_{v}$.
-Current similations have motivated a range of $\epsilon \sim 0.05 - 0.10$, where we take the optimistic case of $\epsilon = 0.10$.
-Both contributions have unique spectral shapes, given to be,
+Current similations have motivated a range of $\epsilon \sim 0.05 - 0.10$  \citep{Caprini:2015zlo}, where we take the optimistic case of $\epsilon = 0.10$.
+Both contributions have unique spectral shapes, given to be \citep{Breitbach:2018ddu},
 

### 2020-02-07 gwnnDraft02.tex
fixed language about alpha inf and alpha

--- 2020-02-05 gwnnDraft02.tex
@@
 Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$.
-The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since $\alpha_{\infty}$ is small, this would typically lead to the a scenario with runaway bublle walls where efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$: this is what we assume for the remainder of this section.
-It should be noted, however, that $\alpha$ can also be small \cite{Bai:2018dxf,Helmboldt:2019pan}; this leads to bubbles that are non-runaway (but $v_w \sim 1$ still \cite{Breitbach:2018ddu,Bodeker2017}) such that non-bubble collision contributions being important --- ultimately leading to significant changes to the GW profile.
+The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since both $\alpha_{\infty}$ and $\alpha$ are parameterically small \cite{Bai:2018dxf,Helmboldt:2019pan} a range of possible scenarios can occur.
+Here, we discuss the two ends of this spectrum: pure runaway walls and pure non-runaway walls.
+The former scenario with runaway bublle walls leads to the efficiency factors for the sound wave and MHD contributions being small and ensures GWs are dominantly produced from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$: this is what we assume for the remainder of this section.
+In the latter case, bubbles are non-runaway (but $v_w \sim 1$ still \cite{Breitbach:2018ddu,Bodeker2017}) such that non-bubble collision contributions being important --- ultimately leading to significant changes to the GW profile.
 This case and the gravitational waves it produces are examined in the appendix.
+Intermediate results are of course possible, and would feature profiles somewhere in between the two extremes.
 

### 2020-02-12 gwnnDraft02.tex
typos corrected, appendix expanded

@@
 Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$.
-The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since both $\alpha_{\infty}$ and $\alpha$ are parameterically small \cite{Bai:2018dxf,Helmboldt:2019pan} a range of possible scenarios can occur.
+The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since both $\alpha_{\infty}$ and $\alpha$ are parameterically small \cite{Bai:2018dxf,Helmboldt:2019pan}, a range of possible scenarios can occur.
 Here, we discuss the two ends of this spectrum: pure runaway walls and pure non-runaway walls.
@@
 Individual SFOPT are understood to create GW that are assumed to follow an approximate power law.
-If a model predicts of the presence of 2, 5, or more additional sectors, or features a single extra sector with multiple PTs, deviations from a standard power law can occur.
+If a model predicts the presence of 2, 5, or more additional sectors, or features a single extra sector with multiple PTs, deviations from a standard power law can occur.
 The multiple transitions that occur in the models outlined here create signals that follow this trend: although the individual GW do obey approximate power laws, their sum does not --- leading to a unique signal indicating so-called dark complexity.
@@
 All contributions are assumed to be from a non-runaway phase transition with terminal velocity $v = 0.95$.
-The colored solid lines use $\beta/H  = 10$ where as the dashed gray line is the total contribution of all sectors for $\beta/H  = 10^4$ .
-The top left figure shows the individua sound wave and MHD contributions.
+The coloured solid lines use $\beta/H  = 10$ where as the dashed grey line is the total contribution of all sectors for $\beta/H  = 10^4$ .
+The top left figure shows the individual sound wave and MHD contributions.
 The shaded curves are the same as Fig.~\ref{fig::Nnatural}.
-In contrast to the runaway case, most scenarios evade the projected sensistivies of future experiments and therefore is the less optimal situation }
+In contrast to the runaway case, most scenarios evade the projected sensitivities.
+}
 \label{fig:Haasw}
@@
 \end{equation}
-Where unlike the runaway case, we do not assume $v = 1$ due to the bubbles reaching a terminal velocity.
-The MHD effieceny factor is a fraction of the sound waves, $\kappa_{turb} = \epsilon\kappa_{v}$.
-Current similations have motivated a range of $\epsilon \sim 0.05 - 0.10$  \citep{Caprini:2015zlo}, where we take the optimistic case of $\epsilon = 0.10$.
+Unlike the runaway case, we do not assume $v = 1$ due to the bubbles reaching a terminal velocity.
+The MHD efficiency factor is a fraction of the sound waves, $\kappa_{turb} = \epsilon\kappa_{v}$.
+Current simulations have motivated a range of $\epsilon \sim 0.05 - 0.10$  \citep{Caprini:2015zlo}, where we take the optimistic case of $\epsilon = 0.10$.
 Both contributions have unique spectral shapes, given to be \citep{Breitbach:2018ddu},
-
+%
 \begin{equation}
@@
 \end{equation}
-The MHD energy density has a spectral shape dependent on the hubble rate at the time of nucleation, $H$.
+The MHD energy density has a spectral shape dependent on the Hubble rate at the time of nucleation, $H$.
 Similar to the scalar spectral shape in Eq.~(\ref{eqn::spectralshape}), the frequencies are scaled by their respective temperature dependent peak frequency,
@@
 Fig.~\ref{fig:Haasw} shows the sum of the GW energy density for the scenarios in Table~\ref{tab:cases}, but instead for the non-runaway case, with a terminal velocity of $v = 0.95$.
+For this case we see that the spectra tend to be shifted to lower frequencies and are more likely to fall in the gap between the interferometers and the pulsar based detectors.
+On the other hand, larger values of $\beta/H$ increase the typical frequency, so this case becomes more sensitive in some scenarios to values of $\beta/H$ on the larger end of the considered range.
+
+Finally, we note that because the sound wave and MHD contributions have different spectral shapes, the overall spectrum has a kink at a frequency above the peak.
+In the top left panel of Fig.~\ref{fig:Haasw}, we show the two contributions separately in addition to their sum to highlight this effect.
 

### 2020-04-01 gwnnDraft02.tex
changes
second ref edits

@@
 \end{equation}
-where we use $v \sim 1$ for runaway bubbles.
+where we use $v = 1$ for runaway bubbles.
 Quantities such as $\Omega_{\textrm{GW}}^*$ that are calculated at the time of nucleation are denoted with an asterisk, and they must then be evolved to relate to their values at the time of observation.
@@
 
-\begin{equation}
+\begin{equation}\label{eqn::SWMHD}
 \begin{split}
@@
 Both contributions have unique spectral shapes, given to be \citep{Breitbach:2018ddu},
+
+In the sound wave case, these parametizations are extracted from simulations with $\beta/H < 100$ corresponding to a long lasting sound wave component.
+For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time.
+When casting the model expectations for $\beta/H = 10^4$ we enter a regime at which ~(\ref{eqn::SNR}) may be overestimated the sound wave contribution.
+Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}.
+Although Independent of overestimating or signal, this paper focuses on the unique spectral shapes that are formed in these extraneous models.
+Therefore we project our results for high $\beta/H$ in Fig.~\ref{fig:Haasw}  to motivate the spectral profiles and not detectability.
 %

### 2020-04-01 gwnnDraft02.tex
rewording appendix

@@
 Both contributions have unique spectral shapes, given to be \citep{Breitbach:2018ddu},
-
-In the sound wave case, these parametizations are extracted from simulations with $\beta/H < 100$ corresponding to a long lasting sound wave component.
-For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time.
-When casting the model expectations for $\beta/H = 10^4$ we enter a regime at which ~(\ref{eqn::SNR}) may be overestimated the sound wave contribution.
-Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}.
-Although Independent of overestimating or signal, this paper focuses on the unique spectral shapes that are formed in these extraneous models.
-Therefore we project our results for high $\beta/H$ in Fig.~\ref{fig:Haasw}  to motivate the spectral profiles and not detectability.
 %
@@
 \\
-f_{p,turb} =  2.7 \times 10^{-5} \, \textrm{Hz}\, \frac{1}{v} \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}},
+f_{p,turb} =  2.7 \times 10^{-5} \, \textrm{Hz}\, \frac{1}{v} \bigg( \frac{\beta}{H}\bigg)\bigg(\frac{T_{\gamma}}{100 \, \textrm{GeV}}\bigg)\bigg(\frac{g_{*}}{100}\bigg)^{\frac{1}{6}}.
 \end{split}
 \end{equation}
-
+%
 We evolve the frequencies and energy densities with the same redshift factors, Eq.~(\ref{eqn::redshifting}) from Sec~\ref{sec:gw}.
@@
 On the other hand, larger values of $\beta/H$ increase the typical frequency, so this case becomes more sensitive in some scenarios to values of $\beta/H$ on the larger end of the considered range.
+
+In the sound wave case, these parametizations are extracted from simulations with $\beta/H < 100$ corresponding to a long lasting sound wave component.
+For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time.
+When estimating the model expectations for $\beta/H = 10^4$, we enter a regime at which Eq.~(\ref{eqn::SNR}) \draftnote{Is this the right equation reference?} may be overestimating the sound wave contribution.
+Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}.
+This effect, however, only affects the amplitude of the signal, and our work focuses on the unique spectral shapes that are formed in these models.
+Therefore we project our results for high $\beta/H$ in Fig.~\ref{fig:Haasw} to motivate the novel spectral profiles.
 

### 2020-04-06 gwnnDraft02.tex
Fixed equation reference and typos.

@@
 
-If the phase transition occurs in the non-runaway regime $(\alpha_{\infty} > \alpha)$, the dominant contributions to the GW energy densities are given by the sound wave $h^2\Omega_{v}$ and MHD $h^2\Omega_{v}$ components \citep{Breitbach:2018ddu},
+If the phase transition occurs in the non-runaway regime $(\alpha_{\infty} > \alpha)$, the dominant contributions to the GW energy densities are given by the sound wave $h^2\Omega_{v}$ and MHD $h^2\Omega_{turb}$ components \citep{Breitbach:2018ddu},
 \begin{equation}\label{eqn:Spectralnonrun}
@@
 For high $\beta/H$ the transition timescale from sound wave to MHD turbulence is much shorter than the Hubble time.
-When estimating the model expectations for $\beta/H = 10^4$, we enter a regime at which Eq.~(\ref{eqn::SNR}) \draftnote{Is this the right equation reference?} may be overestimating the sound wave contribution.
+When estimating the model expectations for $\beta/H = 10^4$, we enter a regime at which Eq.~(\ref{eqn::SWMHD}) may be overestimating the sound wave contribution.
 Investigations of this regime have been done in \citep{Hindmarsh:2017gnf, Ellis:2018mja, Ellis_2019}.

### 2020-04-09 gwnnDraft02.tex
Fixed dof typo

@@
 At the time of photon decoupling, $T_\gamma \sim 0.39 \;\ev$ while the temperature of the exotic sectors is lower.
-This means that for sectors with small and moderate $i$, we can use Eqs.~(\ref{eqn:exoticFM}) and~(\ref{eq:ith_pion_mass}) to see that the pions will be non-relativistic  leaving at most $11.25$ effective degrees of freedom per sector from photons and neutrinos.
+This means that for sectors with small and moderate $i$, we can use Eqs.~(\ref{eqn:exoticFM}) and~(\ref{eq:ith_pion_mass}) to see that the pions will be non-relativistic  leaving at most $7.25$ effective degrees of freedom per sector from photons and neutrinos.
 For very large $i$, the pions can be much lighter, but those sectors also have very little energy in them in the standard reheating scenario.

### 2020-04-14 refereeResponseV2.tex
referee response V2

--- 2020-02-06 refereeResponse.tex
@@
 
-We thank the referee for their valuable comments, and we have made changes to the manuscript to address them. The changes are labeled with respect to the points raised in the referee's report.
+We thank the referee for their valuable comments, and we have made changes to the manuscript to address them.
 
-1) As the referee mentioned, there is a range of allowed values of the inverse transition time, $\beta/H$.
-According to the literature, the allowed range is roughly $10 < \beta/H < 10^4$.
-Originally, we only included the most optimistic scenario where this was taken to be $10$.
-We have added gravitational wave spectra for the other extreme of the range $\beta/H = 10^4$ in all of our plots.
-This demonstrates both the range in possible peak frequencies and signal strengths available for our phase transitions.
-We have also added a discussion of different values of $\beta/H$ in section VI as well as in ???.
-
-2) We have expanded our analysis to include the possibility of sound wave and MHD contributions to the gravitational wave spectrum.
-We have added a discussion in Sec.~VI.A highlighting other possibilities, and we have added an appendix and Fig.
-3 to quantitatively explore the gravitational wave signals where the bubbles are non-runaway and the sound wave and MHD contributions become important.
-The results have a slightly different spectral profile and tend to produce a weaker but (in some cases) still detectable gravitational wave profile.
-
-3)The plots have been relabeled and the capital I has been removed in order to increase clarity.
+As the referee mentioned, at large values of $\beta/H$ the phase transition duration can be short when compared to the intrinsic time scale in the fluid and, as a result, the sound waves that act as GW sources may be active for a much shorter duration than the Hubble time.
+A comment discussing how at large $\beta/H$ the traditional GW profile may overestimate the sound wave contribution has been added to the appendix exploring acoustically sourced GW.
+Since our work focuses on the unique spectral shapes (and not the amplitude) formed in these models, we do not carry out any additional analysis in this direction, but leave appropriate references for the interested reader.
 

### 2020-04-14 refereeResponseV2.tex
response

@@
 \newcommand\course{}
-\newcommand\semester{Jan 2020}
+\newcommand\semester{April 2020}
 \newcommand\hwnumber{}                 % <-- ASSIGNMENT #
@@
 \lhead{\NetIDa\\\NetIDb}                 
-\chead{\textbf{\Large Referee Response \hwnumber}}
+\chead{\textbf{\Large Second Referee Response \hwnumber}}
 \rhead{\course \\ \semester}
@@
 As the referee mentioned, at large values of $\beta/H$ the phase transition duration can be short when compared to the intrinsic time scale in the fluid and, as a result, the sound waves that act as GW sources may be active for a much shorter duration than the Hubble time.
-A comment discussing how at large $\beta/H$ the traditional GW profile may overestimate the sound wave contribution has been added to the appendix exploring acoustically sourced GW.
-Since our work focuses on the unique spectral shapes (and not the amplitude) formed in these models, we do not carry out any additional analysis in this direction, but leave appropriate references for the interested reader.
+The relevant references have been added to the appendix, along with a comment discussing how at large $\beta/H$ the traditional GW profile may overestimate the sound wave contribution.
+Since our paper focuses on the unique spectral shapes (and not the amplitude) formed in these models, additional analysis of this regime is beyond the scope of this work.
 
